### 2021-06-16 paper.tex
first commit

\documentclass[jkps,preprint,fleqn,showpacs,showkeys]{revtex4}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{cleveref}

%\input{commands.tex}

\newcommand{\pp}{\mbox{$pp$}\xspace}
\newcommand{\pAu}{\mbox{$p$+Au}\xspace}
\newcommand{\pPb}{\mbox{$p$+Pb}\xspace}
\newcommand{\pythia}{\textsc{Pythia8}\xspace}
\newcommand{\deta}{\mbox{$\Delta\eta$}\xspace}
\newcommand{\dphi}{\mbox{$\Delta\varphi$}\xspace}
\newcommand{\pt}{\mbox{$p_{\mathrm{T}}$}\xspace}
\newcommand{\pT}{\mbox{$p_{T}$}\xspace}
\newcommand{\Nch}{\mbox{$N_\mathrm{ch}$}\xspace}
\newcommand{\pythiae}{\pythia\ensuremath{~\mathrm{default}}}
\newcommand{\pythiashoving}{{\pythia\ensuremath{~\mathrm{String}~}}\ensuremath{\mathrm{Shoving}}}
\newcommand{\sonly}        {\ensuremath{\sqrt{s}}}

\begin{document}
\setcounter{page}{0}
\title[]{Exploring the string shoving model in PYTHIA8 \\for collective behaviors in $pp$ collisions}
\author{Junlee \surname{Kim}}
\email{junlee.kim@cern.ch}
\author{Eun-Joo \surname{Kim}}
\affiliation{Division of Science Education, Jeonbuk National University, Jeonju 54896}
\author{SuJeong \surname{Ji}}
\author{SangHoon \surname{Lim}}
\email{shlim@pusan.ac.kr}
%\thanks{Fax: +82-2-554-1643}
\affiliation{Department of Physics, Pusan National University, Busan 46241}

%\date[]{Received 6 August 2007}

\begin{abstract}
Two-particle correlations have been used to study property of a produced medium called Quark-Gluon Plasma (QGP) in relativistic heavy-ion collisions, and a long-range correlation among produced particles has been considered as a strong evidence of strongly interacting QGP. 
Strikingly, clear long-range correlations have been also observed in small collision systems like $pp$ and $p$+$A$ at a wide range of collision energies. 
%Several theoretical approaches have been proposed, but results in small collision systems have not fully understood yet.
A model introducing a repulsive force between flux tubes called string shoving can qualitatively describe the long-range near-side correlations in high multiplicity $pp$ collisions. 
This model implemented in the \pythia Monte Calro event generator allows us to perform detailed study.
In this work, a full data analysis to calculate associated yields and flow coefficients is performed with \pythia events, and the results are compared with experimental results.
We find that the string shoving model overestimates long-range near-side correlations particularly in low multiplicity events.
We also introduce a method to subtract such overestimated correlations in low multiplicity to have a more relevant comparison with the data. 
%Further study reveals that the string shoving model also generates the repulsive force in jet fragments. We also introduce a method to subtract such overestimated correlations and find that the predictions from the string shoving  after the subtraction are more comparable with the experimental results.

\end{abstract}

\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
\keywords{String shoving, Collectivity, $pp$ collision}
\maketitle

\input{sec_intro.tex}
\pagebreak
\input{sec_ana.tex}
\pagebreak
\input{sec_results.tex}
\input{sec_summary.tex}

%\pagebreak

\begin{acknowledgments}
%The authors would like to thank for useful discussions and a careful reading of the manuscript. 
%J. Kim and E.-J. Kim acknowledge support from the... .
S.J. Ji and S.H. Lim acknowledge support from a 2-Year Research Grant of Pusan
National University.
%The authors would like to thank Mr. Kim for helpful discussions and
%gratefully acknowledge support by MOCIE through National R$\&$D
%Project for Nano Science and Technology. C. H. C. and W. J. J.
%acknowledge the financial support by MOE through BK21 fellowships.
\end{acknowledgments}

\bibliography{paper}

\end{document}

### 2021-06-16 sec_ana.tex
first commit

% !TEX root = JKPS_TeX_sample_eps.tex

\section{Study with \pythia}
\label{sec:ana}
The string shoving model is quantitatively studied by analyzing charged hadrons from millions of non-diffractive \pythia \pp events at $\sqrt{s}=13~\mathrm{TeV}$. 
The event multiplicity is defined with charged hadrons satisfying $|\eta|<$~2.4 and $\pt>$~0.4~GeV/$c$, which is equivalent definition to the experimental results.
To calculate two-particle correlations, we follow the formula for per-trigger yields~\cite{Khachatryan:2015lva}, which is defined as, 
\begin{align}
    \frac{1}{N_{\rm{trig}}} \frac{ {\rm d^{2}} N_{\rm{pair}} }{ \rm{d}\deta \rm{d}\dphi} = B(0,0)\frac{S(\deta, \dphi)}{B(\deta, \dphi)},
\end{align}
where $N_\mathrm{trig}$ and $N_\mathrm{pair}$ are the number of trigger particles and the number of pairs, respectively.
$S (\Delta\eta, \Delta\varphi)$ and $B(\Delta\eta, \Delta\varphi)$ are per-trigger yields in same and mixed events:
\begin{align}
    S(\deta,\dphi) &= \frac{1}{N_{{\rm trig}}} \frac{ {\rm d^{2}} N_{\rm{pair}}^{\rm same} }{ \rm{d}\deta \rm{d}\dphi},\\
    B(\deta,\dphi) &= \frac{1}{N_{{\rm trig}}} \frac{ {\rm d^{2}} N_{\rm{pair}}^{\rm mixed} }{ \rm{d}\deta \rm{d}\dphi},
\end{align}
and $B(0, 0)$ is the per-trigger yield at $(\deta,\dphi)=(0,0)$, where the pair acceptance is maximum.

\begin{figure}[tbh]
\includegraphics[width=0.49\textwidth]{figures/2D_default_lo_final.pdf}
\includegraphics[width=0.49\textwidth]{figures/2D_default_hi_final.pdf}
\caption{Two-particle correlation functions for charged hadrons in $|\eta|<$~2.4 and 1~$<\pt<$~2~GeV/$c$ from low (left) and high (right) multiplicity \pythia \pp events at $\sqrt{s}=$~13~TeV with the default configuration. \Nch is calculated with charged hadrons in $|\eta|<$~2.4 and $\pt>$~0.4~GeV/$c$.}
\label{fig:2d_default_final}
\end{figure}

\begin{figure}[tbh]
\includegraphics[width=0.49\textwidth]{figures/2D_shoving_lo_final.pdf}
\includegraphics[width=0.49\textwidth]{figures/2D_shoving_hi_final.pdf}
\caption{Two-particle correlation functions for charged hadrons in $|\eta|<$~2.4 and 1~$<\pt<$~2~GeV/$c$ from low (left) and high (right) multiplicity \pythia \pp events at $\sqrt{s}=$~13~TeV with the string shoving model. \Nch is calculated with charged hadrons in $|\eta|<$~2.4 and $\pt>$~0.4~GeV/$c$.}
\label{fig:2d_shoving_final}
\end{figure}

\Cref{fig:2d_default_final,fig:2d_shoving_final,fig:2d_default_initial,fig:2d_shoving_initial} show two-particle \deta--\dphi correlation functions with charged hadrons for 1~$<\pt<$~2~GeV/$c$ in low (left) and high (right) multiplicity \pythia \pp events at $\sqrt{s}=$~13~TeV with different configurations. 
In \pythia events with the default configuration (Figure~\ref{fig:2d_default_final}), there is no long-range near-side correlation in two different multiplicity bins as expected. 
On the other hand, The correlation functions with the string shoving option shown in Figure~\ref{fig:2d_shoving_final} clearly exhibit a long-range near-side correlation called ``ridge''.
It is also worth mentioning that a ridge structure is observed even in low multiplicity events ($0\leq \Nch <20$) with the string shoving model, which is not seen in experimental results~\cite{Khachatryan:2015lva}.
For a closer look on correlations developed in the string shoving model, correlation functions with initial charged hadrons directly produced from partons are calculated as shown in \Cref{fig:2d_default_initial,fig:2d_shoving_initial}.
Like the correlation functions with final charged hadrons, a clear long-range near-side correlation is observed in events with the string shoving, whereas no such correlation is seen in events with the default configuration.
The ridge structure with initial charged hadrons is more prominent than one with final charged hadrons, and this implies that a smearing effect in decay processes decreases the correlation strength among particles.

\begin{figure}[tbh]
\includegraphics[width=0.49\textwidth]{figures/2D_default_lo_initial.pdf}
\includegraphics[width=0.49\textwidth]{figures/2D_default_hi_initial.pdf}
\caption{Two-particle correlation functions for charged hadrons in $|\eta|<$~2.4 and 1~$<\pt<$~2~GeV/$c$ from low (left) and high (right) multiplicity \pythia \pp events at $\sqrt{s}=$~13~TeV with the default configuration. Initial charged particles produced directly from partons are used for the correlations, and \Nch is calculated with final charged hadrons in $|\eta|<$~2.4 and $\pt>$~0.4~GeV/$c$.}
\label{fig:2d_default_initial}
\end{figure}

\begin{figure}[tbh]
\includegraphics[width=0.49\textwidth]{figures/2D_shoving_lo_initial.pdf}
\includegraphics[width=0.49\textwidth]{figures/2D_shoving_hi_initial.pdf}
\caption{Two-particle correlation functions for charged hadrons in $|\eta|<$~2.4 and 1~$<\pt<$~2~GeV/$c$ from low (left) and high (right) multiplicity \pythia \pp events at $\sqrt{s}=$~13~TeV with the string shoving model. Initial charged particles produced directly from partons are used for the correlations, and \Nch is calculated with final charged hadrons in $|\eta|<$~2.4 and $\pt>$~0.4~GeV/$c$.}
\label{fig:2d_shoving_initial}
\end{figure}

One-dimensional \dphi correlation functions are constructed by averaging the two-dimensional correlation functions at a certain \deta range:
\begin{align}
\frac{1}{N_{\mathrm{trig}}} \frac{ \mathrm{d} N_{\mathrm{pair}} }{ \mathrm{d}\Delta\varphi } = \int \mathrm{d} \Delta \eta \frac{1}{\it{N}_{\mathrm{trig}}} \frac{ \mathrm{d}^{2} N_{\mathrm{pair}} }{ \mathrm{d}\Delta\eta d\Delta\varphi}.
\end{align}
For long-range correlations, the \deta range is determined as 2~$<|\deta|<$~4, where non-flow effects from di-jets and particle decay are expected to be not significant. 
The correlated part is estimated by implementing the Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi$=$\Delta\varphi_{\rm{min}}$ for each \dphi correlation function is obtained by fitting the \dphi correlation function with a Fourier series up to the third term and is subtracted from the \dphi correlation function.
This procedure results in the \dphi correlation function at $\Delta\varphi_{\rm{min}}$ to be zero.

Figure~\ref{fig:dphi} shows one-dimensional \dphi correlation functions at long-range (2~$<|\deta|<$~4) after applying the ZYAM procedure for different \pt ranges in low (upper) and high (lower) multiplicity events.
\pythia events with the default configuration show no near-side structure in different \pt and multiplicity ranges. 
\pythia events with the string shoving option, on the other hand, clearly show near-side peaks.
The CMS results~\cite{Khachatryan:2015lva} are compared with the correlation functions from \pythia events, and the multiplicity ranges for \pythia events are selected $\sim15\%$ higher than the multiplicity ranges for CMS results to consider a track reconstruction efficiency.
The string shoving model overestimates near-side correlation for 1~$<\pt<$~2~GeV/$c$ in low multiplicity events.
In the high multiplicity range, the correlation function of final charged hadrons for 1~$<\pt<$~2~GeV/$c$ in \pythia events with the string shoving nicely agrees with the CMS result.
However, the model underestimates the near-side correlation for higher \pt ranges.

\begin{figure}[!h]
\includegraphics[width=1.0\textwidth]{figures/dphi_all2.pdf}
\caption{One-dimensional long-range (2~$<|\Delta\eta|<$~4) $\Delta\varphi$ correlations in low and high multiplicity events for different \pt bins. The CMS results (closed circle)~\cite{Khachatryan:2015lva} are compared with correlation functions using initial (dashed) and final (solid) charged hadrons from \pythia events with (red) and without (blue) the string shoving.}
\label{fig:dphi}
\end{figure}

### 2021-06-16 sec_intro.tex
first commit

% !TEX root = JKPS_TeX_sample_eps.tex

\section{Introduction}
\label{sec:intro}

A strong momentum correlation of produced particles from relativistic heavy-ion collisions is thought to be originated from an initial geometric anisotropy and hydrodynamic evolution~\cite{Busza:2018rrf}.
Two-particle correlations in \dphi (azimuthal angle difference) and \deta (pseudorapidity difference) have been measured to study azimuthal correlations among produced particles, and a clear correlation has been observed in long-range ($|\deta|>2$) where correlations from resonance decay and jet fragmentation are expected to be small.
Interestingly, such long-range correlation has been also observed in small collision systems like \pp, \pAu, and \pPb collisions over a wide range of collision energy at Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC)~\cite{Nagle:2018nvi}.
Extensive studies have been performed to quantify the collective behavior in small collision systems, and a significant elliptic flow has been measured even in \pp collisions~\cite{Aad:2015gqa,Khachatryan:2016txc}.
Many theoretical approaches have been introduced to explain the data.
One is to apply hydrodynamic evolution developed to describe the flow in heavy-ion collisions~\cite{Weller:2017tsr}, and the other is a model of initial-state correlations among gluons~\cite{Dumitru:2010iy}.
The models considering hydrodynamic behavior generally provide a better description of the data, but it is not yet conclusive.

Recently another model called string shoving model was proposed to describe the long-range correlation in high multiplicity \pp collisions~\cite{Bierlich:2016vgw}.
This model introduces a repulsive force between flux tubes so that the flux tube expands both longitudinally and transversely.
In a high multiplicity \pp event, where many partonic interactions can occur, one string may overlap with many other strings.
The repulsion among these overlapping strings right after the collision results in correlation between particles even in a large \deta range.
In the comparison with the experimental data shown in Ref.~\cite{Bierlich:2017vhg}, this model implemented in \pythia event generator~\cite{Sjostrand:2007gs} shows a qualitative agreement in long-range correlation functions.
For more detailed quantitative comparisons, we perform a full analysis of \pythia events with string shoving and calculate quantities which have been measured in experiments.
In the following sections, we describe the analysis procedure and show results using \pythia event generator with different configurations.
The comparison with experimental results and discussion will be followed.

### 2021-06-16 sec_results.tex
first commit

% !TEX root = JKPS_TeX_sample_eps.tex

\section{Results} %discussion?
\label{sec:results}

To have more quantitative comparisons, associated yields of long-range ($2<|\deta|<4$) near-side correlation functions are calculated by integrating one-dimensional correlation functions over the region $|\dphi|<|\dphi_{\rm{min}}|$:
\begin{equation}
   Y^{\rm{assoc}} = \int_{|\Delta \varphi| < |\Delta \varphi_{\mathrm{min}}| } \mathrm{d} \Delta\varphi \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \mathrm{d}\Delta\varphi } - C_{\rm{ZYAM}} \right), 
\end{equation}
where $\dphi_\mathrm{min}$ is the \dphi value from the ZYAM method. 
The left panel of Figure~\ref{fig:ay} shows the associated yield of long-range near-side correlation functions as a function of \Nch for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$, and the multiplicity \Nch is calculated with charged hadrons in $|\eta|<2.4$ and $\pt>0.4~\mathrm{GeV}/c$.
Note that associated yields with initial charged hadrons directly produced from partons are also calculated in the same \Nch bins with final charged hadrons to use same events for associated yields with initial and final hadrons.
The associated yields from \pythia events with the default configuration (red lines) are zero for the entire \Nch range. 
In case of the string shoving model (blue lines), significant amount of associated yields are observed at the entire \Nch range, and it increases with charged hadron multiplicity.
The larger associated yields of initial hadrons than those of final hadrons may indicate that the long-range correlation built from the string shoving smears out through particle decay processes.

\begin{figure}[!h]
\includegraphics[width=0.49\textwidth]{figures/cmsmult.pdf}
\includegraphics[width=0.49\textwidth]{figures/cmspt.pdf}
\caption{Associated yields of long-range near-side correlation functions as a function of \Nch for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$ (left) and as a function of \pt for high multiplicity events (right). The results from \pythia events with the default configuration and the string shoving model are compared with CMS results~\cite{Khachatryan:2015lva}.}
\label{fig:ay}
\end{figure}

The CMS results~\cite{Khachatryan:2015lva} are compared with the string shoving model.
Note that the CMS results are as a function of the number of reconstructed charged particles ($N_\mathrm{ch}^\mathrm{rec}$), the CMS results are shifted along the $x$-axis ($1.15\times N_\mathrm{ch}^\mathrm{rec}$) based on the reported track reconstruction efficiency.
The associated yields of final hadrons from the string shoving model agree with the CMS result in high multiplicity events ($\Nch>120$), but it overestimates associated yields in lower multiplicity events, indicating that there is a long-range correlation from jets in the string shoving model.
For a more detailed comparison, associated yields as a function of \pt in high multiplicity events are shown in the right panel of Figure~\ref{fig:ay}.
Although the associated yields for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$, shown in the plot as a function of \Nch, are comparable between the string shoving model and the CMS result, they show a different \pt dependence.
The associated yields from the string shoving model is higher than the CMS result around $\pt=1~\mathrm{GeV}/c$, and it drops more rapidly for $\pt>2~\mathrm{GeV}/c$.

\begin{figure}[!h]
\includegraphics[width=0.5\textwidth]{figures/mpi2.pdf}
\caption{Associated yields of long-range near-side correlations as a function of $\pt$ in \pythia with the string shoving model for low, high multiplicity events (solid lines), and events without multi-partion interaction (dashed line). }\label{fig:wompi}
\end{figure}

For further investigation on the non-zero associated yields from the string shoving model in low multiplicity events ($N_\mathrm{ch}\lesssim 50$), we generated \pythia events with the string shoving configuration but turning off the multi-parton interaction option, so charged hadrons are mostly produced from hard scattered partons.
In these events where the number of strings is expected to be small, a clear long-range near-side correlation is still observed.
Figure~\ref{fig:wompi} shows associated yields of long-range near-side correlations as a function of \pt for different event classes.
Solid lines are from normal low ($\Nch<20$) and high ($\Nch \geq 120$) multiplicity \pythia events with the string shoving configuration, and the dashed line is from events without multi-parton interaction.
The associated yields in normal low multiplicity events and events without multi-parton interaction are consistent. 
This indicates that the strong shoving model introduces a long-range correlation for particles associated with jets, which is not observed in experimental results.

\begin{figure}[!h]
\includegraphics[width=0.49\textwidth]{figures/cmsmultSub.pdf}
\includegraphics[width=0.49\textwidth]{figures/cmsptSub.pdf}
\caption{Associated yields of long-range near-side correlation functions as a function of \Nch for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$ (left) and as a function of \pt for different multiplicity bins (right). Associated yields in $20\leq\Nch< 30$ are used for the subtraction procedure.}\label{fig:aysub}
\end{figure}

We perform a further analysis to subtract associated yields from jets to have a better comparison with the data.
One simple assumption is that there are two sources of particles, jets and bulk, and there is no correlation between one particle from jets and the other particle from bulk. In such case, long-range two-particle correlation functions after the ZYAM procedure can be expressed as
\begin{align}
    \frac{1}{N_\mathrm{trig}} \frac{\mathrm{d} N_\mathrm{pair}}{\mathrm{d} \dphi} = \frac{1}{N_\mathrm{trig-j} + N_\mathrm{trig-b}} \left( \frac{\mathrm{d} N_\mathrm{pair-j}}{\mathrm{d} \Delta \varphi} + \frac{\mathrm{d} N_\mathrm{pair-b}}{\mathrm{d} \Delta \varphi} \right),
\end{align}
where $N_\mathrm{trig-j}$ ($N_\mathrm{trig-b}$) is the number of trigger particles from jets (bulk), and $N_\mathrm{pair-j}$ ($N_\mathrm{pair-b}$) is the number of pairs between particles from jet (bulk).
The number of pairs from jets ($N_\mathrm{pair-j}$) in a certain high multiplicity bin can be defined as
\begin{align}
    N_\mathrm{pair-j}^\mathrm{HM} = N_\mathrm{pair-j}^\mathrm{LM} N_\mathrm{trig}^\mathrm{LM} \frac{N_\mathrm{evt}^\mathrm{HM}}{N_\mathrm{evt}^\mathrm{LM}},
\end{align}
where $N_\mathrm{evt}$ is the number of events in a certain multiplicity range.
Subtracted associated yields are calculated as
\begin{equation}
   Y^\mathrm{assoc,sub} = \int_{|\Delta \varphi| < |\Delta \varphi_{\mathrm{min}}| } \mathrm{d} \Delta\varphi \left( \frac{1}{\it{N}_{\rm{trig}}^\mathrm{HM}} \frac{ \rm{d}\it{}N_{\rm{pair-b}}^\mathrm{HM} }{ \mathrm{d}\Delta\varphi } \right), 
\end{equation}
where $\it{N}_{\rm{trig}}^\mathrm{HM}$ is the number of trigger particle in high multiplicity events containing trigger particles both from jets and bulk.

Figure~\ref{fig:aysub} shows results from the subtraction method.
Associated yields in $20\leq\Nch<30$ are used for the subtraction based on the distribution of associated yields as a function of $\Nch$ from the string shoving model.
The slope of the increase of associated yields with \Nch changes in $20\leq\Nch<30$.
The jet contribution would be dominating at low multiplicity, so we assume that the associated yields in $20\leq\Nch<30$ are maximum yields from jets.
In addition, no additional multiplicity dependence is considered for yields from jets, as no strong multiplicity dependence is observed in associated yields of short-range ($|\deta|<1$) near-side correlation functions.

The left panel shows associated yields for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$ as a function of \Nch, and the dashed line is a result from the subtraction procedure.
The subtraction procedure shows a larger impact in lower multiplicity, and the subtracted yields shows a similar multiplicity dependence with the CMS results.
In case of associated yields as a function of \pt shown in the right panel, there is no significant change in \pt dependence for the high multiplicity bin.

%%%%%%%%%%%%%%%%%
%%template fit

\begin{figure}[!h]
\includegraphics[width=0.49\textwidth]{figures/TemplateFit_default.pdf}
\includegraphics[width=0.49\textwidth]{figures/TemplateFit_shoving.pdf}
\caption{Template fits to one-dimensional correlation functions in high multiplicity ($100\leq\Nch<110$) \pythia events with the default configuration (left) and the string shoving model (right). The correlation function in low multiplicity ($0\leq\Nch<20$) events are used for the non-flow subtraction procedure.}
\label{fig:templatefit}
\end{figure}

In experiments, long-range two-particle correlations are also quantified with flow coefficients.
A template fit method developed by the ATLAS collaboration~\cite{Aad:2015gqa} to subtract non-flow effects is applied to \pythia events to obtain flow coefficients.
In the template fit method, correlation functions from low multiplicity events are used to estimate non-flow contributions:
\begin{align}
    Y^\mathrm{template}(\dphi) &= Y^\mathrm{ridge}(\dphi) + FY^\mathrm{LM}(\dphi),\nonumber\\
    Y^\mathrm{ridge}(\dphi) &= G \left( 1 + \sum^{\infty}_{n=2} 2 v_{n,n} \cos(n\dphi) \right),
\end{align}
where $F$ is a scale factor for correlation functions in low multiplicity events, and $v_{n,n}$ is a coefficient related to the $n$-th order flow coefficient.
Based on the assumption of factorization of flow coefficients, $v_{n,n}$ from two-particle correlations between trigger particles of $p_\mathrm{T}^{a}$ and associated particles of $p_\mathrm{T}^{b}$ is $v_{n,n}(p_\mathrm{T}^{a}, p_\mathrm{T}^{b}) = v_{n}(p_\mathrm{T}^{a}, p_\mathrm{T}^{b})$.
More details on the template fit method can be found in Ref.~\cite{Aad:2015gqa}.

Figure~\ref{fig:templatefit} shows the example of the template fits to one-dimensional correlation functions of charged hadrons in $0.5<\pt<5.0~\mathrm{GeV}/c$ from high multiplicity \pythia \pp events with the default configuration (left) and the string shoving option (right).
In order to compare with the ATLAS results, slightly different selections are used for multiplicity ($|\eta|<2.5$ and $\pt>0.4~\mathrm{GeV}/c$) and long-range ($2<|\deta|<5$).
In case of the default configuration, the correlation function from high multiplicity events is well described by the scaled correlation function from low multiplicity events.
Hence, the obtained $v_{2,2}$ is very small.
With the string shoving model, a clear near-side structure is seen in the correlation function from high multiplicity events ($Y^\mathrm{HM}(\dphi)$).
However, there is also a near-side peak in the correlation function in low multiplicity events ($Y^\mathrm{LM}(\dphi)$), the scaled $Y^\mathrm{LM}(\dphi)$ take a part of the near-side correlation in $Y^\mathrm{HM}(\dphi)$.
Therefore, one can expect that the obtained $v_{n,n}$ from the template fit method will be smaller than the true $v_{n,n}$ at the same multiplicity range.

\begin{figure}[!h]
\includegraphics[width=0.49\textwidth]{figures/atlasmult.pdf}
\includegraphics[width=0.49\textwidth]{figures/atlaspt.pdf}
\caption{$v_{2,2}$ obtained from the template fit method in \pythia events with the default configuration and the string shoving model, as a function of charged hadron multiplicity (left) and \pt (right). Results from \pythia events are compared with ATLAS results~\cite{Aad:2015gqa}.}
\label{fig:v22}
\end{figure}

%Flow modulations are extracted by subtracting back-to-back jets correlations at away-side in $\Delta\varphi$ correlations function. The subtraction method is implemented to remove back-to-back jets correlations mainly dominating away-side yield. The $\Delta\varphi$ correlations function measured in low-multiplicity event class is used for the subtraction procedure with the assumption that the ridge is negligible in low multiplicity event class, which is also observed in experiments. The template fitting procedure is achieved via
%\begin{eqnarray}
%Y(\Delta\varphi)=G \left\{ 1 + 2v_{2.2}\cos(2\Delta\varphi) + 2v_{3,3}\cos(3\Delta\varphi) \right\} + FY(\Delta\varphi)_{\rm{LM}}\quad.
%\end{eqnarray}
%Flow coefficients are denoted as $v_{2,2}$ and $v_{3,3}$ for elliptic and triangular modulation, respectively. $F$ is introduced to compensate the fact that jet yield measured in high multiplicity event class is higher than in low multiplicity event class, which results in under-subtraction of away-side yield with $F=1$.

Figure~\ref{fig:v22} shows extracted $v_{2,2}$ from the template fit method in \pythia events with the default configuration (red lines) and the string shoving model (blue lines) as a function of charged hadron multiplicity \Nch for charged hadrons in $0.5<\pt<5.0~\mathrm{GeV}/c$ (left) and as a function of \pt for high multiplicity events (right).
The $v_{2,2}$ from \pythia events with the default configuration are close to zero, and this demonstrates the non-flow subtraction method as the previous study in Ref.~\cite{Lim:2019cys}.
The results from \pythia events with the string shoving model show non-zero $v_{2,2}$ values which can be expected from long-range near-side correlation in the correlation functions.
In the comparison of the $v_{2,2}$ with ATLAS results~\cite{Aad:2015gqa}, the $v_{2,2}$ from the string shoving model is significantly lower than ATLAS results.
Based on the similar correlation functions in high multiplicity events shown in Figure~\ref{fig:dphi} and the over-subtraction of non-flow contribution shown in Figure~\ref{fig:templatefit}, the lower $v_{2,2}$ from the string shoving model is mainly due to the non-flow subtraction procedure with $Y^\mathrm{LM}(\dphi)$ showing a near-side peak.

%\begin{figure}[!h]
%\includegraphics[width=0.49\textwidth]{figures/cmsmultSub.pdf}
%\includegraphics[width=0.49\textwidth]{figures/cmsptSub.pdf}
%\caption{(Associated yields of long-range near-side correlation functions as a function of \Nch for charged hadrons in $1<\pt<2~\mathrm{GeV}/c$ (left) and as a function of \pt for different multiplicity bins (right). Associated yields in $20<\Nch\leq 30$ are used for the subtraction procedure.}\label{fig:yasub}
%\end{figure}

### 2021-06-16 sec_summary.tex
first commit

\section{Summary}
\label{sec:summary}

In summary, a quantitative study of long-range two-particle correlations in \pythia events with the string shoving model has been performed.
Clear long-range near-side correlations are observed in the string shoving model, whereas no such structure is seen in \pythia events with the default configuration.
In the comparison with experimental data, the string shoving model qualitatively describes long-range correlations in high multiplicity events.
However, one difference is that long-range near-side correlations exist even at low multiplicity region in the string shoving model.
Due to this fact, the model overestimate associated yields of long-range near-side correlation functions, and flow coefficients ($v_{2,2}$) obtained from the template fit method are lower than
the experimental results.
%expected values with low multiplicity templates of no long-range near-side correlations.
A method to subtract jet correlations in associated yields is tested, and the subtracted yields of charged hadrons for $1<\pt<2~\mathrm{GeV}/c$ shows a similar multiplicity dependence with the experimental results.

### 2021-07-19 paper.tex
Updates

@@
 
-\newcommand{\pp}{\mbox{$pp$}\xspace}
-\newcommand{\pAu}{\mbox{$p$+Au}\xspace}
-\newcommand{\pPb}{\mbox{$p$+Pb}\xspace}
-\newcommand{\pythia}{\textsc{Pythia8}\xspace}
-\newcommand{\deta}{\mbox{$\Delta\eta$}\xspace}
-\newcommand{\dphi}{\mbox{$\Delta\varphi$}\xspace}
-\newcommand{\pt}{\mbox{$p_{\mathrm{T}}$}\xspace}
-\newcommand{\pT}{\mbox{$p_{T}$}\xspace}
-\newcommand{\Nch}{\mbox{$N_\mathrm{ch}$}\xspace}
-\newcommand{\pythiae}{\pythia\ensuremath{~\mathrm{default}}}
-\newcommand{\pythiashoving}{{\pythia\ensuremath{~\mathrm{String}~}}\ensuremath{\mathrm{Shoving}}}
-\newcommand{\sonly}        {\ensuremath{\sqrt{s}}}
+\newcommand{\XGB}{XGBoost}
 
@@
 \setcounter{page}{0}
-\title[]{Exploring the string shoving model in PYTHIA8 \\for collective behaviors in $pp$ collisions}
+\title[]{ Monte-Carlo-based design of a new sampling calorimeter toward the measurement of incident angle }
+
+\author{YoungJun \surname{Kim}}
+\affiliation{Department of Physics, Korea University, Seoul 02841}
 \author{Junlee \surname{Kim}}
@@
 \author{Eun-Joo \surname{Kim}}
-\affiliation{Division of Science Education, Jeonbuk National University, Jeonju 54896}
-\author{SuJeong \surname{Ji}}
-\author{SangHoon \surname{Lim}}
-\email{shlim@pusan.ac.kr}
-%\thanks{Fax: +82-2-554-1643}
-\affiliation{Department of Physics, Pusan National University, Busan 46241}
+\affiliation{Department of Physics education, Jeonbuk National University, Jeonju 54896}
+\author{GeiYoub  \surname{Lim}}
+\affiliation{IPNS/KEK Tshukuba, Jaoan 305-0801}
 
@@
 \begin{abstract}
-Two-particle correlations have been used to study property of a produced medium called Quark-Gluon Plasma (QGP) in relativistic heavy-ion collisions, and a long-range correlation among produced particles has been considered as a strong evidence of strongly interacting QGP.
-Strikingly, clear long-range correlations have been also observed in small collision systems like $pp$ and $p$+$A$ at a wide range of collision energies. 
-%Several theoretical approaches have been proposed, but results in small collision systems have not fully understood yet.
-A model introducing a repulsive force between flux tubes called string shoving can qualitatively describe the long-range near-side correlations in high multiplicity $pp$ collisions. 
-This model implemented in the \pythia Monte Calro event generator allows us to perform detailed study.
-In this work, a full data analysis to calculate associated yields and flow coefficients is performed with \pythia events, and the results are compared with experimental results.
-We find that the string shoving model overestimates long-range near-side correlations particularly in low multiplicity events.
-We also introduce a method to subtract such overestimated correlations in low multiplicity to have a more relevant comparison with the data. 
-%Further study reveals that the string shoving model also generates the repulsive force in jet fragments.
-We also introduce a method to subtract such overestimated correlations and find that the predictions from the string shoving  after the subtraction are more comparable with the experimental results.
+THIS IS ABSTRACT
 
@@
 
-\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
-\keywords{String shoving, Collectivity, $pp$ collision}
+%\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
+%\keywords{String shoving, Collectivity, $pp$ collision}
 \maketitle
 
-\input{sec_intro.tex}
-\pagebreak
-\input{sec_ana.tex}
-\pagebreak
-\input{sec_results.tex}
-\input{sec_summary.tex}
+\section{Motivation}
+\label{sec:mot}
+
+\section{Analysis method}
+\label{sec:ana}
+
+\section{Results}
+\label{sec:res}
+
+\section{Conclusions}
+\label{sec:con}
 
@@
 \begin{acknowledgments}
-%The authors would like to thank for useful discussions and a careful reading of the manuscript. 
-%J. Kim and E.-J. Kim acknowledge support from the... .
-S.J. Ji and S.H. Lim acknowledge support from a 2-Year Research Grant of Pusan
-National University.
-%The authors would like to thank Mr. Kim for helpful discussions and
-%gratefully acknowledge support by MOCIE through National R$\&$D
-%Project for Nano Science and Technology. C. H. C. and W. J. J.
-%acknowledge the financial support by MOE through BK21 fellowships.
 \end{acknowledgments}

### 2021-07-21 paper.tex
Updates

@@
 \setcounter{page}{0}
-\title[]{ Monte-Carlo-based design of a new sampling calorimeter toward the measurement of incident angle }
+\title[]{ A Monte Carlo based design of a new sampling calorimeter toward the measurement of incident angle }
 
@@
 \author{GeiYoub  \surname{Lim}}
-\affiliation{IPNS/KEK Tshukuba, Jaoan 305-0801}
+\affiliation{IPNS/KEK Tsukuba, Japan 305-0801}
 
@@
 \label{sec:mot}
+Electromagnetic (EM) calorimeter is one of major detector in nuclear and particle physics.
 
@@
 \label{sec:ana}
+\subsection{Detector construction}
+
+\subsection{XGBOOST: A toolkit for machine learning}
+\label{sec:anaML}
+Among many packages for machine learning in the high energy physics area~\cite{ATLAS:2020iwa} is the $\XGB$, supporting a scalable tree boosting system~\cite{xgboost:2016}.
+The $\XGB$ package is used to reconstruct the incident angle of incident $\gamma$ particles with deposit energies, which is mainly from the secondary particles of the EM shower, in the each channel.
+The $\XGB$ requires that the number of input data is identical, which is defined as the number of channels in this paper.
+For the $\XGB$ to reconstruct the angle, the training procedure for the $\XGB$ needs to be preceded.
+The training procedure helps the $\XGB$ study how $\gamma$ interacts with the detector and deposits the energy to the each channel with respect to the incident angle for a given $\gamma$ energy.
+From the fact that the training procedure is done with the specific data samples, the $\XGB$ can not reconstruct the angle, which is beyond the sample used for the training.
+Input data, deposit energies for whole channels, are obtained from the calculation of the EM shower in the detector simulated by the Geant4 package.
+Simulations are done with the uniform incident polar angle ($\theta$) distribution from 0 to 50 degree and the uniform azimuthal angle ($\varphi$) distribution from 0 to 360 degree for the training, which makes the $\XGB$ possible to reconstruct events having 0~$<\theta<$~50~degree and 0~$<\varphi<$~360~degree.
+The reconstruction of $\theta$ by the $\XGB$, completing the training procedure, is tested with the fixed $\theta$ and uniform $\varphi$ from 0 to 360 degree.
+The resolution of the reconstruction is defined as the standard deviation of Gaussian function.
 
@@
 \label{sec:res}
+\subsection{Machine learning parameters}
+
+\subsection{Inspection of detector dimension}
 
 \section{Conclusions}
+
 \label{sec:con}

### 2021-07-28 paper.tex
updates

@@
 \setcounter{page}{0}
-\title[]{ A Monte Carlo based design of a new sampling calorimeter toward the measurement of incident angle }
+\title[]{ A Monte Carlo based new sampling calorimeter toward the measurement of $\gamma$ incident angle }
 
@@
 \begin{abstract}
-THIS IS ABSTRACT
-
+SHORT MOTIVATION HERE. 
+We present the studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
+The Geant4 and the $\XGB$ packages are used to simulate interactions of electromagnetic showers with detector materials and to reconstruct the incident angle with the machine learning method.
+The sandwich-type sampling calorimeter is configured with 5-mm-thick scintillator strips and 1-mm-thick lead plates.
+The sampling fraction and the Moliere radius of the detector are xxx and xxx, respectively.
+We find that the configuration with 15-mm-wide scintillator strips is found to provide xxx resolution and the front part of the detector as much as 4.6-radiation-length thickness provides the same resolution with xxx inefficiency.
 \end{abstract}
@@
 \label{sec:mot}
-Electromagnetic (EM) calorimeter is one of major detector in nuclear and particle physics.
+Electromagnetic calorimeter (EM-Cal) has played an important role in nuclear and particle physics especially to detect photon[].
+The most important property of the detector is good energy and timing resolution, and various crystals has been developed for the purpose[].
+On the other hand, the sampling calorimeter consisting of alternating converter generating shower particles and counter measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
 
-\section{Analysis method}
+Due to a fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution.
+This fluctuation becomes not so important for high energy photons owing to large number of shower particles.
+When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.
+There are many efforts to develop new types of calorimeter and a fine-segmented sampling calorimeter is in the line[].
+
+The sampling calorimeter enable us to measure not only energy but also incident angle of photon.
+Considering a stochastic process in shower generation, there is a certain limitation of detection resolution.
+Also, the effect of sampling fluctuation is matter in medium energy photons in range 100 MeV to few GeV photons.
+Even though these drawbacks, there is an experiment to have quite strong motivation on developing the calorimeter able to measure incident angle.
+
+KOTO experiment, being performed at the J-PARC in Japan, aims at searching for the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay.
+This decay is very clean in theoretical calculation[] and large potential to access the new physics beyond the Standard Model[].
+However, current experimental sensitivity is still far from the SM expectation[] mainly due to its extremely small branching fraction and very weak kinematic condition to define a signature of the decay.
+
+Considering negligible detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate which is reconstructed by detecting two photons generated from prompt decay of the $\pi^0$.
+The KOTO utilizes un-doped cesium iodide (CsI) crystals as an EM-Cal to measure the photons.
+An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons[].
+
+In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at beam axis.
+This reconstruction is totally failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
+ In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement.
+By requiring a consistency between two vertices reconstructed from different observables, we can select genuine single $\pi^0$ decay rejecting various kinds of wrong pair of photons such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on.
+It also enable us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis.
+We can expect similar rejection against $K_L \rightarrow \gamma \gamma$ decays when the $K_L$ deviate form the beam center due to scattering.
+
+For the angle measurement of photon, we should get an information about the spatial profile of shower particles generated in the electromagnetic calorimeter.
+This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions.
+A sampling calorimeter consisting of alternating lead sheet and strips of plastic scintillator could be a good candidate of the calorimeter as describe in this paper.
+
+\section{method}
 \label{sec:ana}
 \subsection{Detector construction}
+We constructed a prototype sampling electromagnetic calorimeter with alternative stacking of thin Pb sheets and scintillator strips.
+A Pb sheet has a dimension of 50 cm (w) $\times$ 50 cm (l) $\times$ 1 mm (t).
+And a single layer of scintillator plate consists of 25 long scintillator segments, and each segment has a dimension of 2 cm (w) $\times$ 50 cm (l) $\times$ 5 mm (t).
+The full geometry consists of 105 layers  which is corresponding to 20 $X_0$.
 
@@
 The training procedure helps the $\XGB$ study how $\gamma$ interacts with the detector and deposits the energy to the each channel with respect to the incident angle for a given $\gamma$ energy.
-From the fact that the training procedure is done with the specific data samples, the $\XGB$ can not reconstruct the angle, which is beyond the sample used for the training.
 Input data, deposit energies for whole channels, are obtained from the calculation of the EM shower in the detector simulated by the Geant4 package.
-Simulations are done with the uniform incident polar angle ($\theta$) distribution from 0 to 50 degree and the uniform azimuthal angle ($\varphi$) distribution from 0 to 360 degree for the training, which makes the $\XGB$ possible to reconstruct events having 0~$<\theta<$~50~degree and 0~$<\varphi<$~360~degree.
+Simulations are done with the uniform incident polar angle ($\theta$) distribution from 0 to 50 degree and the uniform azimuthal angle ($\varphi$) from 0 to 360 degree for the training, which makes the $\XGB$ possible to reconstruct events having 0~$<\theta<$~50~degree and 0~$<\varphi<$~360~degree.
 The reconstruction of $\theta$ by the $\XGB$, completing the training procedure, is tested with the fixed $\theta$ and uniform $\varphi$ from 0 to 360 degree.
-The resolution of the reconstruction is defined as the standard deviation of Gaussian function.
+
+%The resolution of the reconstruction is defined as the standard deviation of Gaussian function around $\pm$~2 times standard deviations from the peak of the distribution.
 
@@
 \label{sec:res}
-\subsection{Machine learning parameters}
 
-\subsection{Inspection of detector dimension}
+\subsection{Detector property}
+
+\subsection{Parameterization for machine learning setting}
+The configuration of the $\XGB$ can be defined with five parameters, described in Tab.~\ref{tab:XgbPar}.
+The parameters are selected as one providing better angular resolution.
+It is found that the Max.
+depth mostly affects the angular resolution, and the resolution is not enhanced for Max.
+depth~$>$~15 any more.
+It is also worth mentioning that the N\_estimators larger than 1000 does not provide better resolution with the Max.
+depth~=~15.
+The angular resolution with described parameters is found to be about 1.3~degree, as shown in fig.(def).
+
+\begin{table}[hbt!]
+\centering
+\caption{Parameterization of the $\XGB$}
+\begin{tabular}{ccc}
+\hline 
+Parameter & Function & Suggested value \\ \hline 
+N\_estimators & The number of decision trees & 1000 \\  
+Max. depth & Possible maximum depth of tree structure & 15 \\ 
+Subsample & Fraction of total data used for a single decision & 1 \\ 
+Learning rate & Step length for calculation & 0.08 \\ 
+Gamma & Requirement on minimum loss function & 0 \\ 
+\hline
+\end{tabular}
+\label{tab:XgbPar}
+\end{table}
+
+\subsection{Detector dimension}
+The performance of the detector is tested with different detector dimensions.
+Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000.
+It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths.
+
+The angle reconstruction is tested only with signals in front layers.
+Usages of front-layer signals are applied to the data sample for training and test procedures at the same time.
+The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides identical resolution with one from full geometry, while possessing about xxx\% inefficiency due to no responses in the front region.
+As a results of the inefficiency, A delta peak can be seen in Fig.(fl).
+This peak can be rejected with the application of the total energy threshold (10~MeV in Fig.(fl)) in the front region.
+
+The energy threshold and the attenuation effects are studied.
+The attenuation effect is applied to the deposit energies in each channel with the attenuation function~\cite{Murayama:2020mcp}.
+The energy threshold is applied to the all channels after the application of the attenuation effect.
+The coefficients of the attenuation effect are thought to be same as~\cite{Murayama:2020mcp}, and the applied threshold is 0.5~MeV.
+These responses are applied to the data sample for the training and test procedure.
+The angular resolution is found to be consistent with the resolution without such effects.
+
+The incident angle and the incident energy dependencies of the angle reconstruction are studied with the same configuration and requirements mentioned before. It is found that
 

### 2021-07-28 paper.tex
Updates from Overleaf

@@
 
-%The resolution of the reconstruction is defined as the standard deviation of Gaussian function around $\pm$~2 times standard deviations from the peak of the distribution.
-
 \section{Results}
@@
 depth~=~15.
-The angular resolution with described parameters is found to be about 1.3~degree, as shown in fig.(def).
+The angular resolution of the reconstruction is defined as the standard deviation of Gaussian function, whose parameters are evaluated by fitting the reconstructed angle distribution.
+The angular resolution with described parameters is estimated to be about 1.3~degree, as shown in fig.(def).
 

### 2021-07-29 paper.tex
updates

@@
 The angular resolution of the reconstruction is defined as the standard deviation of Gaussian function, whose parameters are evaluated by fitting the reconstructed angle distribution.
-The angular resolution with described parameters is estimated to be about 1.3~degree, as shown in fig.(def).
+Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ distribution with respect to each incident $\theta$ with described training parameters.
+The angular resolution for all $\theta$ is estimated to be about 1.3~degree.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
+\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution.
+The standard deviation of all Gaussian functions are estimated to be about 1.3 degree.}
+\label{fig:angle_reco_def}
+\end{figure}
 

### 2021-07-30 paper.tex
updates

@@
 \subsection{Detector dimension}
+\begin{figure}[!hbt]
+\includegraphics[width=0.58\textwidth]{figures/Fig2_reco_Width_width.pdf}
+\caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
+\label{fig:angle_reco_width}
+\end{figure}
+
 The performance of the detector is tested with different detector dimensions.
 Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000.
-It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths.
+Figure~\ref{fig:angle_reco_width} shows the angular resolution of the reconstruction as a function of the scintillator strip width with the 5-mm step.
+It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths, and the configuration with larger strip size than 15 mm does not provide improved resolution.
+Based on this, The width of the strip is determined to be 15 mm.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_hist.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_graph.pdf}
+\caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%  }
+\label{fig:angle_reco_layer}
+\end{figure}
 
@@
 Usages of front-layer signals are applied to the data sample for training and test procedures at the same time.
-The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides identical resolution with one from full geometry, while possessing about xxx\% inefficiency due to no responses in the front region.
-As a results of the inefficiency, A delta peak can be seen in Fig.(fl).
-This peak can be rejected with the application of the total energy threshold (10~MeV in Fig.(fl)) in the front region.
+The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides the identical resolution with one from full geometry.
+The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region.
+The inefficiency for (4.6$X_{0}$) is estimated to be 5.8\%.
+Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The reconstructed $\theta$ without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of not enough information to reconstruct $\theta$, And this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold.
+The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
 

### 2021-07-30 paper.tex
updates

@@
 \begin{abstract}
-SHORT MOTIVATION HERE. 
-We present the studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
+We present studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
 The Geant4 and the $\XGB$ packages are used to simulate interactions of electromagnetic showers with detector materials and to reconstruct the incident angle with the machine learning method.
@@
 
-The energy threshold and the attenuation effects are studied.
-The attenuation effect is applied to the deposit energies in each channel with the attenuation function~\cite{Murayama:2020mcp}.
-The energy threshold is applied to the all channels after the application of the attenuation effect.
-The coefficients of the attenuation effect are thought to be same as~\cite{Murayama:2020mcp}, and the applied threshold is 0.5~MeV.
-These responses are applied to the data sample for the training and test procedure.
-The angular resolution is found to be consistent with the resolution without such effects.
+\begin{figure}[!hbt]
+\includegraphics[width=0.8\textwidth]{figures/Fig4_reco_ecut.pdf}
+\caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%  }
+\label{fig:angle_reco_ecut}
+\end{figure}
+
+The detector responses on the energy deposit are studied.
+The attenuation effect, smearing effect due to the photon statistics, and energy threshold for each channel are considered.
+The attenuation effect is applied to the deposit energies in each channel with the attenuation function, described in~\cite{Murayama:2020mcp}.
+The coefficients for the attenuation effect are also obtained from~\cite{Murayama:2020mcp}.
+The energy deposit after the attenuation effect is smeared with respect to the number of photon statistics.
+The number of photons ($\rm{n.p.e}$) is assumed to be 50 for 1 MeV deposit.
+The standard deviation ($\sigma(E)$) for the smearing can be defined as
+\begin{eqnarray}
+\sigma(E) = \sqrt{E/\rm{n.p.e}}
+\end{eqnarray}
+After the smearing attenuated energy deposit, the energy threshold (0.5 MeV) is applied to the all channels.
+These effects are applied to the test samples and the training samples, and the training is done with and without applying such effects and the test is done with applying the effects.
+Figure~\ref{fig:angle_reco_ecut} shows that the angular resolution is found to be consistent regardless of applying such effects.
 

### 2021-09-30 Sec2.tex
updates

\section{Method}
We started the study with a setup of sampling calorimeter consisting of alternating lead sheet and strips of the plastic scintillator as shown in Fig.~\ref{fig:det_conf}. The electromagnetic shower mainly generated at the lead sheet (passive component) due to its short radiation length ($X_0 = 5.6~{\rm mm})$ and the information of the shower particles is obtained by using the scintillator (active  component). The thickness of lead is 1 mm and scintillator is 5 mm, respectively. The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm. By arranging the strips in X- and Y-direction alternatively along Z-direction. The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.  With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them. The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully.

\begin{figure}[!hbt]
%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}

\caption{ The first trial of detector setup for simulation study on angle measurement. It is a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. }
\label{fig:det_conf}
\end{figure}

The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver. xxx) with the standard EM sub-packages (URL: https://geant4.web.cern.ch/node/1828). 
${\it I will describe the coordinator}$
%The contribution of the hadronic interaction is taken into account with $\rm{FTFP\_BERT}$ package. The materials used in detector construction are selected from the Geant4 NIST material database: $\rm{G4\_Pb}$ for the lead and $\rm{G4\_PLASTIC\_SC\_VINYLTOLUENE}$ for the scintillator material.

In order to reconstruct the incident angle of the gamma, we used the $\XGB$, which is one of the machine learning packages supporting a scalable tree boosting system~\cite{xgboost:2016}. Input data for the $\XGB$ are deposit energies on each scintillator strip by the generated shower particles. It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical. As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.

There are five hyperparameters which can be set by user, and their values are selected to provide the better angular resolution as described in tab.~\ref{tab:XgbPar}. Among these hyperparameters, the Max. depth rapidly improves the angular resolution with increasing its value until 100. The N\_estimators also improves the angular resolution with increasing its number up to 1,000 and N\_estimators larger than 1000 does not change the resolution. Its optimal condition becomes 1000 with the Max. depth is 100.

\begin{table}[hbt!]
\centering
\caption{Parameterization of the $\XGB$}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 1000 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
\end{table}

For the training procedure, gammas are generated uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle ($\varphi$). The performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees.

### 2021-09-30 paper.tex
updates

--- 2021-07-29 paper.tex
@@
 \setcounter{page}{0}
-\title[]{ A Monte Carlo based new sampling calorimeter toward the measurement of $\gamma$ incident angle }
+\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle }
 
 \author{YoungJun \surname{Kim}}
+\author{Jung Keun \surname{Ahn}}
 \affiliation{Department of Physics, Korea University, Seoul 02841}
@@
 \author{Eun-Joo \surname{Kim}}
+\email{ejkim@jbnu.ac.kr}
 \affiliation{Department of Physics education, Jeonbuk National University, Jeonju 54896}
@@
 \begin{abstract}
-SHORT MOTIVATION HERE. 
-We present the studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
+We present studies on detector configuration to obtain angular information for gammas of energies in a range from hundred MeV to few GeV.
+For the angular measurement, we need to obtain profiles of energy deposit along to both of the longitudinal and transverse directions, which could be realized by using the sampling calorimeter.
+The sampling calorimeter consists of alternating 1-mm-thick lead sheets producing the electromagnetic shower and strips of 5-mm-thick plastic scintillator measuring the energy deposit by the shower particles.
+The strips are arranged along to the alternating horizontal and vertical directions to give transverse profile by combining the both directions at a given longitudinal position.
+In this studies, we used the GEANT4 to simulate energy deposit to the individual strips of the calorimeter, and the $\XGB$ package to obtain the incident angle from the energy deposits.
+
+The angular resolution weakly depends on the width of the strips up to 25mm and becomes worse rapidly with increasing the width.
+We found the proper detector thickness for the angular measurement is around 5-radiation (5 Xo) and the expected angular resolution becoms to be 1.3 degrees with 25-mm width of the strips.
+This resolution dose not depends on the incident gamma upto 30 degrees, and its energy dependency is expressed as $p_0 + P_1 / \sqrt{E_\gamma}$.
+(p0, p1 will be replaced by the obtained numbers)
+
+%We present studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
 The Geant4 and the $\XGB$ packages are used to simulate interactions of electromagnetic showers with detector materials and to reconstruct the incident angle with the machine learning method.
-The sandwich-type sampling calorimeter is configured with 5-mm-thick scintillator strips and 1-mm-thick lead plates.
+The sampling calorimeter is configured with alternating 5-mm-thick scintillator strips and 1-mm-thick lead plates.
 The sampling fraction and the Moliere radius of the detector are xxx and xxx, respectively.
-We find that the configuration with 15-mm-wide scintillator strips is found to provide xxx resolution and the front part of the detector as much as 4.6-radiation-length thickness provides the same resolution with xxx inefficiency.
+We find that the configuration with 15-mm-wide scintillator strips provides 1.3~deg resolution, and the same resolution is expected with only front part of the detector in 4.6-radiation-length in thickness with 5.8\% inefficiency.
+Furthermore, the incident angle dependency of the angular resolution is found to be consistent, and the incident energy dependency is found to be inversely proportional.
 \end{abstract}
@@
 \label{sec:mot}
-Electromagnetic calorimeter (EM-Cal) has played an important role in nuclear and particle physics especially to detect photon[].
-The most important property of the detector is good energy and timing resolution, and various crystals has been developed for the purpose[].
-On the other hand, the sampling calorimeter consisting of alternating converter generating shower particles and counter measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
+The electromagnetic calorimeter (EM-Cal) has played an important role in experimental studies of the nuclear and particle physics.  
+% experiments specially to detect gamma. 
+Various crystals have been developed for better energy and timing resolution of the calorimeter so far~\cite{Calorimeter}.
+%The most important properties of the detector are good energy and timing resolution, and various crystals has been developed for the purpose[] .
+On the other hand, the sampling calorimeter tends to replace the crystal calorimeter in large-scale high energy experiment mainly due to its cost-effectiveness.
+The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that detect shower particles.
 
-Due to a fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution.
-This fluctuation becomes not so important for high energy photons owing to large number of shower particles.
-When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.
-There are many efforts to develop new types of calorimeter and a fine-segmented sampling calorimeter is in the line[].
+Since the energy deposit into the passive convert can not be measured, its fluctuation called as sampling fluctuation determines the energy resolution of the sampling calorimeter which is generally worth than that of the crystal one.
+%mainly determined by the  which causes a limitation of energy resolution,  
+%Even though the energy deposit in the passive converter is not detected which is related to the 
+%measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
+%Due to the fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution. 
+However, the shower generation becomes more effective by selecting freely among the large numbers of candidate.
+The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}.
+%In addition, the fluctuation becomes not so important for high energy gammas owing to large number of shower particles.
+%When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.
+%There are many efforts to develop new types of calorimeter, and a fine-segmented sampling calorimeter is in the line[].
 
-The sampling calorimeter enable us to measure not only energy but also incident angle of photon.
-Considering a stochastic process in shower generation, there is a certain limitation of detection resolution.
-Also, the effect of sampling fluctuation is matter in medium energy photons in range 100 MeV to few GeV photons.
-Even though these drawbacks, there is an experiment to have quite strong motivation on developing the calorimeter able to measure incident angle.
+A layer structure of the sampling calorimeter enables us to measure the profiles of shower particles in layer by layer along to the shower development.
+That is, we can estimate the direction of incident gamma by connecting the center of each profile.
+We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV.
+%measure not only energy but also incident angle of photon.
+Considering a stochastic process in shower generation, there is a certain limitation of the detection resolution.
+Also, the effect of the sampling fluctuation is a matter in medium energy photons in range 100 MeV to few GeV photons.
+Even though the sampling fluctuation makes limitation on the energy resolution of the calorimeter in this energy range, there is an experiment to have a motivation on developing a detector configuration enable to measure the incident direction.
 
-KOTO experiment, being performed at the J-PARC in Japan, aims at searching for the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay.
-This decay is very clean in theoretical calculation[] and large potential to access the new physics beyond the Standard Model[].
-However, current experimental sensitivity is still far from the SM expectation[] mainly due to its extremely small branching fraction and very weak kinematic condition to define a signature of the decay.
+The KOTO experiment, being performed at the J-PARC in Japan, aims at searching for the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay~\cite{KOTOproposal}.
+This decay is very clean in theoretical calculatio and has a large potential to access the new physics beyond the Standard Model~\cite{NewPhys}.
+However, current experimental sensitivity is still far from the SM expectation mainly due to its extremely small branching fraction and very weak kinematic condition to define a signature of the decay\cite{KOTO}.
 
-Considering negligible detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate which is reconstructed by detecting two photons generated from prompt decay of the $\pi^0$.
-The KOTO utilizes un-doped cesium iodide (CsI) crystals as an EM-Cal to measure the photons.
-An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons[].
-
-In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at beam axis.
-This reconstruction is totally failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
- In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement.
-By requiring a consistency between two vertices reconstructed from different observables, we can select genuine single $\pi^0$ decay rejecting various kinds of wrong pair of photons such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on.
-It also enable us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis.
+Considering negligible detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$.
+The KOTO utilizes undoped Cesium Iodide (CsI) crystals as an EM-Cal to measure the gamma~\cite{CsI}.
+%An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons.
+For the reconstruction, we need an assumption that the two gammas are generated from a single $\pi^0$ decaying at the beam axis in addition to the detection variables.
+This means that we would get a wrong $\pi^0$ in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
+With a new information, incident angle, we can judge a validity of the reconstructed $\pi^0$.
+%In order to reconstruct a  $\pi^0$ from obtained information of the two gammas 
+%In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at the beam axis.
+This reconstruction would be failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
+% In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement.
+By requiring a consistency between two vertices reconstructed with different observables, we can select genuine single $\pi^0$ decay rejecting wrong pairs due to various sources such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on.
+It also enables us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis.
 We can expect similar rejection against $K_L \rightarrow \gamma \gamma$ decays when the $K_L$ deviate form the beam center due to scattering.
 
-For the angle measurement of photon, we should get an information about the spatial profile of shower particles generated in the electromagnetic calorimeter.
+%For the angle measurement of gamma, we should get information about the spatial profile of shower particles generated in the EM-Cal.
 This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions.
-A sampling calorimeter consisting of alternating lead sheet and strips of plastic scintillator could be a good candidate of the calorimeter as describe in this paper.
+We studied a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator for the angular measurement of incident gamma.
+%could be a good candidate of the calorimeter as describe in this paper.
+In the following section, the configuration of detector and the reconstruction of $\gamma$-incident angle will be described.
+The discussion on the optimal configuration and its expected performance will be followed.
 
-\section{method}
-\label{sec:ana}
-\subsection{Detector construction}
-We constructed a prototype sampling electromagnetic calorimeter with alternative stacking of thin Pb sheets and scintillator strips.
+\section{Method}
+We started the study with a setup of sampling calorimeter consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter.
+% as shown in Fig.~\ref{fig:det_conf}.
+The electromagnetic shower mainly generated at the lead sheet (passive component) due to its short radiation length ($X_0 = 5.6~{\rm mm})$ and the information of the shower particles is obtained by using the scintillator (active  component).
+The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
+The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}.
+The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
+With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them.
+The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully.
+The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver.
+xxx) with the standard EM sub-packages ~\cite{GEANT4}.
+
+\begin{figure}[!hbt]
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
+\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
+
+\caption{ The first trial of detector setup for simulation study on angle measurement. It is a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. }
+\label{fig:det_conf}
+\end{figure}
+
+%{\it I will describe the coordinator and the gamma enter to the center of strips}
+%The contribution of the hadronic interaction is taken into account with $\rm{FTFP\_BERT}$ package.
+The materials used in detector construction are selected from the Geant4 NIST material database: $\rm{G4\_Pb}$ for the lead and $\rm{G4\_PLASTIC\_SC\_VINYLTOLUENE}$ for the scintillator material.
+
+In order to reconstruct the incident angle of the gamma, we used the $\XGB$, which is one of the popular machine learning packages supporting a scalable tree boosting system~\cite{xgboost:2016}.
+Input data for the $\XGB$ are deposit energies on each scintillator strip by the generated shower particles.
+It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical.
+As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.
+
+There are five hyper parameters which can be optimized by user, and their values are selected to provide the best angular resolution as described in table~\ref{tab:XgbPar}.
+Among the parameters, the Max.
+depth rapidly improves the angular resolution with increasing its value until 15.
+The N\_estimators also improves the angular resolution with increasing its number, which is correlated to the value of the Max.
+depth.
+Its optimal condition becomes 1000 when the Max.
+depth is 15.
+
+\begin{table}[hbt!]
+\centering
+\caption{Hyperparameters of the $\XGB$}
+\begin{tabular}{cccc}
+\hline 
+Parameter & Function & Default value & Used value \\ \hline 
+N\_estimators & The number of decision trees & N.A. & 1000 \\  
+Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
+Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
+Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
+Gamma & Requirement on minimum loss function & 0 & 0 \\ 
+\hline
+\end{tabular}
+\label{tab:XgbPar}
+\end{table}
+
+For the training procedure, gammas are generated uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle.
+The performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees.
+
+%\input{Sec2.tex}
+%\section{method}
+%\label{sec:ana}
+
+%\subsection{Geant4 simulation}
+%In this paper, the photon shower and corresponding detector responses, the prerequisites for the machine learning inputs, are simulated based on the Geant4 framework.
+Among several physics packages, the $\rm{FTFP\_BERT}$ physics package is used for electromagnetic and hadronic interactions as it is generally recommended for the high energy physics calorimetry.
+
+%The materials used in detector construction are selected from the Geant4 NIST material database: $\rm{G4\_Pb}$ for the lead and $\rm{G4\_PLASTIC\_SC\_VINYLTOLUENE}$ for the scintillator material.
+
+%\subsection{Detector construction}
+%We constructed a prototype sampling electromagnetic calorimeter with alternative stacking of thin Pb sheets and scintillator strips.
 A Pb sheet has a dimension of 50 cm (w) $\times$ 50 cm (l) $\times$ 1 mm (t).
@@
 The full geometry consists of 105 layers  which is corresponding to 20 $X_0$.
+In order to investigate the detector properties and test the reconstruction performance of the indicent angle of $\gamma$, we generated $\gamma$ beam data samples with several incident angles and energies.
+%In this study, we utilized a physics package $FPFT\_BERT$ for the hadronic and electromagnetic interactions
+%We started the study with a setup of sampling calorimeter consisting of alternating lead sheet and strips of plastic scintillator as shown in Fig.~\ref{fig:det_conf}.
+The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
+The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm.
+By arranging the strips in X- and Y-direction alternatively along Z-direction.
+The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
+With the configuration, we can get shower profiles in X-Z and Y-Z planes in turn, and estimate the incident angle from them.
+The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully.
 
-\subsection{XGBOOST: A toolkit for machine learning}
-\label{sec:anaML}
-Among many packages for machine learning in the high energy physics area~\cite{ATLAS:2020iwa} is the $\XGB$, supporting a scalable tree boosting system~\cite{xgboost:2016}.
-The $\XGB$ package is used to reconstruct the incident angle of incident $\gamma$ particles with deposit energies, which is mainly from the secondary particles of the EM shower, in the each channel.
-The $\XGB$ requires that the number of input data is identical, which is defined as the number of channels in this paper.
+%\begin{figure}[!hbt]
+%%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
+
+%\caption{ The first trial of detector setup for simulation study on angle measurement. It is a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. }
+%\label{fig:det_conf}
+%\end{figure}
+
+%\subsection{Electromagnetic shower Generation}
+%\subsection{Properties of electromagnetic shower (EM shower)}
+%We generated the EM shower generated inside the detector with GEANT4, which provides reliable results for them polish-up later).
+
+%\subsection{Properties of electromagnetic shower (EM shower)}
+
+%In general, the less the photon shower develops in the transverse direction, the more separable the photon clusters, and the higher the visible ratio, the better the energy resolution.
+However, these properties are incompatible as they have strong inverse correlation.
+For the trade-off configuration, we investigated the Molière radius and the visible ratio with several configurations.
+
+% 어떤 configuration, energy? 등등
+% 2.5, 5, 10, 15, 20 mm for scint., 0.5, 1, 2 mm for lead 1GeV gamma
+% For energy resolution, 100 MeV step 100MeV ~ 2GeV gamma
+
+%\subsection{Backsplash}
+% backsplash particle이 veto signal을 만들어 accidental event loss를 만든다.
+% incident photon의 에너지와 각도를 바꿔가며 front surface로 빠져나오는 backsplash particle의 개수를 카운팅
+% 1개 이상의 backsplash particle이 있으면 veto에 counting
+
+%\subsection{XGBOOST: A toolkit for machine learning}
+%\label{sec:anaML}
+%Among many packages for machine learning in the high energy physics area~\cite{ATLAS:2020iwa}, we used the $\XGB$, supporting a scalable tree boosting system~\cite{xgboost:2016}.
+The $\XGB$ package is used to reconstruct the incident angle of incident $\gamma$ particles with deposit energies in the each channel, where secondary particles of the EM shower raise signals.
+Input data for the $\XGB$ are deposit energies for whole channels including zero-energies to tally with the requirement that the number of input data should be identical.
 For the $\XGB$ to reconstruct the angle, the training procedure for the $\XGB$ needs to be preceded.
 The training procedure helps the $\XGB$ study how $\gamma$ interacts with the detector and deposits the energy to the each channel with respect to the incident angle for a given $\gamma$ energy.
-Input data, deposit energies for whole channels, are obtained from the calculation of the EM shower in the detector simulated by the Geant4 package.
 Simulations are done with the uniform incident polar angle ($\theta$) distribution from 0 to 50 degree and the uniform azimuthal angle ($\varphi$) from 0 to 360 degree for the training, which makes the $\XGB$ possible to reconstruct events having 0~$<\theta<$~50~degree and 0~$<\varphi<$~360~degree.
@@
 
-\subsection{Detector property}
+\subsection{Properties of generated shower}
+% moliere rad, visible ratio graph
+% energy resolution (+as a function of E)
+% gamma beam energy에 따라 backsplash가 만드는 event veto
+% + incident angle에 따라?
+Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
+%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$). 
+Its longitudinal projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
+can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
+\begin{equation}
+    F(E,t)=E_0\cdot (bt)^{a-1}e^{-bt}/\Gamma(a),
+    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
+\end{equation}
+where t is the z-position in radiation length. It is natural that the distributions on converter and counter are identical. 
+%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
+%\begin{equation}
+    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
+%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
+%\end{equation}
+%or
+%\begin{equation}
+    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
+%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
+%\end{equation}
+%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.
 
-\subsection{Parameterization for machine learning setting}
-The configuration of the $\XGB$ can be defined with five parameters, described in Tab.~\ref{tab:XgbPar}.
+On the other hand, the transverse shower spread is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers as shown in Figure XXX.
+This distribution is expressed by the Molière radius defined as
+\begin{equation}
+\rho_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
+\end{equation}
+where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
+For the sampling calorimeter consisting of different materials, let us define the Molière radius as the radius of cylinder containing 90\% of shower energy.
+As shown in Figure xxx, the test model (1-mm lead and 5-mm scintillator) shows $\rho_M=70$ mm in average which changes with the shower depth.
+That is, we can expect an improvement on separating two gammas closely incident to the calorimeter. We will study on this subject and not treat in this paper.
+%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal
+
+The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
+\begin{equation}
+R = { \frac{E_{act}} {E_{act}+E_{pas}}},
+\end{equation}
+where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively.
+This visible ratio is roughly given by a ratio of material budget between the converter and the counter.
+%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
+%by thickness of the converter.
+It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter.
+As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon.
+However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers.
+Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too).
+When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX.
+This is because the number of low energy electrons and positrons penetrating the lead sheet.
+Even though the small improvement on the visible ratio, the energy resolution improved greatly with the thinner layer.
+%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.
+
+\begin{figure}[!hbt]
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileZ.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileXZ.pdf}
+\caption{Profile of the EM shower in Z axis(left) and X-Z plane(right)  }
+\label{fig:EMshower}
+\end{figure}
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/3.2/moliere_radius.pdf}
+\includegraphics[width=0.48\textwidth]{figures/3.2/visible_ratio.pdf}
+\caption{Dependence of Moliere radius(left) and visible ratio(right) on the thickness of scintillators}
+\label{fig:moliere_vis}
+\end{figure}
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
+\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
+\caption{The dependence of the energy resolution on the thickness of scintillators(left) and the incident energy of $\gamma$(right)}
+\label{fig:energy_res}
+\end{figure}
+
+%\subsection{Machine learning configuration}
+%The configuration of the $\XGB$ can be organized with five parameters, described in Tab.~\ref{tab:XgbPar}.
 The parameters are selected as one providing better angular resolution.
@@
 depth~$>$~15 any more.
-It is also worth mentioning that the N\_estimators larger than 1000 does not provide better resolution with the Max.
+It is also worth mentioning that configurations with N\_estimators larger than 1000 do not provide better resolution with the Max.
 depth~=~15.
@@
 Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ distribution with respect to each incident $\theta$ with described training parameters.
-The angular resolution for all $\theta$ is estimated to be about 1.3~degree.
+The angular resolution for all $\theta$ is estimated to be 1.3~degree.
+
+%\begin{figure}[!hbt]
+%\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
+%\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution.
+The standard deviation of all Gaussian functions are estimated to be 1.3 degree.}
+%\label{fig:angle_reco_def}
+%\end{figure}
+
+%\begin{table}[hbt!]
+%\centering
+%\caption{Parameterization of the $\XGB$}
+%\begin{tabular}{cccc}
+%\hline 
+%Parameter & Function & Default value & Used value \\ \hline 
+%N\_estimators & The number of decision trees & N.A. & 1000 \\  
+%Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
+%Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
+%Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
+%Gamma & Requirement on minimum loss function & 0 & 0 \\ 
+%\hline
+%\end{tabular}
+%\label{tab:XgbPar}
+%\end{table}
+
+%\subsection{Detector dimension}
+\subsection{Angle reconstruction using Machine Learning}
+
+Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ obtained from the test samples, which are generated for fixed angles in range of $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
+The number of generated gammas is $10^5$ and their energy is 1 GeV.
+The $\XGB$ correctly reconstructs $\theta=$ with a typical resolution as 1.2 degrees.
+There is no significant difference according to the incident angle.
 
@@
 \caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution.
-The standard deviation of all Gaussian functions are estimated to be about 1.3 degree.}
+The standard deviation of all Gaussian functions are estimated to be 1.3 degree.}
 \label{fig:angle_reco_def}
@@
 
-\begin{table}[hbt!]
-\centering
-\caption{Parameterization of the $\XGB$}
-\begin{tabular}{ccc}
-\hline 
-Parameter & Function & Suggested value \\ \hline 
-N\_estimators & The number of decision trees & 1000 \\  
-Max. depth & Possible maximum depth of tree structure & 15 \\ 
-Subsample & Fraction of total data used for a single decision & 1 \\ 
-Learning rate & Step length for calculation & 0.08 \\ 
-Gamma & Requirement on minimum loss function & 0 \\ 
-\hline
-\end{tabular}
-\label{tab:XgbPar}
-\end{table}
+\begin{figure}[!hbt]
+\includegraphics[width=0.58\textwidth]{figures/Fig2_reco_Width_width.pdf}
+\caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
+\label{fig:angle_reco_width}
+\end{figure}
 
-\subsection{Detector dimension}
-The performance of the detector is tested with different detector dimensions.
+With the narrower width of the scintillator strips, we may get more precise information about the shower shape.
+In order to find detector configuration providing the best angular resolution, we produced gamma events with changing the width of strips from 5 mm to 35 mm in 5 mm steps.
+As shown in Fig.~\ref{fig:angle_reco_width}, the narrower width doesn't give the better angular resolution.
+The main reason seems to be a limitation of the number of training sample caused by lack of computer memory.
+As shown in Fig XXX, the obtained angular resolution for the 5-mm width becomes better with increasing the number of training sample, while the other larger width is saturated already.
+%achine learning for increasing number of input data.
+XXXX.
+Also, the angular resolution is not changed up to 25 mm in width of the strips, which means the more precise information is not essential for the better angular resolution because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects does not align the incident direction.
+
+%On the other hand, the finite size of the strip is related to the effect of incident gamma position.
+The previous results given in the Fig.~\ref{fig:angle_reco_width} are obtained from the data samples in which the incident gammas enter to a fixed position, the center of the strip.
+When we generated the gammas entering uniformly to the strip, we get the angular resolution as shown in Fig.
+xxx.
+Base on the results, we decide the width of the strip as xxx mm for a testing module to confirm the M.C.
+studies.
+%The performance of the detector is tested with different detector dimensions.
 Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000.
-It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths.
+Figure~\ref{fig:angle_reco_width} shows the angular resolution of the reconstruction as a function of the scintillator strip width with 5-mm-wide steps.
+It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths, and configurations with larger strip size than 15 mm do not provide improved resolution so that the width of the strip is determined to be 15 mm.
 
-The angle reconstruction is tested only with signals in front layers.
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_hist.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_graph.pdf}
+\caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%  }
+\label{fig:angle_reco_layer}
+\end{figure}
+
+When we focus only on the angle measurement, we don't need the full scale of the detector for containing the whole shower particles.
+We can reconstruct incident angle by using only the front-layer signals.
+% and check its performance.
+%with the same configuration. 
+As shown in Figure~\ref{fig:angle_reco_layer}, the angular resolution is not improved larger than 24 layers which corresponds to the 4.6$X_{0}$.
+With the energy threshold of 10 MeV to the first 24 layers, 94$\%$ of incident gammas are reconstructed correctly, and the remained 6$\%$ do not generate enough shower particles.
+
+%reconstruction with the first 24 layers, which corresponds to the 4.6$X_{0}$, provides the identical resolution with one with the full geometry.
+The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region.
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%.
+Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The reconstructed $\theta$ distribution without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of failures of the $\theta$ reconstruction, and this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold.
+The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold, and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
+
+%The angle reconstruction is tested only with signals in front layers.
 Usages of front-layer signals are applied to the data sample for training and test procedures at the same time.
-The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides identical resolution with one from full geometry, while possessing about xxx\% inefficiency due to no responses in the front region.
-As a results of the inefficiency, A delta peak can be seen in Fig.(fl).
-This peak can be rejected with the application of the total energy threshold (10~MeV in Fig.(fl)) in the front region.
+The reconstruction with 24 layers, which possess 4.6$X_{0}$, provides the identical resolution with one with the full geometry.
+The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region.
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%.
+Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The reconstructed $\theta$ distribution without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of failures of the $\theta$ reconstruction, and this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold.
+The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold, and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
 
-The energy threshold and the attenuation effects are studied.
-The attenuation effect is applied to the deposit energies in each channel with the attenuation function~\cite{Murayama:2020mcp}.
-The energy threshold is applied to the all channels after the application of the attenuation effect.
-The coefficients of the attenuation effect are thought to be same as~\cite{Murayama:2020mcp}, and the applied threshold is 0.5~MeV.
-These responses are applied to the data sample for the training and test procedure.
-The angular resolution is found to be consistent with the resolution without such effects.
+%\begin{figure}[!hbt]
+%\includegraphics[width=0.8\textwidth]{figures/Fig4_reco_ecut.pdf}
+%\caption{ (Color online) Reconstructed $\theta$ before (black) and after (red and green) applying the responses related with the energy measurement.
+The red (green) distribution is constructed with the training samples without (with) such effects and the test samples with such effects.
+Simulated effects are found to be not significant.}
+%\label{fig:angle_reco_ecut}
+%\end{figure}
 
-The incident angle and the incident energy dependencies of the angle reconstruction are studied with the same configuration and requirements mentioned before. It is found that
+- Threshold effect
+
+%\subsection{Expected performance}
+
+%- W-Fiber
+
+%- Attenuation effect (NIM A715, pp48-55 (2013))
+
+%- Light Yield (40/1mm $\rightarrow$ 200/MeV (UCV) other reference ?)
+
+%The detector responses on the energy deposit are studied.
+The attenuation effect, smearing effect due to the photon statistics, and energy threshold for each channel are considered.
+The attenuation effect is applied to the deposit energy in each channel with the attenuation function, described in~\cite{Murayama:2020mcp}.
+The coefficients for the attenuation effect are assumed to be same with~\cite{Murayama:2020mcp}.
+The energy deposit after the attenuation effect is smeared with respect to the number of photon statistics.
+The number of photons ($\rm{n.p.e}$) is assumed to be 50 for 1 MeV.
+The standard deviation ($\sigma(E)$) for the smearing can be defined as
+
+%\begin{eqnarray}
+%\sigma(E) = \sqrt{E/\rm{n.p.e}}
+%\end{eqnarray}
+%After the smearing attenuated energy deposit, the energy threshold (0.5 MeV) is applied to the all channels.
+These effects are applied to the test samples and the training samples, and the training is done with and without applying such effects and the test is done with applying the effects.
+Figure~\ref{fig:angle_reco_ecut} shows that the angular resolution is found to be not significant against such effects.
+
+%\begin{figure}[!hbt]
+%\includegraphics[width=0.6\textwidth]{figures/Fig5_reco_hist.pdf}
+%\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ and true %$\gamma$ energy.
+The incident $\theta_{\rm{true}}$ is illustrated with different colors, which are explained in fig.\ref{fig:angle_reco_def}, and the $\gamma$ energy is illustrated with different lines.}
+%\label{fig:angle_reco_dep}
+%\end{figure}
+
+%The $\theta$ reconstruction dependencies on the incident angle and the incident energy are studied.
+Figure~\ref{fig:angle_reco_dep} shows the reconstructed $\theta$ with respect to the incident angle and the incident energy with different line colors and styles.
+The incident angle dependence of the reconstruction is found to be not significant for higher $E_{\gamma}>$~500~MeV and appears at lower $E_{\gamma}=$~200~MeV.
+The dependence on the incident energy can be clearly seen for all $\theta_{\rm{true}}$.
+The reconstruction for $\theta_{\rm{true}}=$~5~deg with lower $E_{\gamma}<$~200~MeV has a shifted maximum point due to their large standard deviations.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_graph.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
+\caption{ The angular resolution as a function of $\gamma$ energy (left), and the angular resolution for 1 GeV as a function of incident $\theta_{\rm{true}}$ (right). }
+\label{fig:angle_reco_dep_gr}
+\end{figure}
+
+Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta_{\rm{true}}=$~10~deg on the left panel.
+The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}}$, where the $p_{0}$ denotes the contribution from energy-independent term and is estimated to be zero, and the $p_{1}$ denotes the contribution from energy-dependent term, mainly related with the development of the EM shower.
+The estimated $p_{1}$ for different $\theta_{\rm{true}}$ can be seen in the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
+They are deviating within $\pm$~0.05~deg range from the 1.25~deg.
 
 \section{Conclusions}
+We studied the sampling calorimeter to measure incident angle of the gamma.
+With the configuration of alternation 1-mm thick lead sheets and 5-mm thick plastic scintillators will produce the energy resolution as 4$\%$  for 1 GeV gamma due to the sampling fluctuation.
+When we focus only on the angle measurement, the first 24 layers (4.6 Xo) produce the same resolution as that of the full geometry (20 Xo) with 94$\%$ of detection efficiency.
+The angular resolution is not changed significantly increasing the width of the strips up to 25mm and expected to be 1.2 degrees for the 1 GeV gamma.
+
+https://github.com/chenkkkk/MTR-TSF
 

### 2022-01-04 paper.tex
updates

@@
 \usepackage{cleveref}
+\usepackage {xcolor}
 
@@
 \setcounter{page}{0}
-\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle }
+\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident }
 
@@
 \label{sec:mot}
-The electromagnetic calorimeter (EM-Cal) has played an important role in experimental studies of the nuclear and particle physics.  
+The electromagnetic calorimeter has played an important role in experimental studies on the nuclear and particle physics.  
 % experiments specially to detect gamma. 
-Various crystals have been developed for better energy and timing resolution of the calorimeter so far~\cite{Calorimeter}.
+Various crystals have been developed for better energy and timing resolution of the detector so far~\cite{Calorimeter}.
 %The most important properties of the detector are good energy and timing resolution, and various crystals has been developed for the purpose[] .
-On the other hand, the sampling calorimeter tends to replace the crystal calorimeter in large-scale high energy experiment mainly due to its cost-effectiveness.
-The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that detect shower particles.
-
-Since the energy deposit into the passive convert can not be measured, its fluctuation called as sampling fluctuation determines the energy resolution of the sampling calorimeter which is generally worth than that of the crystal one.
+On the other hand, the sampling calorimeter becomes popular in large-scale high energy experiment mainly due to its cost-effectiveness.
+The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that obtain information on it.
+Since the energy-deposit in the passive convert can not be measured, its fluctuation, called sampling fluctuation, determines the energy resolution of the  calorimeter, which is generally worth than that of the detector made of crystals.
 %mainly determined by the  which causes a limitation of energy resolution,  
@@
 %Due to the fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution. 
-However, the shower generation becomes more effective by selecting freely among the large numbers of candidate.
-The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}.
+It is possible, however, to optimize configuration of a large-size detector by selecting the converters and the counters among various candidates those are easily fabricated with low costs.
+A 5m-long cylindrical calorimeter made of alternating lead and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
+
+%The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}.
 %In addition, the fluctuation becomes not so important for high energy gammas owing to large number of shower particles.
@@
 
-A layer structure of the sampling calorimeter enables us to measure the profiles of shower particles in layer by layer along to the shower development.
-That is, we can estimate the direction of incident gamma by connecting the center of each profile.
-We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV.
+A layer structure of the sampling calorimeter enables us to measure the individual profiles of the shower along to the accumulating direction, and we can estimate the direction of incident gamma by connecting the center of them.
+When we  decide momentum vector of incident $\gamma$ by using only the calorimeter, it is expected more reliable event reconstruction with better background rejection.
+In a particular experiment, KOTO, aiming to detect the final state existing only single $\pi^0$ without any other particles, the experimental method will be an important tool for the successful measurement.
+
+%Even though the sampling fluctuation makes limitation on the energy resolution in this energy range, there is a merit to construct momentum vector of $\gamma$ by using only the calorimeter without additional
+
+%We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV. 
 %measure not only energy but also incident angle of photon.
@@
 Also, the effect of the sampling fluctuation is a matter in medium energy photons in range 100 MeV to few GeV photons.
-Even though the sampling fluctuation makes limitation on the energy resolution of the calorimeter in this energy range, there is an experiment to have a motivation on developing a detector configuration enable to measure the incident direction.
+ %information about its generation position. Since the $  Participating in event reconstruction
+
+%experiment to have a motivation on developing a detector configuration enable to measure the incident direction.
 
@@
 
-Considering negligible detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$.
-The KOTO utilizes undoped Cesium Iodide (CsI) crystals as an EM-Cal to measure the gamma~\cite{CsI}.
+Considering negligibly small detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$.
+The KOTO utilizes undoped Cesium Iodide (CsI) crystals to measure the incident energies and positions of the $\gamma$~\cite{CsI}.
 %An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons.
-For the reconstruction, we need an assumption that the two gammas are generated from a single $\pi^0$ decaying at the beam axis in addition to the detection variables.
+In order to reconstruct $\pi^0$ from the detected two $\gamma '$s, we need an assumption that they are generated from the single $\pi^0$ decaying at the beam axis.
+This assumption works correctly with $K_L$ beam having small-size cross-section and hermetic veto counters assuring the two-$\gamma$ final state
+
+There are, however, large amount of background events have a possibility to become the two-$\gamma$ final state because of various reasons.
+For example, the $K_L \rightarrow \pi^0 \pi^0$ decay will be the two-$\gamma$ event when we can not detect additional two $\gamma$'s due to limited detection efficiency of detectors.
+Considering the 8 orders of larger branching ratio of the $K_L \rightarrow \pi^0 \pi^0$ decay compared to that of the $K_L \rightarrow \pi^0 \nu \bar{\nu}$, it is a challenging to achieve the required detection efficiency which is closely connected to the achievable experimental sensitivity in terms of accidental loss.
+If the remained two $\gamma$'s are generated from different $\pi^0$, the reconstructed $\pi^0$ will be differ from another results from obtained by newly obtained the momentum vectors.
+We can reject so-called odd-pairing  of the $K_L \rightarrow \pi^0 \pi^0$ decays.
+%without strict veto requirement.
+%strict detection efficiency of the additional $\gamma$'s.
+
+In addition, small fraction of neutrons those are dominant component of the $K_L$, can interact with detectors and produce $\pi^0$ or two-$\gamma$-like events.
+Those events are rejected by the shower shape analysis looking into energy sharing among the finely segmented CsI crystals, and the rejection power will be greatly improved if we could use the additional information on the $\gamma$'s.
+
+%$contaminated
+
+%considerable background event still be the two-$\gamma$ final state
+
+%There as in addition to the detection variables.
 This means that we would get a wrong $\pi^0$ in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
@@
 This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions.
-We studied a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator for the angular measurement of incident gamma.
-%could be a good candidate of the calorimeter as describe in this paper.
-In the following section, the configuration of detector and the reconstruction of $\gamma$-incident angle will be described.
-The discussion on the optimal configuration and its expected performance will be followed.
+Since the electromagnetic shower development is a stochastic process, there should be a limitation on the resolution of the measurement.
+We have studied about the angle measure with a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator.
+The have performed an feasibility study on the angle measurement to estimate feasibility  achievable angular resolution in ballpark figure and clarify the items we have to solve for better performance.
 
-\section{Method}
-We started the study with a setup of sampling calorimeter consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter.
+%the angular measurement of incident gamma. %could be a good candidate of the calorimeter as describe in this paper.
+In the following section, the configuration of detector and Monte Carlo simulation for electromagnetic shower generation will be given.
+In the section III, we will describe how to reconstruct incident angle from the generated detector response by using one of the most attractive toolkit of the machine learning; $\XGB$.
+Finally, we will summarize our study briefly.
+
+\section{ELECTROMAGNETIC SHOWER}
+We started the study with a detector setup consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter.
 % as shown in Fig.~\ref{fig:det_conf}.
@@
 The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
-The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}.
-The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
-With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them.
-The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully.
-The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver.
-xxx) with the standard EM sub-packages ~\cite{GEANT4}.
+The lead sheet has a cross-section of  500 mm $\times$ 500 mm and each scintillator strips of 500 mm $\times$ 15 mm  being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}.
+Total number of alternating layers is 105 which corresponds to 20 radiation length (20 Xo) and possible to contain all of the shower particles generated by $\gamma$ in the region of medium energy (from  100 MeV to few GeV).
 
@@
 
+The generation of incident $\gamma$ and its interaction with detector materials was simulated by using the GEANT4 package (ver. xxx) with the standard EM sub-packages~\cite{GEANT4}.
+The $\gamma$ entered the center of the detector and moved to the positive direction of Z-axis, where the surface of the first layer is defined as a starting point (Z=0).
+Its incident angle is defined as the polar angle ($\theta$) along to the Z-direction, that is, $\theta = 0$ for the $\gamma$ enters perpendicular to the detector surface.
+%The generated energies are in range from hundred MeV to few GeV which is interested to the KOTO experiment.
+Figure~\ref{fig:Evt_Dis} shows a typical event display describing the energy deposit to the each scintillator strips in both of X-Z and Y-Z plane for 1-GeV $\gamma$ entering in perpendicular to the center of the detector ($\theta=0$ and $\phi=0$).
+%We can get an three-dimensional information on the shower development combining them and will use them as inputs of the machine learning package, $\XGB$.
+%This information indicates the shower development, and will be used as an input of the machine learning package, $\XGB$. 
+%We can get the shower profiles from energy deposits in individual strips arranged in the 3-dimension.
+Figure XXX shows a event display for 1 GeV gamma entering with $\theta =0$ in X-Z and Y-Z planes.
+The amount of energy deposit to each strips are expressed by the darkness (color online).
+
+\begin{figure}[!hbt]
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
+\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
+\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
+
+\caption{Distribution of energy deposit to the each scintillator strips in X-Z plane (Left) and Y-Z plane (Right) for 1-GeV $\gamma$ entering perpendicularly to the detector ($\theta=0$ and $\phi=0$).}
+\label{fig:Evt_Dis}
+\end{figure}
+
+%With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from the
+
+%energies are in range from hundred MeV to few GeV by considering the KOTO experiment.
+
+%its origin is defined as the centers of the central strips both of the X- and Y- There generation position is the centers of both of the X- and Y- strip moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
+With the configration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them.%The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver.
+xxx) with the standard EM sub-packages ~\cite{GEANT4}.
+
 %{\it I will describe the coordinator and the gamma enter to the center of strips}
@@
 
-In order to reconstruct the incident angle of the gamma, we used the $\XGB$, which is one of the popular machine learning packages supporting a scalable tree boosting system~\cite{xgboost:2016}.
-Input data for the $\XGB$ are deposit energies on each scintillator strip by the generated shower particles.
-It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical.
-As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.
+%\subsection{Properties of generated shower}
+% moliere rad, visible ratio graph
+% energy resolution (+as a function of E)
+% gamma beam energy에 따라 backsplash가 만드는 event veto
+% + incident angle에 따라?
+%Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
+%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$).
 
-There are five hyper parameters which can be optimized by user, and their values are selected to provide the best angular resolution as described in table~\ref{tab:XgbPar}.
-Among the parameters, the Max.
-depth rapidly improves the angular resolution with increasing its value until 15.
-The N\_estimators also improves the angular resolution with increasing its number, which is correlated to the value of the Max.
-depth.
-Its optimal condition becomes 1000 when the Max.
-depth is 15.
+%Figure~\ref{fig:EMshower} shows side (left) and top view (right) of energy deposit in the each strips for $\gamma$ entering the center of the detector with energy of 1 GeV and incident angle of 10 degrees and azimuthal angle of 0 degree .
+By using this profiles along with the alternating X- and Y-direction, we can reconstruct incident angle of the $\gamma$ after studying its nature with the $\XGB$ package.
 
-\begin{table}[hbt!]
-\centering
-\caption{Hyperparameters of the $\XGB$}
-\begin{tabular}{cccc}
-\hline 
-Parameter & Function & Default value & Used value \\ \hline 
-N\_estimators & The number of decision trees & N.A. & 1000 \\  
-Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
-Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
-Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
-Gamma & Requirement on minimum loss function & 0 & 0 \\ 
-\hline
-\end{tabular}
-\label{tab:XgbPar}
-\end{table}
+The GRANT4 can provide reliable results on the electromagnetic shower produced by the incident $\gamma$. 
+%by usis well produced by showers show typical distributions both of longitudinal and transverse directions.
+Figure~\ref{fig:Longitudinal} shows longitudinal distribution of average sum of the energy deposit in strips of each counter layers regardless the direction of arrangement.
+%Considering the EM shower is generated mainly at the converter, the both distributions of the converter and counter are identical and can be expressed by two parameters,
+Its longitudinal profile depends on incident energy and can be expressed \cite{Longo} by the three parameters as following;
+%When we ignore large radiation of the scintillator, the profile can
+%projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
+%can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
+\begin{equation}
+    F(E,t)=A  t^\alpha e^{-bt},
+    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
+\end{equation}
+where t is the position of scintillator strips along the Z-direction.
+As shown in Fig.~\ref{fig:Longitudinal}, the Eq.
+1 describes the obtained average energy deposit on each layer of scintillator strips reasonably.
+In the case of the sampling calorimeter, however, the energy deposit on the converters and counters is caused by multiple processes and its fraction is changed along with the shower develpoment.
+%is changed according to the shower depth because there is a change of energy depositing process. 
+%and uwe focus only on the energy deposit 
+%the probability of the shower generation is much different between the counter and converter.
+As a result, the ratio of the energy deposit in counter and in converter changes according to the layer position as shown in Fig.~\ref{fig:Longitudinal} (right).% because there are multiple process of which probability changes according to development.
+In order to describe the shower profile in the sampling calorimeter, we need to take into account the layer dependent of the energy deposit.
+Since we will use the simulated results only for current study on angle measurement, we did not proceed any further analytic study on the process.
+%As a results, the Eq.
+1 needs an additional correction factor ...
+to express the obtained results more correctly.
+%We can take into account the changes by using layer-by-layer structure of the detector.
+%({\it Shall we investigate energy dependency of the parameters ?)}% Considering the EM shower is generated mainly at theIt is natural that the distributions on converter and counter are identical.
+%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
+%\begin{equation}
+    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
+%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
+%\end{equation}
+%or
+%\begin{equation}
+    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
+%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
+%\end{equation}
+%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.
 
-For the training procedure, gammas are generated uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle.
-The performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees.
+\begin{figure}[!hbt]
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
+%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
+\includegraphics[width=0.48\textwidth]{figures/LongProfile.jpg}
+\includegraphics[width=0.48\textwidth]{figures/LayerVisibleRatio.jpg}+
+\caption{Generated average energy deposit on the scintillator strips along Z axis(left) and visible ratio for each layer.}
+\label{fig:Longitudinal}
+\end{figure}
+
+On the other hand, the lateral spread of the shower
+%is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers.  This spread 
+is expressed as the the Molière radius defined ~\cite{PDG} as 
+\begin{equation}
+R_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
+\end{equation}
+where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
+Since the sampling calorimeter contains different materials placed at the different localized positions, we defined the $R_M$ as the radius of cylinder containing 90\% of the energy deposit instead of using the Eq.
+(2).
+The left panel of Figure~\ref{fig:Moliere_vis} shows energy deposit per each layer (black line) and integrated energy deposit up to the layers.
+We can deduce the Molière radius as 70 mm, which is largely depends on the position of its measurement.
+The right panel of Figure~\ref{fig:Moliere_vis} shows the radius as a function of scintillator layer, which increases along the shower depth.
+The first three bins show large radius because of large contribution of shower particles generated opposite to the incident direction.
+
+%difference of $\rho_M$ for different configurations of the detector and its dependency on the detector layer.
+We need to notice the spread of shower is different along to the its development similar to the ratio of the energy deposit mentioned above.
+We can take into account the complicated response of the sampling calorimeter by using the individual energy deposit of the strips as inputs of the machine learning for the angle reconstruction.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.44\textwidth]{figures/Edep_R.jpg}
+\includegraphics[width=0.48\textwidth]{figures/Moliere_layer.jpg}
+\caption{Left:Energy deposit for given radius as a differential(black line) and integral distribution(red line) Right: Moliere radius as a function of ID of scintillator-strip layers.}
+\label{fig:Moliere_vis}
+\end{figure}
+
+With the detector configuration shown in Fig.~\ref{fig:det_conf}, we can get three dimensional information on the showers.
+By using the obtained data as an input of the machine learning package, we can extract the incident angle of the $\gamma$ as explained following section.
+%When we apply the three dimensional information on the generated shower profile, we can reconstruct incident $\gamma$ more correctly by integrating the energy deposit. 
+%For simplicity in numerical calculation, %For the sampling calorimeter consisting of different materials, 
+%let us define the Molière radius as the radius of cylinder containing 90\% of shower energy.
+As shown in Fig.~\ref{fig:Moliere_vis}, the configuration of 1-mm lead and 5-mm scintillator shows $\rho_M=70$ mm in average which changes with the shower depth.
+%That is, we can expect an improvement on separating two gammas closely incident to the calorimeter.
+We will study on this subject and not discuss any more in this paper.
+%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal
+
+%The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
+%\begin{equation}
+%R = { \frac{E_{act}} {E_{act}+E_{pas}}},
+%\end{equation}
+%where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively.
+This visible ratio is roughly given by the ratio of material budget between the converter and the counter.
+%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
+%by thickness of the converter.
+It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter.
+%As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon.
+However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers.
+Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too).
+When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX.
+This is because the number of low energy electrons and positrons penetrating the lead sheet is increased in case of thinner converter.
+As a result of the increasing probability, the sampling fluctuation becomes small and the energy resolution improved as a result.
+%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.
+
+%\begin{figure}[!hbt]
+%\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
+%\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
+%\caption{Visible ratio of the sampling calorimeter for different configuration (Left) and energy resolution as a function of incident $\gamma$ energy (right).}
+%\label{fig:energy_res}
+%\end{figure}
 
@@
 
-\section{Results}
+\section{ANGLE RECONSTRUCTION}
 \label{sec:res}
 
-\subsection{Properties of generated shower}
-% moliere rad, visible ratio graph
-% energy resolution (+as a function of E)
-% gamma beam energy에 따라 backsplash가 만드는 event veto
-% + incident angle에 따라?
-Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
-%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$). 
-Its longitudinal projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
-can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
-\begin{equation}
-    F(E,t)=E_0\cdot (bt)^{a-1}e^{-bt}/\Gamma(a),
-    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
-\end{equation}
-where t is the z-position in radiation length. It is natural that the distributions on converter and counter are identical. 
-%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
-%\begin{equation}
-    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
-%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
-%\end{equation}
-%or
-%\begin{equation}
-    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
-%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
-%\end{equation}
-%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.
+The incident angle of the $\gamma$ can be estimated as a results of machine learning by using the $\XGB$, which is one of the popular packages supporting a scalable tree boosting system~\cite{xgboost:2016}.
+We used energy deposits on each scintillator strips as input data for the $\XGB$, and the packages connects the relationship among the input data to estimate the incident angle.
+** a little detail one or two senteces***
 
-On the other hand, the transverse shower spread is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers as shown in Figure XXX.
-This distribution is expressed by the Molière radius defined as
-\begin{equation}
-\rho_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
-\end{equation}
-where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
-For the sampling calorimeter consisting of different materials, let us define the Molière radius as the radius of cylinder containing 90\% of shower energy.
-As shown in Figure xxx, the test model (1-mm lead and 5-mm scintillator) shows $\rho_M=70$ mm in average which changes with the shower depth.
-That is, we can expect an improvement on separating two gammas closely incident to the calorimeter. We will study on this subject and not treat in this paper.
-%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal
+%are deposit energies on each scintillator strip by the generated shower particles.
+It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical.
+As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.
+({\it This part should be updated)}
 
-The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
-\begin{equation}
-R = { \frac{E_{act}} {E_{act}+E_{pas}}},
-\end{equation}
-where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively.
-This visible ratio is roughly given by a ratio of material budget between the converter and the counter.
-%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
-%by thickness of the converter.
-It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter.
-As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon.
-However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers.
-Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too).
-When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX.
-This is because the number of low energy electrons and positrons penetrating the lead sheet.
-Even though the small improvement on the visible ratio, the energy resolution improved greatly with the thinner layer.
-%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.
-
-\begin{figure}[!hbt]
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileZ.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileXZ.pdf}
-\caption{Profile of the EM shower in Z axis(left) and X-Z plane(right)  }
-\label{fig:EMshower}
-\end{figure}
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/3.2/moliere_radius.pdf}
-\includegraphics[width=0.48\textwidth]{figures/3.2/visible_ratio.pdf}
-\caption{Dependence of Moliere radius(left) and visible ratio(right) on the thickness of scintillators}
-\label{fig:moliere_vis}
-\end{figure}
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
-\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
-\caption{The dependence of the energy resolution on the thickness of scintillators(left) and the incident energy of $\gamma$(right)}
-\label{fig:energy_res}
-\end{figure}
+For the training of the $\XGB$, we generated $\gamma$'s uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle ($\varphi$) for given energy (training sample).
+By using another data set (testing sample) which was generated at a fixed polar angle, we estimated performance of angular reconstruction of the detector.
+The number of generated $\gamma$ was
+$2\times10^5$ for the training sample and $1\times10^5$ for the testing sample, respectively.
 
@@
 %\subsection{Detector dimension}
-\subsection{Angle reconstruction using Machine Learning}
+%\subsection{Angle reconstruction using Machine Learning}
 
-Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ obtained from the test samples, which are generated for fixed angles in range of $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
-The number of generated gammas is $10^5$ and their energy is 1 GeV.
-The $\XGB$ correctly reconstructs $\theta=$ with a typical resolution as 1.2 degrees.
-There is no significant difference according to the incident angle.
+%With the results of the $\XGB$ by using the training sample generated with the uniform distributions in both of polar and azimuthal angles, we estimated the incident angle of photons generated with a fixed value for a given energy.
+Figure~\ref{fig:angle_10degree} shows the distribution of reconstructed angles for 1-GeV $\gamma$ entered detector with 10 degrees of incident angle.
+%The Gaussian distribution (black solid line) provides the proper mean value,  the $\XGB$ can provide correct answer.
+We can get proper mean value of the distribution, however, it has heavier tail compared to that of the Gaussian distribution.
+In order to describe the obtained result more correctly, we tried to fit it with the Generalized Gaussian (GG) function.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
+\caption{ (Color online) Reconstructed $\theta$ with respect to 10 degrees of incident $\theta$.
+The gaussian function can not describe the tail region (red dotted line).
+The generalized gaussian function (black solid line) shows much better agreement with the obtained result.}
+\label{fig:angle_10degree}
+\end{figure}
+
+%In order to include the heavier tail more correctly in the performance study, we tried to fit the distribution with two different function; one is a convolution of a Lorentz and Gaussian distribution (Voigt function) and the other is a Generalized Gaussian function.
+%The Voigt fuction expressed as 
+%\begin{equation}
+%V(x; \sigma, \gamma) = \int_{- \infty}^{\infty} G(x';\sigma)L(x-x';\gamma) dx',
+%\end{equation}
+%becomes to be Lorentz distribution $L(x; \gamma)$ in case of $\gamma$=0 
+%\begin{equation}
+%L(x;\mu, \gamma) = {\gamma \over {\pi ((x-\mu)^2 + \gamma^2)}}
+%\end{equation}
+%of peak position at x=$\mu$ in case of $\sigma$ =0 
+%and to be Gaussian distribution $G(x;\sigma)$
+%\begin{equation}
+%G(x;\mu, \sigma) = {1 \over {\sqrt{2 \pi} \sigma}} e^{-(x-\mu)^2/2\sigma^2} 
+%\end{equation}
+%when the $\gamma$ equal to be zero. The function is available in the analysis framework of the ROOT~\cite{Voigt}, and  improves the fitness a little.
+
+The GG function provides more flexible modeling to data than the Gaussian can do by introducing an additional parameter to describe the shape of distribution.
+This function was suggested by Subbotin~\cite{Subbotin} in 1923 treating the accidental errors not only to be continuous but also to be expanded in the power series.
+Its probability density function is expressed as
+%has received considerable attention especially at the image processing studies\cite{Dytso},  
+%Among various parametrization of the function, we take that its probability density distribution (pdd) is given as~\cite{Gonzalez}  
+\begin{equation}    
+  % GG(x;\mu, \sigma,     p) = {C_p \over \sigma} e^{-{|x-\mu|^p}/{2 \sigma ^p}}, 
+   %f(x; \mu, \alpha, \beta) = {\beta \over {2 \alpha \Gamma(1/\beta)}} e^{-(|x-\mu|/\alpha)^\beta} , 
+     f(x; \mu, \alpha, \beta) = \frac{\beta}{2 \alpha \Gamma(1/\beta)} e^{-(|x-\mu|/\alpha)^\beta} , 
+%   f(x; \mu, \alpha, \beta) = {\beta \over {2 \alpha \Gamma (1/\beta)}} e^{-(|x-\mu|/\alpha)^\beta} , 
+\end{equation}    
+where $\beta$ is the so-called shaping factor
+%Also  
+%\begin{equation}    
+%    A ={ {\beta p}  \over {2\Gamma(1/p)}},
+%\end{equation}
+and the $\Gamma(.)$ is the gamma function.
+It becomes the Laplace distribution if $\beta$=1 
+\begin{equation}
+LP(x;\mu, \sigma) = \frac{1}{\sqrt{2}\sigma} e^{-{\sqrt{2}{|x-\mu|} / \sigma}} 
+\end{equation}
+and Gaussian distribution
+\begin{equation}
+G(x;\mu, \sigma) = \frac{1}{\sqrt{2 \pi} \sigma} e^{-(x-\mu)^2/2\sigma^2} 
+\end{equation}
+for $\beta$=2.  The second moment of the GG function is given as
+\begin{equation}    
+    E[X]^2  = \alpha^2 \frac{\Gamma(3/p)}{\Gamma(1/p)}  \equiv \sigma^2 , 
+\end{equation}
+which becomes the variance of the Gaussian distribution in case of the $\beta$=2.
+This value can be interpreted equal footing regardless of the $\beta$-values, and will be used as the angular resolution for given detector configuration from now.
+%we can treat it as a width of the distribution which contains same meaning %regardless of the p-values.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.45\textwidth]{figures/PDF_Gonzalez.pdf}
+\includegraphics[width=0.45\textwidth]{figures/Int_Gonzalez.pdf}
+\caption{ The probability density distribution (left), and their integrated distributions (right) of the generalized gaussian (GG) function in the case of  $\mu = 0$ and $E[X]^2 = 1$ for various shaping paramete $\beta$.
+It changes from the Laplace ($\beta$=1) to the Gaussian ($\beta$=2) distribution according to the $\beta$.
+On the other hands, their integral probability density show similar distributions implying its second moment can be interpreted equally regardless of the $\beta$ values in the range of $1<\beta<2$.}
+\label{fig:GG_pdf}
+\end{figure}
+
+Figure~\ref{fig:GG_pdf} (left) shows the probability density distribution of the GG function in the case of $\mu = 0$ and $E[X]^2 = 1$ for different $\beta$ values from 1 to 2.
+We can figure out the change from the Laplace ($\beta = 1$) to the Gaussian distribution ($\beta=2$).
+As shown in the right plot of the Fig.~\ref{fig:GG_pdf}, the integrated probability for 1$\sigma$ interval becomes to be from 68.3$\%$ ($\beta=2$) to 75.7$\%$ ($\beta=1$).
+In the case of $\beta=1.5$ as obtained from the data fitting, it is to be 71.2$\%$ which is just 4$\%$ larger than that of the Gaussian.
+Moreover, a statement of "1.7$\sigma$ interval contains 91$\%$ of entries" can be applied in range of $1<\beta<2$, thus we will use the $\sigma$ as a definition of the angular resolution in this paper.
+%When we take an angular resolution as the width of fitted distribution, it is determined by the two parameters, $\sigma$ and p.
+Figure~\ref{fig:GG_pdf} shows distributions of probability density (left) and integrated the density for $\sigma =1$ with changing value of p from 1.0 to 2.0.
+We can parameterize the angular resolution, $\sigma_{R}$ as
+%\begin{equation}
+%\sigma_{R} = f(p) \cdot \sigma,
+%\end{equation}
+%where the $f(p)$ is a empirically determined scale factor from the Fig.~\ref{fig:GG_pdf} (right).
+With the definition, the integrated probability becomes 68.3$\%$ inside the $\sigma_R$ for all p values in the range of $1 \leq p \leq 2$.
+
+%for a given value of p in the range of. That is, the fitted result of the Fig.~\ref{fig:angle_10degree} ($\sigma$=
+
+%its performance of the angle measurement is tested with the test sample forq given angle.
+%tested its reconstruction performance with $10^6$ gamma samples for each fixed polar angle from $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
+%of the $\XGB$ by using $10^6$ gamma samples generated with uniform distribution in both of polar angle in range of 0 to 50 degrees and azimuthal angle of 0 to 360 degrees, we tested its reconstruction performance with $10^6$ gamma samples for each fixed polar angle from $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
+%Figure~\ref{fig:angle_reco_def} shows the distribution of reconstructed angles for incident gammas those have 1-GeV of energy and 10-degree of polar angle.
+The distribution has heavier tail compared with that of the Gaussian, and we tried to fit the distribution with the Generalized Gaussian distribution.
+The distribution
+
+%which agree well with the generated values.
+%The angles are properly reconstructed with a typical resolution as 1.2 degrees. There are no significant differences among the various incident angles. 
+%Typical angular resolution is obtained as 1.2 degrees and does not show significant dependency on incident angle.
 
@@
 \includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
-\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution.
-The standard deviation of all Gaussian functions are estimated to be 1.3 degree.}
+\caption{\textcolor{red}{plots should be updated}
+Angular resolution for different incident angles (left) and shape parameter $\beta$ of reconstructed angluar distribution (right).}
 \label{fig:angle_reco_def}
@@
 
+Since the angular resolution depends on the hyperparameters of the $\XGB$ which control the details of the training process, we scanned them with monitoring the angular resolution $\sigma$ defined at the Eq.
+7.
+There are five hyper parameters which can be optimized by user, and correlated among them.
+Figure~\ref{fig:par_scan} shows part of the scanning results, which enables us to determine the best parameters set to provide the best angular resolution.
+%their values are selected to provide the best angular resolution as described in
+The decided values of the parameters are given in Table~\ref{tab:XgbPar} with their function in the training process.
+%Among the parameters, the Max.
+depth rapidly improves the angular resolution with increasing its value until 15.
+The N\_estimators also improves the angular resolution with increasing its number, which is correlated to the value of the Max.
+depth.
+Its optimal condition becomes 1000 when the Max.
+depth is 15.
+({\it This part should be updated) - can we mention more detail?}
+
 \begin{figure}[!hbt]
-\includegraphics[width=0.58\textwidth]{figures/Fig2_reco_Width_width.pdf}
+\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
+\caption{\textcolor{red}{plots should be updated}
+Angular resolution for different hyperparameter valuse.}
+\label{fig:par_scan}
+\end{figure}
+
+%performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees. ({\it This part should be updated)}
+
+\begin{table}[hbt!]
+\centering
+\caption{Hyperparameters of the $\XGB$}
+\begin{tabular}{cccc}
+\hline 
+Parameter & Function & Default value & Used value \\ \hline 
+N\_estimators & The number of decision trees & N.A. & 1000 \\  
+Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
+Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
+Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
+Gamma & Requirement on minimum loss function & 0 & 0 \\ 
+\hline
+\end{tabular}
+\label{tab:XgbPar}
+\end{table}
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
 \caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
@@
 
-With the narrower width of the scintillator strips, we may get more precise information about the shower shape.
-In order to find detector configuration providing the best angular resolution, we produced gamma events with changing the width of strips from 5 mm to 35 mm in 5 mm steps.
-As shown in Fig.~\ref{fig:angle_reco_width}, the narrower width doesn't give the better angular resolution.
-The main reason seems to be a limitation of the number of training sample caused by lack of computer memory.
-As shown in Fig XXX, the obtained angular resolution for the 5-mm width becomes better with increasing the number of training sample, while the other larger width is saturated already.
+For the study of the angle-reconstruction performance for different incident angles, we generated test samples of fixed value in range of 5 to 45 degrees with 5-degree steps.
+Each test sample contains $10^5$ $\gamma$'s and common parameter settings are used for calculating their incident angle, which showed similar performance for all samples.
+Figure~\ref{fig:angle_reco_def} shows the angular resolutions defined in Eq.
+7 for each incident angle (right) and shape-parameter $\beta$ (left).The performance of the angle reconstruction does not depend on the incident angle.
+
+%With the scintillator strips having a narrower width, we may get more precise information about the shower shape. 
+With an assumption that getting more precise information on the shower profile enables us to estimate with better resolution, we have studied the angle reconstruction by changing the width of the strips from 5 mm to 35 mm in 5 mm steps.
+As shown in Fig.~\ref{fig:angle_reco_width}, the best resolution is obtained when the width is 15mm.
+We can interpret that the larger-width configurations suffer the dilution of shower information and produce worth result.
+On the other hands, the narrower-width configuration does insufficient training due to limited statistics because of increased input features.
+This problem will be explained detailed later.
+
+%In order to figure out the optimal detector configuration providing the best angular resolution, we repeated the calculation by changing the width of the strips from 5 mm to 35 mm in 5 mm steps.
+Even though the narrower width is expected to provide more precise information about the shower shape, it does not mean to provide the better resolution as shown in Fig.~\ref{fig:angle_reco_width}.
+The angular resolution is not changed with increasing strip width up to 25 mm, which implies that the precise information on the shower shape is not essential to the angular resolution in a certain range because  of the stochastic nature of the shower generation.
+On the other hand, there is a possibility of insufficient training due to rapid increasing of the number of input according to the finer segmentation, while the number of events and hyper parameters for the training remain the same values optimized for the configuration of the 15-mm width.
+
+%because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects are not aligned in the incident direction.
+
+%The main reason seems to be a limitation of the number of training sample caused by lack of computer memory. 
+%As shown in Fig XXX, the obtained angular Aresolution for the 5-mm width is improved with increasing the number of training sample, while the other larger width is saturated already.
 %achine learning for increasing number of input data.
 XXXX.
-Also, the angular resolution is not changed up to 25 mm in width of the strips, which means the more precise information is not essential for the better angular resolution because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects does not align the incident direction.
+%Also, the angular resolution is not changed with increasing strip width up to 25 mm, which means the more precise information is not essential for the better angular resolution because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects are not aligned in the incident direction.
 
@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_hist.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_graph.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_graph.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
+\caption{ The angular resolution as a function of $\gamma$ energy (left), and the angular resolution for 1 GeV as a function of incident $\theta_{\rm{true}}$ (right). }
+\label{fig:angle_reco_dep_gr}
+\end{figure}
+
+Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta_{\rm{true}}=$~10~degrees on the left panel.
+The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}(GeV)}$, where the $p_{0}$ denotes the contribution from energy-independent term and \textcolor{blue}{is estimated to be zero ($<$= is this true ?)}, and the $p_{1}$ denotes the contribution from energy-dependent term, mainly related with the development of the EM shower.
+The estimated $p_{1}$ for different $\theta_{\rm{true}}$ can be seen in the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
+They are deviating within $\pm$~0.05~deg range from the 1.25~deg.
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/res_Nlayer.jpg}
+\includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
 \caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
-The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%  }
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\% with 10 MeV selection criteria.
+The large error bars less than 4.6 Xo is due to insufficient fitting because the reconstructed angular distributions deviated from the General Gaussian function.
+}
 \label{fig:angle_reco_layer}
@@
 
-When we focus only on the angle measurement, we don't need the full scale of the detector for containing the whole shower particles.
-We can reconstruct incident angle by using only the front-layer signals.
-% and check its performance.
+Considering a measurement of incident angle only, we don't need the full-scaled detector to contain the generated shower completely.
+We can expect 99\% of $\gamma$ will start to generate shower inside detector within 5 radiation length (Xo).
+The left panel of Figure~\ref{fig:angle_reco_layer} shows reconstructed angle by using only the front 24 layers of the detector which corresponds to the length of 4.6 Xo for 1 GeV $\gamma$.
+The failed events located near the 0 are due to insufficient energy deposit ($<$ 10 MeV) to reconstruct the angle, of which ratio is estimated to be 5.8\%.
+As shown in the right panel of Figure~\ref{fig:angle_reco_layer}, the 4.6 Xo is needed to achieve equivalent resolution to that of the full-scaled detector.
+This results suggest that we can design a calorimeter producing complete information of incident $\gamma$ for itself by putting an fine segmented sampling calorimeter in front of the main calorimeter.
+
+The obtained angular resolution is determined by combined multiple sources, mainly the performance of learning process, number of layers for the measurement and the width of strips.
+Figure~\ref{fig:multi-parameter} shows the relation among the sources.
+For the larger width (25mm), the larger numbers of layers gives the better resolution (left).
+In order to achieve the best resolution for narrower width (5mm), we need much larger number of events for training the $\XGB$
+
+\begin{figure}[!hbt]
+\includegraphics[width=0.48\textwidth]{figures/layer-width.jpg}
+\includegraphics[width=0.48\textwidth]{figures/layer-event.jpg}
+\caption{ (Color online) left:Obtained angular resolution for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ as a function of number of layers used for reconstruction for 3 different strip widths when the number of trained sample is $2 \times 10^5$.
+right: Dependence on the number of training samples for using only the first 24 layers (open markers) and full-scaled one(closed markers).
+}
+\label{fig:multi-parameter}
+\end{figure}
+
+%We can place a 5Xo-thick sampling calorimeter for angle measurement in front of a main calorimeter measuring energy of $\gamma$, and obtained angle information with resolution closed to the intrinsic value.
+
+%angular resolution depends on the radiation length used in the angle measurement and the dependence get disappeared with increasing radiation length.
+The reconstruction with 4.6$X_{0}$, which corresponds to 24 layers, provides 1.3 degree angular resolution.
+
+%We can reconstruct incident angle by using only the front-layer signals. % and check its performance.
 %with the same configuration. 
-As shown in Figure~\ref{fig:angle_reco_layer}, the angular resolution is not improved larger than 24 layers which corresponds to the 4.6$X_{0}$.
+%As signals in front layers are only used, $\gamma$s starting to interact at the rear layers can not be detected and their angles, therefore, can not be reconstructed.
+To reject such cases, total energy in the front layer is required to be larger than 1\% of incident $\gamma$ energy.
+Inefficiency due to the selection is estimated to be 5.8\%.
+
+%the angular resolution is improved larger than 24 layers which corresponds to the 4.6$X_{0}$.
 With the energy threshold of 10 MeV to the first 24 layers, 94$\%$ of incident gammas are reconstructed correctly, and the remained 6$\%$ do not generate enough shower particles.
@@
 
-- Threshold effect
+%- Threshold effect
 
@@
 
-\begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_graph.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
-\caption{ The angular resolution as a function of $\gamma$ energy (left), and the angular resolution for 1 GeV as a function of incident $\theta_{\rm{true}}$ (right). }
-\label{fig:angle_reco_dep_gr}
-\end{figure}
+\section{SUMMARY}
+We studied a possibility to measure incident angle of the medium-energy $\gamma$ by using a finely segmented sampling calorimeter.
+With the configuration of alternation 1-mm thick lead sheets and 5-mm thick plastic scintillators, it will measure the energy for 1-GeV $\gamma$ with 4$\%$ of resolution which is mainly determined by the sampling fluctuation.
 
-Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta_{\rm{true}}=$~10~deg on the left panel.
-The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}}$, where the $p_{0}$ denotes the contribution from energy-independent term and is estimated to be zero, and the $p_{1}$ denotes the contribution from energy-dependent term, mainly related with the development of the EM shower.
-The estimated $p_{1}$ for different $\theta_{\rm{true}}$ can be seen in the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
-They are deviating within $\pm$~0.05~deg range from the 1.25~deg.
+For the angular measurement, we need to optimize detector configuration such as width of strips and number of layers.
+Also, the angular resolution is strongly depends on the goodness of the training of the $\XGB$ which depends on the number of training sample.
+For a case study of 15-mm strip width and 24 layers, we can achieve the angular resolution as 1.2 degrees with 94$\%$ efficiency.
+It depends on the incident energy of the $\gamma$, which will limit strictly on the applicable ranger of the measurement.
 
-\section{Conclusions}
-We studied the sampling calorimeter to measure incident angle of the gamma.
-With the configuration of alternation 1-mm thick lead sheets and 5-mm thick plastic scintillators will produce the energy resolution as 4$\%$  for 1 GeV gamma due to the sampling fluctuation.
-When we focus only on the angle measurement, the first 24 layers (4.6 Xo) produce the same resolution as that of the full geometry (20 Xo) with 94$\%$ of detection efficiency.
+On the other hand, there are three major parameters to determine the performance of the measurement.
+With detailed studies on the optimization of the parameters, it would be possible to design the detector to satisfy the experimental requirement in various studies.
+
+%Still there are many sources o
+
+%When we focus only on the angle measurement, the first 24 layers (4.6 Xo) provide a resolution as that of the full geometry (20 Xo) with 94$\%$ of detection efficiency.
 The angular resolution is not changed significantly increasing the width of the strips up to 25mm and expected to be 1.2 degrees for the 1 GeV gamma.
 
-https://github.com/chenkkkk/MTR-TSF
+%https://github.com/chenkkkk/MTR-TSF
 

### 2022-01-04 paper.tex
update

@@
 
-%\input{commands.tex}
-
 \newcommand{\XGB}{XGBoost}
@@
 \setcounter{page}{0}
-\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident }
+\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle }
 
@@
 \begin{abstract}
-We present studies on detector configuration to obtain angular information for gammas of energies in a range from hundred MeV to few GeV.
-For the angular measurement, we need to obtain profiles of energy deposit along to both of the longitudinal and transverse directions, which could be realized by using the sampling calorimeter.
-The sampling calorimeter consists of alternating 1-mm-thick lead sheets producing the electromagnetic shower and strips of 5-mm-thick plastic scintillator measuring the energy deposit by the shower particles.
-The strips are arranged along to the alternating horizontal and vertical directions to give transverse profile by combining the both directions at a given longitudinal position.
-In this studies, we used the GEANT4 to simulate energy deposit to the individual strips of the calorimeter, and the $\XGB$ package to obtain the incident angle from the energy deposits.
+We present studies on the detector configuration to measure the incident angle of the $\gamma$, which has the energy ranging from hundred MeV to few GeV using a new sampling calorimeter.
+The sampling calorimeter consists of alternating 1-mm-thick lead sheets producing the electromagnetic (EM) shower and strips of 5-mm-thick plastic scintillators measuring the energy deposit by the shower particles.
+The strips are arranged along to the alternating horizontal and vertical directions to measure the transverse profile by combining the both directions at a given longitudinal position.
+In this paper, we used the GEANT4 to simulate energy deposit to the individual strips of the calorimeter, and the $\XGB$ to reconstruct the incident angle from energy deposits.
 
-The angular resolution weakly depends on the width of the strips up to 25mm and becomes worse rapidly with increasing the width.
-We found the proper detector thickness for the angular measurement is around 5-radiation (5 Xo) and the expected angular resolution becoms to be 1.3 degrees with 25-mm width of the strips.
-This resolution dose not depends on the incident gamma upto 30 degrees, and its energy dependency is expressed as $p_0 + P_1 / \sqrt{E_\gamma}$.
-(p0, p1 will be replaced by the obtained numbers)
+The angular resolution weakly depends on the width of the strips up to 15 mm and becomes worse with the increasing width.
+It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length of the detector.
+The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.1+1.2$/ \sqrt{E_\gamma}$.
 
-%We present studies on Monte Carlo based detector configuration to measure the incident angle of the $\gamma$.
-The Geant4 and the $\XGB$ packages are used to simulate interactions of electromagnetic showers with detector materials and to reconstruct the incident angle with the machine learning method.
-The sampling calorimeter is configured with alternating 5-mm-thick scintillator strips and 1-mm-thick lead plates.
-The sampling fraction and the Moliere radius of the detector are xxx and xxx, respectively.
-We find that the configuration with 15-mm-wide scintillator strips provides 1.3~deg resolution, and the same resolution is expected with only front part of the detector in 4.6-radiation-length in thickness with 5.8\% inefficiency.
-Furthermore, the incident angle dependency of the angular resolution is found to be consistent, and the incident energy dependency is found to be inversely proportional.
 \end{abstract}
@@
 \label{sec:mot}
-The electromagnetic calorimeter has played an important role in experimental studies on the nuclear and particle physics.  
-% experiments specially to detect gamma. 
-Various crystals have been developed for better energy and timing resolution of the detector so far~\cite{Calorimeter}.
-%The most important properties of the detector are good energy and timing resolution, and various crystals has been developed for the purpose[] .
-On the other hand, the sampling calorimeter becomes popular in large-scale high energy experiment mainly due to its cost-effectiveness.
-The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that obtain information on it.
-Since the energy-deposit in the passive convert can not be measured, its fluctuation, called sampling fluctuation, determines the energy resolution of the  calorimeter, which is generally worth than that of the detector made of crystals.
-%mainly determined by the  which causes a limitation of energy resolution,  
-%Even though the energy deposit in the passive converter is not detected which is related to the 
-%measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
-%Due to the fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution. 
-It is possible, however, to optimize configuration of a large-size detector by selecting the converters and the counters among various candidates those are easily fabricated with low costs.
-A 5m-long cylindrical calorimeter made of alternating lead and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
+The EM calorimeter has played an important role in experimental studies on the nuclear and particle physics.
+Various materials have been developed for better energy and timing resolution so far~\cite{Calorimeter}.
+On the other side, the sampling calorimeter becomes popular in the large-scale high energy experiment mainly due to its cost-effectiveness.
+The sampling calorimeter consists of alternating passive converters that generate the EM shower and active counters that measure the energy deposit.
+Since the energy deposit in the passive convert is not measured, the fluctuation of energy deposits in the converter and the counter, called sampling fluctuation, determines the energy resolution of the  calorimeter.
+The sampling fluctuation can be optimized by combining the converter and the counter with a specific portion.
+A 5-m-long cylindrical calorimeter made of alternating lead and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
 
-%The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}.
-%In addition, the fluctuation becomes not so important for high energy gammas owing to large number of shower particles.
-%When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.
-%There are many efforts to develop new types of calorimeter, and a fine-segmented sampling calorimeter is in the line[].
+The layer structure of the sampling calorimeter enables us to measure the individual profile of the shower along to the beam direction, and the incident angle can be estimated by correlating energy deposits on neighboring layers.
+The measurement of the incident angle largely benefits the background rejection.
+Of particular, The incident angle will be an important tool for the KOTO experiment~\cite{KOTOproposal}.
 
-A layer structure of the sampling calorimeter enables us to measure the individual profiles of the shower along to the accumulating direction, and we can estimate the direction of incident gamma by connecting the center of them.
-When we  decide momentum vector of incident $\gamma$ by using only the calorimeter, it is expected more reliable event reconstruction with better background rejection.
-In a particular experiment, KOTO, aiming to detect the final state existing only single $\pi^0$ without any other particles, the experimental method will be an important tool for the successful measurement.
+Since the EM shower is evolving via stochastic processes, the incident angle would be reconstructed with a certain angular resolution.
+Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution.
+The evolution of the EM shower is generated with the GEANT4 and $\XGB$ was used to reconstruct the incident angle.
 
-%Even though the sampling fluctuation makes limitation on the energy resolution in this energy range, there is a merit to construct momentum vector of $\gamma$ by using only the calorimeter without additional
-
-%We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV. 
-%measure not only energy but also incident angle of photon.
-Considering a stochastic process in shower generation, there is a certain limitation of the detection resolution.
-Also, the effect of the sampling fluctuation is a matter in medium energy photons in range 100 MeV to few GeV photons.
- %information about its generation position. Since the $  Participating in event reconstruction
-
-%experiment to have a motivation on developing a detector configuration enable to measure the incident direction.
-
-The KOTO experiment, being performed at the J-PARC in Japan, aims at searching for the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay~\cite{KOTOproposal}.
-This decay is very clean in theoretical calculatio and has a large potential to access the new physics beyond the Standard Model~\cite{NewPhys}.
-However, current experimental sensitivity is still far from the SM expectation mainly due to its extremely small branching fraction and very weak kinematic condition to define a signature of the decay\cite{KOTO}.
-
-Considering negligibly small detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$.
-The KOTO utilizes undoped Cesium Iodide (CsI) crystals to measure the incident energies and positions of the $\gamma$~\cite{CsI}.
-%An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons.
-In order to reconstruct $\pi^0$ from the detected two $\gamma '$s, we need an assumption that they are generated from the single $\pi^0$ decaying at the beam axis.
-This assumption works correctly with $K_L$ beam having small-size cross-section and hermetic veto counters assuring the two-$\gamma$ final state
-
-There are, however, large amount of background events have a possibility to become the two-$\gamma$ final state because of various reasons.
-For example, the $K_L \rightarrow \pi^0 \pi^0$ decay will be the two-$\gamma$ event when we can not detect additional two $\gamma$'s due to limited detection efficiency of detectors.
-Considering the 8 orders of larger branching ratio of the $K_L \rightarrow \pi^0 \pi^0$ decay compared to that of the $K_L \rightarrow \pi^0 \nu \bar{\nu}$, it is a challenging to achieve the required detection efficiency which is closely connected to the achievable experimental sensitivity in terms of accidental loss.
-If the remained two $\gamma$'s are generated from different $\pi^0$, the reconstructed $\pi^0$ will be differ from another results from obtained by newly obtained the momentum vectors.
-We can reject so-called odd-pairing  of the $K_L \rightarrow \pi^0 \pi^0$ decays.
-%without strict veto requirement.
-%strict detection efficiency of the additional $\gamma$'s.
-
-In addition, small fraction of neutrons those are dominant component of the $K_L$, can interact with detectors and produce $\pi^0$ or two-$\gamma$-like events.
-Those events are rejected by the shower shape analysis looking into energy sharing among the finely segmented CsI crystals, and the rejection power will be greatly improved if we could use the additional information on the $\gamma$'s.
-
-%$contaminated
-
-%considerable background event still be the two-$\gamma$ final state
-
-%There as in addition to the detection variables.
-This means that we would get a wrong $\pi^0$ in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
-With a new information, incident angle, we can judge a validity of the reconstructed $\pi^0$.
-%In order to reconstruct a  $\pi^0$ from obtained information of the two gammas 
-%In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at the beam axis.
-This reconstruction would be failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately.
-% In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement.
-By requiring a consistency between two vertices reconstructed with different observables, we can select genuine single $\pi^0$ decay rejecting wrong pairs due to various sources such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on.
-It also enables us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis.
-We can expect similar rejection against $K_L \rightarrow \gamma \gamma$ decays when the $K_L$ deviate form the beam center due to scattering.
-
-%For the angle measurement of gamma, we should get information about the spatial profile of shower particles generated in the EM-Cal.
-This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions.
-Since the electromagnetic shower development is a stochastic process, there should be a limitation on the resolution of the measurement.
-We have studied about the angle measure with a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator.
-The have performed an feasibility study on the angle measurement to estimate feasibility  achievable angular resolution in ballpark figure and clarify the items we have to solve for better performance.
-
-%the angular measurement of incident gamma. %could be a good candidate of the calorimeter as describe in this paper.
+The sec~\ref{sec:ems} sec~\ref{sec:res} sec~\ref{sec:sum}
 In the following section, the configuration of detector and Monte Carlo simulation for electromagnetic shower generation will be given.
@@
 \section{ELECTROMAGNETIC SHOWER}
+\label{sec:ems}
 We started the study with a detector setup consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter.
-% as shown in Fig.~\ref{fig:det_conf}.
-The electromagnetic shower mainly generated at the lead sheet (passive component) due to its short radiation length ($X_0 = 5.6~{\rm mm})$ and the information of the shower particles is obtained by using the scintillator (active  component).
 The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
@@
 \begin{figure}[!hbt]
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
 \includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
@@
 Figure~\ref{fig:Evt_Dis} shows a typical event display describing the energy deposit to the each scintillator strips in both of X-Z and Y-Z plane for 1-GeV $\gamma$ entering in perpendicular to the center of the detector ($\theta=0$ and $\phi=0$).
-%We can get an three-dimensional information on the shower development combining them and will use them as inputs of the machine learning package, $\XGB$.
-%This information indicates the shower development, and will be used as an input of the machine learning package, $\XGB$. 
-%We can get the shower profiles from energy deposits in individual strips arranged in the 3-dimension.
-Figure XXX shows a event display for 1 GeV gamma entering with $\theta =0$ in X-Z and Y-Z planes.
-The amount of energy deposit to each strips are expressed by the darkness (color online).
 
 \begin{figure}[!hbt]
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
 \includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
 \includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
-
 \caption{Distribution of energy deposit to the each scintillator strips in X-Z plane (Left) and Y-Z plane (Right) for 1-GeV $\gamma$ entering perpendicularly to the detector ($\theta=0$ and $\phi=0$).}
@@
 
-%With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from the
-
-%energies are in range from hundred MeV to few GeV by considering the KOTO experiment.
-
-%its origin is defined as the centers of the central strips both of the X- and Y- There generation position is the centers of both of the X- and Y- strip moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
-With the configration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them.%The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver.
-xxx) with the standard EM sub-packages ~\cite{GEANT4}.
-
-%{\it I will describe the coordinator and the gamma enter to the center of strips}
-%The contribution of the hadronic interaction is taken into account with $\rm{FTFP\_BERT}$ package.
-The materials used in detector construction are selected from the Geant4 NIST material database: $\rm{G4\_Pb}$ for the lead and $\rm{G4\_PLASTIC\_SC\_VINYLTOLUENE}$ for the scintillator material.
-
-%\subsection{Properties of generated shower}
-% moliere rad, visible ratio graph
-% energy resolution (+as a function of E)
-% gamma beam energy에 따라 backsplash가 만드는 event veto
-% + incident angle에 따라?
-%Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
-%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$).
-
-%Figure~\ref{fig:EMshower} shows side (left) and top view (right) of energy deposit in the each strips for $\gamma$ entering the center of the detector with energy of 1 GeV and incident angle of 10 degrees and azimuthal angle of 0 degree .
-By using this profiles along with the alternating X- and Y-direction, we can reconstruct incident angle of the $\gamma$ after studying its nature with the $\XGB$ package.
-
 The GRANT4 can provide reliable results on the electromagnetic shower produced by the incident $\gamma$.
-%by usis well produced by showers show typical distributions both of longitudinal and transverse directions.
-Figure~\ref{fig:Longitudinal} shows longitudinal distribution of average sum of the energy deposit in strips of each counter layers regardless the direction of arrangement.
-%Considering the EM shower is generated mainly at the converter, the both distributions of the converter and counter are identical and can be expressed by two parameters,
 Its longitudinal profile depends on incident energy and can be expressed \cite{Longo} by the three parameters as following;
-%When we ignore large radiation of the scintillator, the profile can
-%projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
-%can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
 \begin{equation}
     F(E,t)=A  t^\alpha e^{-bt},
-    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
 \end{equation}
@@
 In the case of the sampling calorimeter, however, the energy deposit on the converters and counters is caused by multiple processes and its fraction is changed along with the shower develpoment.
-%is changed according to the shower depth because there is a change of energy depositing process. 
-%and uwe focus only on the energy deposit 
-%the probability of the shower generation is much different between the counter and converter.
-As a result, the ratio of the energy deposit in counter and in converter changes according to the layer position as shown in Fig.~\ref{fig:Longitudinal} (right).% because there are multiple process of which probability changes according to development.
+
+As a result, the ratio of the energy deposit in counter and in converter changes according to the layer position as shown in Fig.~\ref{fig:Longitudinal} (right).
 In order to describe the shower profile in the sampling calorimeter, we need to take into account the layer dependent of the energy deposit.
 Since we will use the simulated results only for current study on angle measurement, we did not proceed any further analytic study on the process.
-%As a results, the Eq.
-1 needs an additional correction factor ...
-to express the obtained results more correctly.
-%We can take into account the changes by using layer-by-layer structure of the detector.
-%({\it Shall we investigate energy dependency of the parameters ?)}% Considering the EM shower is generated mainly at theIt is natural that the distributions on converter and counter are identical.
-%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
-%\begin{equation}
-    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
-%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
-%\end{equation}
-%or
-%\begin{equation}
-    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
-%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
-%\end{equation}
-%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.
 
 \begin{figure}[!hbt]
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
 \includegraphics[width=0.48\textwidth]{figures/LongProfile.jpg}
@@
 The first three bins show large radius because of large contribution of shower particles generated opposite to the incident direction.
-
-%difference of $\rho_M$ for different configurations of the detector and its dependency on the detector layer.
-We need to notice the spread of shower is different along to the its development similar to the ratio of the energy deposit mentioned above.
-We can take into account the complicated response of the sampling calorimeter by using the individual energy deposit of the strips as inputs of the machine learning for the angle reconstruction.
 
@@
 \section{SUMMARY}
+\label{sec:sum}
 We studied a possibility to measure incident angle of the medium-energy $\gamma$ by using a finely segmented sampling calorimeter.

### 2022-01-04 paper.tex
updates

@@
 The angular resolution weakly depends on the width of the strips up to 15 mm and becomes worse with the increasing width.
-It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length of the detector.
+It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length (5$X_{0}$) of the detector.
 The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.1+1.2$/ \sqrt{E_\gamma}$.
@@
 Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution.
-The evolution of the EM shower is generated with the GEANT4 and $\XGB$ was used to reconstruct the incident angle.
+The evolution of the EM shower is generated with the GEANT4, and $\XGB$ was used to reconstruct the incident angle.
 
-The sec~\ref{sec:ems} sec~\ref{sec:res} sec~\ref{sec:sum}
-In the following section, the configuration of detector and Monte Carlo simulation for electromagnetic shower generation will be given.
-In the section III, we will describe how to reconstruct incident angle from the generated detector response by using one of the most attractive toolkit of the machine learning; $\XGB$.
-Finally, we will summarize our study briefly.
+In sec~\ref{sec:ems}, generic explanation of the EM shower and its evolution.
+We describe the reconstruction and angular resolution of the sampling calorimeter in sec~\ref{sec:res}.
+We summarize the study in sec~\ref{sec:sum}.
 

### 2022-01-24 paper.tex
update

@@
 \begin{abstract}
-We present studies on the detector configuration to measure the incident angle of the $\gamma$, which has the energy ranging from hundred MeV to few GeV using a new sampling calorimeter.
-The sampling calorimeter consists of alternating 1-mm-thick lead sheets producing the electromagnetic (EM) shower and strips of 5-mm-thick plastic scintillators measuring the energy deposit by the shower particles.
-The strips are arranged along to the alternating horizontal and vertical directions to measure the transverse profile by combining the both directions at a given longitudinal position.
+We present studies on the detector configuration to measure the incident angle of the $\gamma$ with energies ranging from hundred MeV to few GeV using a new sampling calorimeter.
+The sampling calorimeter consists of alternating 1-mm-thick lead plates producing the electromagnetic (EM) shower and strips of 5-mm-thick plastic scintillators measuring the energy deposit by the shower particles.
+The strips are arranged along the alternating horizontal and vertical directions to measure the transverse profile by combining both directions at a given longitudinal position.
 In this paper, we used the GEANT4 to simulate energy deposit to the individual strips of the calorimeter, and the $\XGB$ to reconstruct the incident angle from energy deposits.
@@
 It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length (5$X_{0}$) of the detector.
-The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.1+1.2$/ \sqrt{E_\gamma}$.
+The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.2+1.1$/ \sqrt{E_\gamma}$.
 
@@
 \label{sec:mot}
-The EM calorimeter has played an important role in experimental studies on the nuclear and particle physics.
+The EM calorimeter has played an important role in experimental studies for the nuclear and particle physics.
 Various materials have been developed for better energy and timing resolution so far~\cite{Calorimeter}.
@@
 The sampling fluctuation can be optimized by combining the converter and the counter with a specific portion.
-A 5-m-long cylindrical calorimeter made of alternating lead and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
+A 5-m-long cylindrical calorimeter made of alternating lead plates and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
 
-The layer structure of the sampling calorimeter enables us to measure the individual profile of the shower along to the beam direction, and the incident angle can be estimated by correlating energy deposits on neighboring layers.
+The layer structure of the sampling calorimeter allow one to measure the individual profile of the shower along the beam direction, and the incident angle can be estimated by correlating energy deposits on neighboring layers.
 The measurement of the incident angle largely benefits the background rejection.
@@
 Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution.
-The evolution of the EM shower is generated with the GEANT4, and $\XGB$ was used to reconstruct the incident angle.
+The evolution of the EM shower is generated with the GEANT4, and the $\XGB$ was used to reconstruct the incident angle.
 
-In sec~\ref{sec:ems}, generic explanation of the EM shower and its evolution.
+In sec~\ref{sec:ems}, generic explanation of the EM shower and its evolution are described.
 We describe the reconstruction and angular resolution of the sampling calorimeter in sec~\ref{sec:res}.
@@
 \label{sec:ems}
-We started the study with a detector setup consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter.
-The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
-The lead sheet has a cross-section of  500 mm $\times$ 500 mm and each scintillator strips of 500 mm $\times$ 15 mm  being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}.
-Total number of alternating layers is 105 which corresponds to 20 radiation length (20 Xo) and possible to contain all of the shower particles generated by $\gamma$ in the region of medium energy (from  100 MeV to few GeV).
 
@@
 \includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
-
-\caption{ The first trial of detector setup for simulation study on angle measurement. It is a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. }
+\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter. It consists of alternating lead plates and scintillator strips.  }
 \label{fig:det_conf}
@@
 
-The generation of incident $\gamma$ and its interaction with detector materials was simulated by using the GEANT4 package (ver. xxx) with the standard EM sub-packages~\cite{GEANT4}.
-The $\gamma$ entered the center of the detector and moved to the positive direction of Z-axis, where the surface of the first layer is defined as a starting point (Z=0).
-Its incident angle is defined as the polar angle ($\theta$) along to the Z-direction, that is, $\theta = 0$ for the $\gamma$ enters perpendicular to the detector surface.
-%The generated energies are in range from hundred MeV to few GeV which is interested to the KOTO experiment.
-Figure~\ref{fig:Evt_Dis} shows a typical event display describing the energy deposit to the each scintillator strips in both of X-Z and Y-Z plane for 1-GeV $\gamma$ entering in perpendicular to the center of the detector ($\theta=0$ and $\phi=0$).
+The sampling calorimeter was designed as alternating 1-mm-thick lead plates for passive converters and 5-mm-thick strips of the plastic scintillator for active counters.
+The cross section of the lead plate and the scintillator is 525 mm $\times$ 525 mm and 15 mm $\times$ 525 mm, respectively.
+Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}.
+The total number of alternating layers is 105, which corresponds to 20$X_{0}$ to make it possible to absorb whole products from the EM shower ranging from 100 MeV to few GeV energy.
 
 \begin{figure}[!hbt]
-\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
-\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
-\caption{Distribution of energy deposit to the each scintillator strips in X-Z plane (Left) and Y-Z plane (Right) for 1-GeV $\gamma$ entering perpendicularly to the detector ($\theta=0$ and $\phi=0$).}
+%\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
+%\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
+\includegraphics[width=0.48\textwidth]{figures/SingleEventXZHit.pdf}
+\includegraphics[width=0.48\textwidth]{figures/SingleEventYZHit.pdf}
+\caption{ An event display of the energy deposit to each scintillator strip in the $x$--$z$ plane (left) and the $y$--$z$ plane (right) for the 1~GeV $\gamma$ perpendicularly entering to the detector ($\theta=$~0).}
 \label{fig:Evt_Dis}
@@
 
-The GRANT4 can provide reliable results on the electromagnetic shower produced by the incident $\gamma$.
-Its longitudinal profile depends on incident energy and can be expressed \cite{Longo} by the three parameters as following;
-\begin{equation}
-    F(E,t)=A  t^\alpha e^{-bt},
-\end{equation}
-where t is the position of scintillator strips along the Z-direction.
-As shown in Fig.~\ref{fig:Longitudinal}, the Eq.
-1 describes the obtained average energy deposit on each layer of scintillator strips reasonably.
-In the case of the sampling calorimeter, however, the energy deposit on the converters and counters is caused by multiple processes and its fraction is changed along with the shower develpoment.
-
-As a result, the ratio of the energy deposit in counter and in converter changes according to the layer position as shown in Fig.~\ref{fig:Longitudinal} (right).
-In order to describe the shower profile in the sampling calorimeter, we need to take into account the layer dependent of the energy deposit.
-Since we will use the simulated results only for current study on angle measurement, we did not proceed any further analytic study on the process.
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/LongProfile.jpg}
-\includegraphics[width=0.48\textwidth]{figures/LayerVisibleRatio.jpg}+
-\caption{Generated average energy deposit on the scintillator strips along Z axis(left) and visible ratio for each layer.}
-\label{fig:Longitudinal}
-\end{figure}
-
-On the other hand, the lateral spread of the shower
-%is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers.  This spread 
-is expressed as the the Molière radius defined ~\cite{PDG} as 
-\begin{equation}
-R_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
-\end{equation}
-where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
-Since the sampling calorimeter contains different materials placed at the different localized positions, we defined the $R_M$ as the radius of cylinder containing 90\% of the energy deposit instead of using the Eq.
-(2).
-The left panel of Figure~\ref{fig:Moliere_vis} shows energy deposit per each layer (black line) and integrated energy deposit up to the layers.
-We can deduce the Molière radius as 70 mm, which is largely depends on the position of its measurement.
-The right panel of Figure~\ref{fig:Moliere_vis} shows the radius as a function of scintillator layer, which increases along the shower depth.
-The first three bins show large radius because of large contribution of shower particles generated opposite to the incident direction.
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.44\textwidth]{figures/Edep_R.jpg}
-\includegraphics[width=0.48\textwidth]{figures/Moliere_layer.jpg}
-\caption{Left:Energy deposit for given radius as a differential(black line) and integral distribution(red line) Right: Moliere radius as a function of ID of scintillator-strip layers.}
-\label{fig:Moliere_vis}
-\end{figure}
-
-With the detector configuration shown in Fig.~\ref{fig:det_conf}, we can get three dimensional information on the showers.
-By using the obtained data as an input of the machine learning package, we can extract the incident angle of the $\gamma$ as explained following section.
-%When we apply the three dimensional information on the generated shower profile, we can reconstruct incident $\gamma$ more correctly by integrating the energy deposit. 
-%For simplicity in numerical calculation, %For the sampling calorimeter consisting of different materials, 
-%let us define the Molière radius as the radius of cylinder containing 90\% of shower energy.
-As shown in Fig.~\ref{fig:Moliere_vis}, the configuration of 1-mm lead and 5-mm scintillator shows $\rho_M=70$ mm in average which changes with the shower depth.
-%That is, we can expect an improvement on separating two gammas closely incident to the calorimeter.
-We will study on this subject and not discuss any more in this paper.
-%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal
-
-%The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
-%\begin{equation}
-%R = { \frac{E_{act}} {E_{act}+E_{pas}}},
-%\end{equation}
-%where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively.
-This visible ratio is roughly given by the ratio of material budget between the converter and the counter.
-%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
-%by thickness of the converter.
-It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter.
-%As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon.
-However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers.
-Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too).
-When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX.
-This is because the number of low energy electrons and positrons penetrating the lead sheet is increased in case of thinner converter.
-As a result of the increasing probability, the sampling fluctuation becomes small and the energy resolution improved as a result.
-%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.
+The interaction of incident $\gamma$ with the detector was simulated using the GEANT4 (ver.
+4.10.06) with the standard EM sub-packages~\cite{GEANT4}.
+The surface of the detector is defined as $z=$~0, and the $\gamma$ starts to interact with the detector.
+the incident angle of the $\gamma$ is defined as the polar angle ($\theta$) along the $z$ direction, where $\theta = 0$ case denotes that the $\gamma$ perpendicularly enters into the detector surface.
+Figure~\ref{fig:Evt_Dis} shows the event display illustrating the energy deposit on the each scintillator strip in both of $x$--$z$ and $y$--$z$ planes for the 1~GeV~$\gamma$ with $\theta = 0$.
 
 %\begin{figure}[!hbt]
-%\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
-%\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
-%\caption{Visible ratio of the sampling calorimeter for different configuration (Left) and energy resolution as a function of incident $\gamma$ energy (right).}
-%\label{fig:energy_res}
+%\includegraphics[width=0.48\textwidth]{figures/LayerVisibleRatio.jpg}
+%\includegraphics[width=0.48\textwidth]{figures/Moliere_layer.jpg}
+%\caption{  \textcolor{red}{plots should be updated} Sampling fraction (left) and Moliere radius (right) from 1 GeV %$\gamma$ events ($\theta=0$) for each layer}
+%\label{fig:sc_prop}
 %\end{figure}
 
-%\input{Sec2.tex}
-%\section{method}
-%\label{sec:ana}
-
-%\subsection{Geant4 simulation}
-%In this paper, the photon shower and corresponding detector responses, the prerequisites for the machine learning inputs, are simulated based on the Geant4 framework.
-Among several physics packages, the $\rm{FTFP\_BERT}$ physics package is used for electromagnetic and hadronic interactions as it is generally recommended for the high energy physics calorimetry.
-
-%The materials used in detector construction are selected from the Geant4 NIST material database: $\rm{G4\_Pb}$ for the lead and $\rm{G4\_PLASTIC\_SC\_VINYLTOLUENE}$ for the scintillator material.
-
-%\subsection{Detector construction}
-%We constructed a prototype sampling electromagnetic calorimeter with alternative stacking of thin Pb sheets and scintillator strips.
-A Pb sheet has a dimension of 50 cm (w) $\times$ 50 cm (l) $\times$ 1 mm (t).
-And a single layer of scintillator plate consists of 25 long scintillator segments, and each segment has a dimension of 2 cm (w) $\times$ 50 cm (l) $\times$ 5 mm (t).
-The full geometry consists of 105 layers  which is corresponding to 20 $X_0$.
-In order to investigate the detector properties and test the reconstruction performance of the indicent angle of $\gamma$, we generated $\gamma$ beam data samples with several incident angles and energies.
-%In this study, we utilized a physics package $FPFT\_BERT$ for the hadronic and electromagnetic interactions
-%We started the study with a setup of sampling calorimeter consisting of alternating lead sheet and strips of plastic scintillator as shown in Fig.~\ref{fig:det_conf}.
-The thickness of lead is 1 mm and scintillator is 5 mm, respectively.
-The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm.
-By arranging the strips in X- and Y-direction alternatively along Z-direction.
-The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.
-With the configuration, we can get shower profiles in X-Z and Y-Z planes in turn, and estimate the incident angle from them.
-The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully.
-
-%\begin{figure}[!hbt]
-%%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
-%\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
-
-%\caption{ The first trial of detector setup for simulation study on angle measurement. It is a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. }
-%\label{fig:det_conf}
-%\end{figure}
-
-%\subsection{Electromagnetic shower Generation}
-%\subsection{Properties of electromagnetic shower (EM shower)}
-%We generated the EM shower generated inside the detector with GEANT4, which provides reliable results for them polish-up later).
-
-%\subsection{Properties of electromagnetic shower (EM shower)}
-
-%In general, the less the photon shower develops in the transverse direction, the more separable the photon clusters, and the higher the visible ratio, the better the energy resolution.
-However, these properties are incompatible as they have strong inverse correlation.
-For the trade-off configuration, we investigated the Molière radius and the visible ratio with several configurations.
-
-% 어떤 configuration, energy? 등등
-% 2.5, 5, 10, 15, 20 mm for scint., 0.5, 1, 2 mm for lead 1GeV gamma
-% For energy resolution, 100 MeV step 100MeV ~ 2GeV gamma
-
-%\subsection{Backsplash}
-% backsplash particle이 veto signal을 만들어 accidental event loss를 만든다.
-% incident photon의 에너지와 각도를 바꿔가며 front surface로 빠져나오는 backsplash particle의 개수를 카운팅
-% 1개 이상의 backsplash particle이 있으면 veto에 counting
-
-%\subsection{XGBOOST: A toolkit for machine learning}
-%\label{sec:anaML}
-%Among many packages for machine learning in the high energy physics area~\cite{ATLAS:2020iwa}, we used the $\XGB$, supporting a scalable tree boosting system~\cite{xgboost:2016}.
-The $\XGB$ package is used to reconstruct the incident angle of incident $\gamma$ particles with deposit energies in the each channel, where secondary particles of the EM shower raise signals.
-Input data for the $\XGB$ are deposit energies for whole channels including zero-energies to tally with the requirement that the number of input data should be identical.
-For the $\XGB$ to reconstruct the angle, the training procedure for the $\XGB$ needs to be preceded.
-The training procedure helps the $\XGB$ study how $\gamma$ interacts with the detector and deposits the energy to the each channel with respect to the incident angle for a given $\gamma$ energy.
-Simulations are done with the uniform incident polar angle ($\theta$) distribution from 0 to 50 degree and the uniform azimuthal angle ($\varphi$) from 0 to 360 degree for the training, which makes the $\XGB$ possible to reconstruct events having 0~$<\theta<$~50~degree and 0~$<\varphi<$~360~degree.
-The reconstruction of $\theta$ by the $\XGB$, completing the training procedure, is tested with the fixed $\theta$ and uniform $\varphi$ from 0 to 360 degree.
+%Figure~\ref{fig:sc_prop} shows the sampling fraction and the Moliere radius~\cite{PDG} for each layer with 1~GeV $\gamma$.
+In this paper, Moliere radius is defined as the distance including 90\% of (deposited) energy from the center of energy.
+The visible ratio (Moliere radius) decreases (increases) with increasing layer ID.
+It is, therefore, estimated to have better energy resolution and position separation with front layers.
+Note that the very front few layers are largely affected by secondaries going backward.
 
@@
 
-The incident angle of the $\gamma$ can be estimated as a results of machine learning by using the $\XGB$, which is one of the popular packages supporting a scalable tree boosting system~\cite{xgboost:2016}.
-We used energy deposits on each scintillator strips as input data for the $\XGB$, and the packages connects the relationship among the input data to estimate the incident angle.
-** a little detail one or two senteces***
+The incident angle of the $\gamma$ is reconstructed with the $\XGB$, which is one of the popular machine learning toolkit providing a scalable tree boosting system~\cite{xgboost:2016}.
+The machine learning is required to be trained.
+The feature, characteristic of a phenomenon, and the target, output to be predicted, are essential inputs for the training.
+The machine learning correlates each feature with the corresponding target for different features.
+Trained machine learning takes measured features and gives the target based on correlations which are made during the training.
+In this paper, the feature corresponds to energy deposits on each scintillator strip and the target corresponds to the incident angle of the $\gamma$.
 
-%are deposit energies on each scintillator strip by the generated shower particles.
-It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical.
-As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.
-({\it This part should be updated)}
-
-For the training of the $\XGB$, we generated $\gamma$'s uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle ($\varphi$) for given energy (training sample).
-By using another data set (testing sample) which was generated at a fixed polar angle, we estimated performance of angular reconstruction of the detector.
-The number of generated $\gamma$ was
-$2\times10^5$ for the training sample and $1\times10^5$ for the testing sample, respectively.
-
-%\subsection{Machine learning configuration}
-%The configuration of the $\XGB$ can be organized with five parameters, described in Tab.~\ref{tab:XgbPar}.
-The parameters are selected as one providing better angular resolution.
-It is found that the Max.
-depth mostly affects the angular resolution, and the resolution is not enhanced for Max.
-depth~$>$~15 any more.
-It is also worth mentioning that configurations with N\_estimators larger than 1000 do not provide better resolution with the Max.
-depth~=~15.
-The angular resolution of the reconstruction is defined as the standard deviation of Gaussian function, whose parameters are evaluated by fitting the reconstructed angle distribution.
-Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ distribution with respect to each incident $\theta$ with described training parameters.
-The angular resolution for all $\theta$ is estimated to be 1.3~degree.
-
-%\begin{figure}[!hbt]
-%\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
-%\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution.
-The standard deviation of all Gaussian functions are estimated to be 1.3 degree.}
-%\label{fig:angle_reco_def}
-%\end{figure}
-
-%\begin{table}[hbt!]
-%\centering
-%\caption{Parameterization of the $\XGB$}
-%\begin{tabular}{cccc}
-%\hline 
-%Parameter & Function & Default value & Used value \\ \hline 
-%N\_estimators & The number of decision trees & N.A. & 1000 \\  
-%Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
-%Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
-%Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
-%Gamma & Requirement on minimum loss function & 0 & 0 \\ 
-%\hline
-%\end{tabular}
-%\label{tab:XgbPar}
-%\end{table}
-
-%\subsection{Detector dimension}
-%\subsection{Angle reconstruction using Machine Learning}
-
-%With the results of the $\XGB$ by using the training sample generated with the uniform distributions in both of polar and azimuthal angles, we estimated the incident angle of photons generated with a fixed value for a given energy.
-Figure~\ref{fig:angle_10degree} shows the distribution of reconstructed angles for 1-GeV $\gamma$ entered detector with 10 degrees of incident angle.
-%The Gaussian distribution (black solid line) provides the proper mean value,  the $\XGB$ can provide correct answer.
-We can get proper mean value of the distribution, however, it has heavier tail compared to that of the Gaussian distribution.
-In order to describe the obtained result more correctly, we tried to fit it with the Generalized Gaussian (GG) function.
+If the feature for the training is biased, the prediction of the $\XGB$ would be correspondingly biased as the $\XGB$ reliably believes there are no biases in all features given by a user.
+To minimize this, the incident angle is uniformly generated in the range 0 to 50 degrees for incident polar angle ($\theta$) and 0 to 360 degrees for incident azimuthal angle ($\varphi$), which makes the $\XGB$ train all features we are interested in.
+The number of samples for the training is $2\times10^5$ considering computing resources.
+To test the reconstruction of the incident angle, the incident angle is generated with the fixed $\theta$.
+Note that the incident energy is known.
 
@@
 \includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
-\caption{ (Color online) Reconstructed $\theta$ with respect to 10 degrees of incident $\theta$.
-The gaussian function can not describe the tail region (red dotted line).
-The generalized gaussian function (black solid line) shows much better agreement with the obtained result.}
+\caption{ Reconstructed $\theta$ distribution for $\theta=$~10~deg events.
+The distribution is fitted with the Gaussian function and the Generalized Gaussian function.
+The Generalized Gaussian function provides better description for both tails.}
 \label{fig:angle_10degree}
@@
 
-%In order to include the heavier tail more correctly in the performance study, we tried to fit the distribution with two different function; one is a convolution of a Lorentz and Gaussian distribution (Voigt function) and the other is a Generalized Gaussian function.
-%The Voigt fuction expressed as 
-%\begin{equation}
-%V(x; \sigma, \gamma) = \int_{- \infty}^{\infty} G(x';\sigma)L(x-x';\gamma) dx',
-%\end{equation}
-%becomes to be Lorentz distribution $L(x; \gamma)$ in case of $\gamma$=0 
-%\begin{equation}
-%L(x;\mu, \gamma) = {\gamma \over {\pi ((x-\mu)^2 + \gamma^2)}}
-%\end{equation}
-%of peak position at x=$\mu$ in case of $\sigma$ =0 
-%and to be Gaussian distribution $G(x;\sigma)$
-%\begin{equation}
-%G(x;\mu, \sigma) = {1 \over {\sqrt{2 \pi} \sigma}} e^{-(x-\mu)^2/2\sigma^2} 
-%\end{equation}
-%when the $\gamma$ equal to be zero. The function is available in the analysis framework of the ROOT~\cite{Voigt}, and  improves the fitness a little.
-
-The GG function provides more flexible modeling to data than the Gaussian can do by introducing an additional parameter to describe the shape of distribution.
-This function was suggested by Subbotin~\cite{Subbotin} in 1923 treating the accidental errors not only to be continuous but also to be expanded in the power series.
-Its probability density function is expressed as
-%has received considerable attention especially at the image processing studies\cite{Dytso},  
-%Among various parametrization of the function, we take that its probability density distribution (pdd) is given as~\cite{Gonzalez}  
+Figure~\ref{fig:angle_10degree} shows reconstructed $\theta$ for 1~GeV $\gamma$ with $\theta=$~10~degrees.
+The distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
+GG function provides better description for both tails of the distribution.
+The GG function can be expressed as
 \begin{equation} 
-  % GG(x;\mu, \sigma,     p) = {C_p \over \sigma} e^{-{|x-\mu|^p}/{2 \sigma ^p}}, 
-   %f(x; \mu, \alpha, \beta) = {\beta \over {2 \alpha \Gamma(1/\beta)}} e^{-(|x-\mu|/\alpha)^\beta} , 
-     f(x; \mu, \alpha, \beta) = \frac{\beta}{2 \alpha \Gamma(1/\beta)} e^{-(|x-\mu|/\alpha)^\beta} , 
-%   f(x; \mu, \alpha, \beta) = {\beta \over {2 \alpha \Gamma (1/\beta)}} e^{-(|x-\mu|/\alpha)^\beta} , 
+f(x; \mu, \alpha, \beta) = \frac{\beta}{2 \alpha \Gamma(1/\beta)}e^{-(|x-\mu|/\alpha)^\beta}
 \end{equation}
-where $\beta$ is the so-called shaping factor
-%Also  
-%\begin{equation}    
-%    A ={ {\beta p}  \over {2\Gamma(1/p)}},
-%\end{equation}
-and the $\Gamma(.)$ is the gamma function.
-It becomes the Laplace distribution if $\beta$=1 
-\begin{equation}
-LP(x;\mu, \sigma) = \frac{1}{\sqrt{2}\sigma} e^{-{\sqrt{2}{|x-\mu|} / \sigma}} 
-\end{equation}
-and Gaussian distribution
-\begin{equation}
-G(x;\mu, \sigma) = \frac{1}{\sqrt{2 \pi} \sigma} e^{-(x-\mu)^2/2\sigma^2} 
-\end{equation}
-for $\beta$=2.  The second moment of the GG function is given as
-\begin{equation}    
-    E[X]^2  = \alpha^2 \frac{\Gamma(3/p)}{\Gamma(1/p)}  \equiv \sigma^2 , 
-\end{equation}
-which becomes the variance of the Gaussian distribution in case of the $\beta$=2.
-This value can be interpreted equal footing regardless of the $\beta$-values, and will be used as the angular resolution for given detector configuration from now.
-%we can treat it as a width of the distribution which contains same meaning %regardless of the p-values.
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.45\textwidth]{figures/PDF_Gonzalez.pdf}
-\includegraphics[width=0.45\textwidth]{figures/Int_Gonzalez.pdf}
-\caption{ The probability density distribution (left), and their integrated distributions (right) of the generalized gaussian (GG) function in the case of  $\mu = 0$ and $E[X]^2 = 1$ for various shaping paramete $\beta$.
-It changes from the Laplace ($\beta$=1) to the Gaussian ($\beta$=2) distribution according to the $\beta$.
-On the other hands, their integral probability density show similar distributions implying its second moment can be interpreted equally regardless of the $\beta$ values in the range of $1<\beta<2$.}
-\label{fig:GG_pdf}
-\end{figure}
-
-Figure~\ref{fig:GG_pdf} (left) shows the probability density distribution of the GG function in the case of $\mu = 0$ and $E[X]^2 = 1$ for different $\beta$ values from 1 to 2.
-We can figure out the change from the Laplace ($\beta = 1$) to the Gaussian distribution ($\beta=2$).
-As shown in the right plot of the Fig.~\ref{fig:GG_pdf}, the integrated probability for 1$\sigma$ interval becomes to be from 68.3$\%$ ($\beta=2$) to 75.7$\%$ ($\beta=1$).
-In the case of $\beta=1.5$ as obtained from the data fitting, it is to be 71.2$\%$ which is just 4$\%$ larger than that of the Gaussian.
-Moreover, a statement of "1.7$\sigma$ interval contains 91$\%$ of entries" can be applied in range of $1<\beta<2$, thus we will use the $\sigma$ as a definition of the angular resolution in this paper.
-%When we take an angular resolution as the width of fitted distribution, it is determined by the two parameters, $\sigma$ and p.
-Figure~\ref{fig:GG_pdf} shows distributions of probability density (left) and integrated the density for $\sigma =1$ with changing value of p from 1.0 to 2.0.
-We can parameterize the angular resolution, $\sigma_{R}$ as
-%\begin{equation}
-%\sigma_{R} = f(p) \cdot \sigma,
-%\end{equation}
-%where the $f(p)$ is a empirically determined scale factor from the Fig.~\ref{fig:GG_pdf} (right).
-With the definition, the integrated probability becomes 68.3$\%$ inside the $\sigma_R$ for all p values in the range of $1 \leq p \leq 2$.
-
-%for a given value of p in the range of. That is, the fitted result of the Fig.~\ref{fig:angle_10degree} ($\sigma$=
-
-%its performance of the angle measurement is tested with the test sample forq given angle.
-%tested its reconstruction performance with $10^6$ gamma samples for each fixed polar angle from $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
-%of the $\XGB$ by using $10^6$ gamma samples generated with uniform distribution in both of polar angle in range of 0 to 50 degrees and azimuthal angle of 0 to 360 degrees, we tested its reconstruction performance with $10^6$ gamma samples for each fixed polar angle from $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps.
-%Figure~\ref{fig:angle_reco_def} shows the distribution of reconstructed angles for incident gammas those have 1-GeV of energy and 10-degree of polar angle.
-The distribution has heavier tail compared with that of the Gaussian, and we tried to fit the distribution with the Generalized Gaussian distribution.
-The distribution
-
-%which agree well with the generated values.
-%The angles are properly reconstructed with a typical resolution as 1.2 degrees. There are no significant differences among the various incident angles. 
-%Typical angular resolution is obtained as 1.2 degrees and does not show significant dependency on incident angle.
+The variation of the GG function can be expressed as, then, $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
+The angular resolution of the incident angle reconstruction is defined as $\sigma$.
 
@@
 \includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
-\caption{\textcolor{red}{plots should be updated}
-Angular resolution for different incident angles (left) and shape parameter $\beta$ of reconstructed angluar distribution (right).}
-\label{fig:angle_reco_def}
-\end{figure}
-
-Since the angular resolution depends on the hyperparameters of the $\XGB$ which control the details of the training process, we scanned them with monitoring the angular resolution $\sigma$ defined at the Eq.
-7.
-There are five hyper parameters which can be optimized by user, and correlated among them.
-Figure~\ref{fig:par_scan} shows part of the scanning results, which enables us to determine the best parameters set to provide the best angular resolution.
-%their values are selected to provide the best angular resolution as described in
-The decided values of the parameters are given in Table~\ref{tab:XgbPar} with their function in the training process.
-%Among the parameters, the Max.
-depth rapidly improves the angular resolution with increasing its value until 15.
-The N\_estimators also improves the angular resolution with increasing its number, which is correlated to the value of the Max.
-depth.
-Its optimal condition becomes 1000 when the Max.
-depth is 15.
-({\it This part should be updated) - can we mention more detail?}
-
-\begin{figure}[!hbt]
-\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
-\caption{\textcolor{red}{plots should be updated}
-Angular resolution for different hyperparameter valuse.}
+\caption{\textcolor{red}{plots should be updated} The angular resolution for the varying AAA and the varying BBB. The best angular resolution is obtained with AAA=XXX and BBB=YYY.  }
 \label{fig:par_scan}
@@
 
-%performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees. ({\it This part should be updated)}
+As the reconstruction of the incident angle depends on hyperparameters of the $\XGB$, which controls the details of training processes, dedicated tests to optimize the hyperparameter were executed.
+It is assumed that a set of hyperperameters providing the best angular resolution would be optimized.
+The test scans the evaluated angular resolution with different hyperparameters.
+Figure~\ref{fig:par_scan} shows the result of the test for AAA and BBB.
+The AAA works for *******, and the BBB works for *****.
+The AAA and BBB are determined to be XXX and YYY, respectively.
+Different tests determine the set of hyperparameters, which is shown in Tab~\ref{tab:XgbPar}.
 
@@
 N\_estimators & The number of decision trees & N.A. & 1000 \\  
-Max. depth & Possible maximum depth of tree structure & 6 & 15 \\ 
+Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
 Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
@@
 \includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
-\caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
+\caption{ The angular resolution as a function of the scintillator strip width for 1~GeV $\gamma$ with $\theta=$~10~deg. The angular resolution is optimized with 15- to 20-mm-wide strips.}
 \label{fig:angle_reco_width}
@@
 
-For the study of the angle-reconstruction performance for different incident angles, we generated test samples of fixed value in range of 5 to 45 degrees with 5-degree steps.
-Each test sample contains $10^5$ $\gamma$'s and common parameter settings are used for calculating their incident angle, which showed similar performance for all samples.
-Figure~\ref{fig:angle_reco_def} shows the angular resolutions defined in Eq.
-7 for each incident angle (right) and shape-parameter $\beta$ (left).The performance of the angle reconstruction does not depend on the incident angle.
-
-%With the scintillator strips having a narrower width, we may get more precise information about the shower shape. 
-With an assumption that getting more precise information on the shower profile enables us to estimate with better resolution, we have studied the angle reconstruction by changing the width of the strips from 5 mm to 35 mm in 5 mm steps.
-As shown in Fig.~\ref{fig:angle_reco_width}, the best resolution is obtained when the width is 15mm.
-We can interpret that the larger-width configurations suffer the dilution of shower information and produce worth result.
-On the other hands, the narrower-width configuration does insufficient training due to limited statistics because of increased input features.
-This problem will be explained detailed later.
-
-%In order to figure out the optimal detector configuration providing the best angular resolution, we repeated the calculation by changing the width of the strips from 5 mm to 35 mm in 5 mm steps.
-Even though the narrower width is expected to provide more precise information about the shower shape, it does not mean to provide the better resolution as shown in Fig.~\ref{fig:angle_reco_width}.
-The angular resolution is not changed with increasing strip width up to 25 mm, which implies that the precise information on the shower shape is not essential to the angular resolution in a certain range because  of the stochastic nature of the shower generation.
-On the other hand, there is a possibility of insufficient training due to rapid increasing of the number of input according to the finer segmentation, while the number of events and hyper parameters for the training remain the same values optimized for the configuration of the 15-mm width.
-
-%because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects are not aligned in the incident direction.
-
-%The main reason seems to be a limitation of the number of training sample caused by lack of computer memory. 
-%As shown in Fig XXX, the obtained angular Aresolution for the 5-mm width is improved with increasing the number of training sample, while the other larger width is saturated already.
-%achine learning for increasing number of input data.
-XXXX.
-%Also, the angular resolution is not changed with increasing strip width up to 25 mm, which means the more precise information is not essential for the better angular resolution because the shower generation is a stochastic process and low energy photons produced by the Compton scattering and photoelectric effects are not aligned in the incident direction.
-
-%On the other hand, the finite size of the strip is related to the effect of incident gamma position.
-The previous results given in the Fig.~\ref{fig:angle_reco_width} are obtained from the data samples in which the incident gammas enter to a fixed position, the center of the strip.
-When we generated the gammas entering uniformly to the strip, we get the angular resolution as shown in Fig.
-xxx.
-Base on the results, we decide the width of the strip as xxx mm for a testing module to confirm the M.C.
-studies.
-%The performance of the detector is tested with different detector dimensions.
-Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000.
-Figure~\ref{fig:angle_reco_width} shows the angular resolution of the reconstruction as a function of the scintillator strip width with 5-mm-wide steps.
-It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths, and configurations with larger strip size than 15 mm do not provide improved resolution so that the width of the strip is determined to be 15 mm.
+The angular resolution was evaluated with the width of scintillator strips varying from 5 mm to 35 mm.
+Figure~\ref{fig:angle_reco_width} shows the angular resolution as a function of the width.
+15-mm-wide strips provide the best angular resolution.
+The width longer than 15 mm suffers from the dilution of the EM shower, resulting in worse resolution.
+On the other hand, the width shorter than 15 mm results in larger size of features, which causes a negative influence on the machine learning.
+Dedicated study is described in fig~\ref{fig:angle_reco_width}.
 
@@
 \includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
-\caption{ The angular resolution as a function of $\gamma$ energy (left), and the angular resolution for 1 GeV as a function of incident $\theta_{\rm{true}}$ (right). }
+\caption{ The angular resolution as a function of the $\gamma$ energy (left), and $p_{1}$ for 1 GeV as a function of the incident angle (right).
+$p_{1}$ is consistent down to $\theta=$~15~deg and changing at $\theta=$~10~deg, which is coming from the definition of $\theta$ }
 \label{fig:angle_reco_dep_gr}
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta_{\rm{true}}=$~10~degrees on the left panel.
-The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}(GeV)}$, where the $p_{0}$ denotes the contribution from energy-independent term and \textcolor{blue}{is estimated to be zero ($<$= is this true ?)}, and the $p_{1}$ denotes the contribution from energy-dependent term, mainly related with the development of the EM shower.
-The estimated $p_{1}$ for different $\theta_{\rm{true}}$ can be seen in the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
-They are deviating within $\pm$~0.05~deg range from the 1.25~deg.
+Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta=$~10~degrees on the left panel.
+The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}(GeV)}$, where the $p_{0}$ denotes the energy-independent contribution and is estimated to be 0.2, and the $p_{1}$ denotes the energy-dependent contribution, mainly related with the development of the EM shower.
+The estimated $p_{1}$ for different $\theta$ can be seen on the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
+They are deviating within $\pm$~0.05~deg range from the 1.1~deg.
 
@@
 \includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
-\caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
-The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\% with 10 MeV selection criteria.
-The large error bars less than 4.6 Xo is due to insufficient fitting because the reconstructed angular distributions deviated from the General Gaussian function.
-}
+\caption{ Reconstructed $\theta$ for 1 GeV $\gamma$ with $\theta=$~10~deg with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
+The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\% with 10~MeV selection.
+The large error bars less than 4.6$X_{0}$ is due to insufficient fitting because the reconstructed angular distributions deviated from the General Gaussian function.}
 \label{fig:angle_reco_layer}
@@
 
-Considering a measurement of incident angle only, we don't need the full-scaled detector to contain the generated shower completely.
-We can expect 99\% of $\gamma$ will start to generate shower inside detector within 5 radiation length (Xo).
-The left panel of Figure~\ref{fig:angle_reco_layer} shows reconstructed angle by using only the front 24 layers of the detector which corresponds to the length of 4.6 Xo for 1 GeV $\gamma$.
-The failed events located near the 0 are due to insufficient energy deposit ($<$ 10 MeV) to reconstruct the angle, of which ratio is estimated to be 5.8\%.
-As shown in the right panel of Figure~\ref{fig:angle_reco_layer}, the 4.6 Xo is needed to achieve equivalent resolution to that of the full-scaled detector.
-This results suggest that we can design a calorimeter producing complete information of incident $\gamma$ for itself by putting an fine segmented sampling calorimeter in front of the main calorimeter.
-
-The obtained angular resolution is determined by combined multiple sources, mainly the performance of learning process, number of layers for the measurement and the width of strips.
-Figure~\ref{fig:multi-parameter} shows the relation among the sources.
-For the larger width (25mm), the larger numbers of layers gives the better resolution (left).
-In order to achieve the best resolution for narrower width (5mm), we need much larger number of events for training the $\XGB$
+The reconstruction of the incident angle is tested with the front layer instead of the full layers considering the cost-effectiveness from the fact that 99\% of the $\gamma$ generates the EM shower in front of 5$X_{0}$.
+The left panel of Figure~\ref{fig:angle_reco_layer} shows reconstructed angle using the front 24 layers of the detector, which corresponds to the 4.6$X_{0}$ for 1~GeV $\gamma$.
+Some $\gamma$s are failed to be reconstructed due to the lack of the channel having the energy deposit.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV.
+The angular resolution with the front layer is estimated to be XXX while possessing inefficiency estimated to be 5.8\%.
 
 \begin{figure}[!hbt]
-\includegraphics[width=0.48\textwidth]{figures/layer-width.jpg}
-\includegraphics[width=0.48\textwidth]{figures/layer-event.jpg}
-\caption{ (Color online) left:Obtained angular resolution for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ as a function of number of layers used for reconstruction for 3 different strip widths when the number of trained sample is $2 \times 10^5$.
-right: Dependence on the number of training samples for using only the first 24 layers (open markers) and full-scaled one(closed markers).
+\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
+\caption{  \textcolor{red}{plots should be updated} The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers.
 }
@@
 
-%We can place a 5Xo-thick sampling calorimeter for angle measurement in front of a main calorimeter measuring energy of $\gamma$, and obtained angle information with resolution closed to the intrinsic value.
-
-%angular resolution depends on the radiation length used in the angle measurement and the dependence get disappeared with increasing radiation length.
-The reconstruction with 4.6$X_{0}$, which corresponds to 24 layers, provides 1.3 degree angular resolution.
-
-%We can reconstruct incident angle by using only the front-layer signals. % and check its performance.
-%with the same configuration. 
-%As signals in front layers are only used, $\gamma$s starting to interact at the rear layers can not be detected and their angles, therefore, can not be reconstructed.
-To reject such cases, total energy in the front layer is required to be larger than 1\% of incident $\gamma$ energy.
-Inefficiency due to the selection is estimated to be 5.8\%.
-
-%the angular resolution is improved larger than 24 layers which corresponds to the 4.6$X_{0}$.
-With the energy threshold of 10 MeV to the first 24 layers, 94$\%$ of incident gammas are reconstructed correctly, and the remained 6$\%$ do not generate enough shower particles.
-
-%reconstruction with the first 24 layers, which corresponds to the 4.6$X_{0}$, provides the identical resolution with one with the full geometry.
-The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region.
-The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%.
-Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right).
-The reconstructed $\theta$ distribution without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of failures of the $\theta$ reconstruction, and this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold.
-The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold, and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
-
-%The angle reconstruction is tested only with signals in front layers.
-Usages of front-layer signals are applied to the data sample for training and test procedures at the same time.
-The reconstruction with 24 layers, which possess 4.6$X_{0}$, provides the identical resolution with one with the full geometry.
-The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region.
-The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%.
-Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right).
-The reconstructed $\theta$ distribution without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of failures of the $\theta$ reconstruction, and this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold.
-The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold, and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
-
-%\begin{figure}[!hbt]
-%\includegraphics[width=0.8\textwidth]{figures/Fig4_reco_ecut.pdf}
-%\caption{ (Color online) Reconstructed $\theta$ before (black) and after (red and green) applying the responses related with the energy measurement.
-The red (green) distribution is constructed with the training samples without (with) such effects and the test samples with such effects.
-Simulated effects are found to be not significant.}
-%\label{fig:angle_reco_ecut}
-%\end{figure}
-
-%- Threshold effect
-
-%\subsection{Expected performance}
-
-%- W-Fiber
-
-%- Attenuation effect (NIM A715, pp48-55 (2013))
-
-%- Light Yield (40/1mm $\rightarrow$ 200/MeV (UCV) other reference ?)
-
-%The detector responses on the energy deposit are studied.
-The attenuation effect, smearing effect due to the photon statistics, and energy threshold for each channel are considered.
-The attenuation effect is applied to the deposit energy in each channel with the attenuation function, described in~\cite{Murayama:2020mcp}.
-The coefficients for the attenuation effect are assumed to be same with~\cite{Murayama:2020mcp}.
-The energy deposit after the attenuation effect is smeared with respect to the number of photon statistics.
-The number of photons ($\rm{n.p.e}$) is assumed to be 50 for 1 MeV.
-The standard deviation ($\sigma(E)$) for the smearing can be defined as
-
-%\begin{eqnarray}
-%\sigma(E) = \sqrt{E/\rm{n.p.e}}
-%\end{eqnarray}
-%After the smearing attenuated energy deposit, the energy threshold (0.5 MeV) is applied to the all channels.
-These effects are applied to the test samples and the training samples, and the training is done with and without applying such effects and the test is done with applying the effects.
-Figure~\ref{fig:angle_reco_ecut} shows that the angular resolution is found to be not significant against such effects.
-
-%\begin{figure}[!hbt]
-%\includegraphics[width=0.6\textwidth]{figures/Fig5_reco_hist.pdf}
-%\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ and true %$\gamma$ energy.
-The incident $\theta_{\rm{true}}$ is illustrated with different colors, which are explained in fig.\ref{fig:angle_reco_def}, and the $\gamma$ energy is illustrated with different lines.}
-%\label{fig:angle_reco_dep}
-%\end{figure}
-
-%The $\theta$ reconstruction dependencies on the incident angle and the incident energy are studied.
-Figure~\ref{fig:angle_reco_dep} shows the reconstructed $\theta$ with respect to the incident angle and the incident energy with different line colors and styles.
-The incident angle dependence of the reconstruction is found to be not significant for higher $E_{\gamma}>$~500~MeV and appears at lower $E_{\gamma}=$~200~MeV.
-The dependence on the incident energy can be clearly seen for all $\theta_{\rm{true}}$.
-The reconstruction for $\theta_{\rm{true}}=$~5~deg with lower $E_{\gamma}<$~200~MeV has a shifted maximum point due to their large standard deviations.
+Figure~\ref{fig:multi-parameter} shows the angular resolution with different numbers of training samples for different detector configurations.
+All configurations show a decrease in the angular resolution with increasing training samples, which means that enhanced statistics for the training results in better reconstruction.
+The angular resolution with 5-mm-wide scintillator strips is more rapidly decreasing than others.
+The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features.
+Considering limited computing resources, The setup with 2$\times10^{5}$ events, 24 layers, and the 15-mm-wide strip is chosen for the training of the $\XGB$, where the result is under 0.1 degree difference from the best setup.
 
@@
 \label{sec:sum}
-We studied a possibility to measure incident angle of the medium-energy $\gamma$ by using a finely segmented sampling calorimeter.
-With the configuration of alternation 1-mm thick lead sheets and 5-mm thick plastic scintillators, it will measure the energy for 1-GeV $\gamma$ with 4$\%$ of resolution which is mainly determined by the sampling fluctuation.
 
-For the angular measurement, we need to optimize detector configuration such as width of strips and number of layers.
-Also, the angular resolution is strongly depends on the goodness of the training of the $\XGB$ which depends on the number of training sample.
-For a case study of 15-mm strip width and 24 layers, we can achieve the angular resolution as 1.2 degrees with 94$\%$ efficiency.
-It depends on the incident energy of the $\gamma$, which will limit strictly on the applicable ranger of the measurement.
+We conduct a feasibility study to measure the incident angle of the $\gamma$ with the finely segmented sampling calorimeter.
+With alternating 1-mm-thick lead plates and 5-mm-thick plastic scintillator strips, the EM shower is largely generated in lead sheets, and is measured by scintillators.
+The incident angle the $\gamma$ is reconstructed with the $\XGB$ using the energy deposited in each scintillator strip.
 
-On the other hand, there are three major parameters to determine the performance of the measurement.
-With detailed studies on the optimization of the parameters, it would be possible to design the detector to satisfy the experimental requirement in various studies.
+We optimize the hyperparameter of the $\XGB$, and optimize the detector configuration using the optimized $\XGB$.
+We scan the hyperparameter in the 5-dimensional space and find the set providing the best angular resolution for different detector configurations.
+We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.2+1.1$/ \sqrt{E_\gamma}$ for different incident angles.
+We also find that using 24 front layers gives the angular resolution which is compatible with the angular resolution we get from the full layer.
 
-%Still there are many sources o
-
-%When we focus only on the angle measurement, the first 24 layers (4.6 Xo) provide a resolution as that of the full geometry (20 Xo) with 94$\%$ of detection efficiency.
-The angular resolution is not changed significantly increasing the width of the strips up to 25mm and expected to be 1.2 degrees for the 1 GeV gamma.
-
-%https://github.com/chenkkkk/MTR-TSF
+The angular resolution is changing with the variation of the training of the $\XGB$ and the detector configuration.
+As the strip width decreases, more channels of scintillator strips are required, and the training of the $\XGB$ gets affected due to the increased feature size.
+This is quenched with the larger number of training samples, which qualitatively improves the training of the $\XGB$.
+On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse.
+We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and 2$\times10^{5}$ training samples.
 

### 2022-01-24 paper.tex
updates

@@
 \includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
-\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter. It consists of alternating lead plates and scintillator strips.  }
+\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter.
+It consists of 105 alternating lead plates and scintillator strips.
+Each scintillator layer consists of 35 scintillator strips.
+The cross section of each 1-mm-thick lead plate is 525 mm $\times$ 525 mm.
+The cross section of each 5-mm-tihck scintillator strip is 525 mm $\times$ 15 mm.
+}
 \label{fig:det_conf}
@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
-\caption{\textcolor{red}{plots should be updated} The angular resolution for the varying AAA and the varying BBB. The best angular resolution is obtained with AAA=XXX and BBB=YYY.  }
+\includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
+\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators=300 and Max. depth=100.  }
 \label{fig:par_scan}
@@
 The test scans the evaluated angular resolution with different hyperparameters.
-Figure~\ref{fig:par_scan} shows the result of the test for AAA and BBB.
-The AAA works for *******, and the BBB works for *****.
-The AAA and BBB are determined to be XXX and YYY, respectively.
-Different tests determine the set of hyperparameters, which is shown in Tab~\ref{tab:XgbPar}.
+Figure~\ref{fig:par_scan} shows the result of the test for N\_estimators and Max.
+depth.
+N\_estimators defines allowed maximal number of decision trees, and the Max.
+depth defines complexity of the structure of decision trees.
+The N\_estimators and Max.
+depth are determined to be 300 and 100, respectively.
+Similar tests are applied to different hyperparameters, and definitive values for each hyperparameter are shown in Tab~\ref{tab:XgbPar}.
 
@@
 Parameter & Function & Default value & Used value \\ \hline 
-N\_estimators & The number of decision trees & N.A. & 1000 \\  
+N\_estimators & The number of decision trees & N.A. & 300 \\  
 Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
-Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
-Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
+Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
+Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
 Gamma & Requirement on minimum loss function & 0 & 0 \\ 

### 2022-01-24 paper.tex
updates

@@
 The sampling calorimeter was designed as alternating 1-mm-thick lead plates for passive converters and 5-mm-thick strips of the plastic scintillator for active counters.
+Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}.
 The cross section of the lead plate and the scintillator is 525 mm $\times$ 525 mm and 15 mm $\times$ 525 mm, respectively.
-Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}.
+The material for the scintillator strip is polyvinyltoluene.
 The total number of alternating layers is 105, which corresponds to 20$X_{0}$ to make it possible to absorb whole products from the EM shower ranging from 100 MeV to few GeV energy.
@@
 \includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
-\caption{  \textcolor{red}{plots should be updated} The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers.
-}
+\caption{ The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
 \label{fig:multi-parameter}

### 2022-01-25 paper.tex
updates

@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
-\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter.
+\includegraphics[width=0.6\textwidth]{figures/FullLayer_2.jpeg}
+\caption{ Schematic view of the sampling calorimeter.
 It consists of 105 alternating lead plates and scintillator strips.
@@
 \includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
-\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators=300 and Max. depth=100.  }
+\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
 \label{fig:par_scan}

### 2022-02-07 paper.tex
updates

@@
 \usepackage{cleveref}
+\usepackage{stackengine}
 \usepackage {xcolor}
@@
 \setcounter{page}{0}
-\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle }
+\title[]{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
 
@@
 \begin{abstract}
-We present studies on the detector configuration to measure the incident angle of the $\gamma$ with energies ranging from hundred MeV to few GeV using a new sampling calorimeter.
-The sampling calorimeter consists of alternating 1-mm-thick lead plates producing the electromagnetic (EM) shower and strips of 5-mm-thick plastic scintillators measuring the energy deposit by the shower particles.
-The strips are arranged along the alternating horizontal and vertical directions to measure the transverse profile by combining both directions at a given longitudinal position.
-In this paper, we used the GEANT4 to simulate energy deposit to the individual strips of the calorimeter, and the $\XGB$ to reconstruct the incident angle from energy deposits.
-
-The angular resolution weakly depends on the width of the strips up to 15 mm and becomes worse with the increasing width.
-It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length (5$X_{0}$) of the detector.
-The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.2+1.1$/ \sqrt{E_\gamma}$.
+We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
+A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
+The scintillator plates are alternatively segmented in horizontal and vertical strips.
+In this study, we obtained energy deposit in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees.
+Angular resolutions are studied in terms of the strip width.
+The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter.
+The angular resolution is almost constant for small angles less than 30$^{\circ}$, and varies significantly with the incident photon energy.
+The
+energy dependence can be expressed as $\sigma_{\theta}=$~xxx~$\oplus$~yyy~$/\sqrt{E_{\gamma}}$.
 
@@
 %\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
-%\keywords{String shoving, Collectivity, $pp$ collision}
+\keywords{Electromagnetic Calorimeter, Geant4, XGBoost, KOTO}
 \maketitle
@@
 \label{sec:mot}
-The EM calorimeter has played an important role in experimental studies for the nuclear and particle physics.
-Various materials have been developed for better energy and timing resolution so far~\cite{Calorimeter}.
-On the other side, the sampling calorimeter becomes popular in the large-scale high energy experiment mainly due to its cost-effectiveness.
-The sampling calorimeter consists of alternating passive converters that generate the EM shower and active counters that measure the energy deposit.
-Since the energy deposit in the passive convert is not measured, the fluctuation of energy deposits in the converter and the counter, called sampling fluctuation, determines the energy resolution of the calorimeter.
-The sampling fluctuation can be optimized by combining the converter and the counter with a specific portion.
-A 5-m-long cylindrical calorimeter made of alternating lead plates and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
+The electromagnetic (EM) calorimeter plays an important role in experimental studies for the nuclear and particle physics.
+Various materials have been developed for better energy and timing resolutions so far~\cite{Calorimeter}.
+EM calorimeters can be divided into two groups: sampling calorimeters and homogeneous calorimeter.
+Sampling calorimeters consist of alternating layers of an absorber generating EM showers and an active medium providing signals.
+On the other hand, homogeneous calorimeters are built of only a single type of material that facilitates both EM showers and signal generations.
+Today, the sampling calorimeter becomes very popular in large-scale high energy experiments, owing to its cost-effectiveness.
+In sampling calorimeters the energy deposited in the active medium fluctuates because the active layers are interleaved with absorber layers.
+This so-called sampling fluctuation dominates the energy resolution.
 
-The layer structure of the sampling calorimeter allow one to measure the individual profile of the shower along the beam direction, and the incident angle can be estimated by correlating energy deposits on neighboring layers.
-The measurement of the incident angle largely benefits the background rejection.
-Of particular, The incident angle will be an important tool for the KOTO experiment~\cite{KOTOproposal}.
+The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
+A 5-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
 
-Since the EM shower is evolving via stochastic processes, the incident angle would be reconstructed with a certain angular resolution.
-Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution.
-The evolution of the EM shower is generated with the GEANT4, and the $\XGB$ was used to reconstruct the incident angle.
+The segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction.
+The photon direction can also be deduced from the information on the EM shower shape.
+The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTOproposal}.
 
-In sec~\ref{sec:ems}, generic explanation of the EM shower and its evolution are described.
-We describe the reconstruction and angular resolution of the sampling calorimeter in sec~\ref{sec:res}.
-We summarize the study in sec~\ref{sec:sum}.
+Stochastic behaviors of the EM shower development limit to the angular resolution of the photon direction measurement.
+Energy deposits in each active layer of a sampling calorimeter fluctuate event by event so that the reconstruction of photon directions necessitates the longitudinal and lateral segmentation of the calorimeter.
 
-\section{ELECTROMAGNETIC SHOWER}
+This paper describes a machine learning approach based on XGBoost (XGB) model~\cite{xgboost:2016} with boosted decision trees in order to reconstruct the directions of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
+We generated EM showers in a sampling calorimeter using Geant4 simulations.
+We report on the detector configuration providing the acceptable angular resolution, and report on the angular resolution of the EM sampling calorimeter in terms of the incident angle and energy.
+
+\section{Electromagnetic Shower Simulation}
 \label{sec:ems}
@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.6\textwidth]{figures/FullLayer_2.jpeg}
-\caption{ Schematic view of the sampling calorimeter.
-It consists of 105 alternating lead plates and scintillator strips.
-Each scintillator layer consists of 35 scintillator strips.
-The cross section of each 1-mm-thick lead plate is 525 mm $\times$ 525 mm.
-The cross section of each 5-mm-tihck scintillator strip is 525 mm $\times$ 15 mm.
+\includegraphics[width=0.6\textwidth]{figures/FullLayer_3.jpeg}
+\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb plate and a segmented scintillator plate in 35 strips.
+Each scintillator plate is oriented alternatively in horizontal and vertical directions.
+See text for details.
 }
@@
 
-The sampling calorimeter was designed as alternating 1-mm-thick lead plates for passive converters and 5-mm-thick strips of the plastic scintillator for active counters.
-Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}.
-The cross section of the lead plate and the scintillator is 525 mm $\times$ 525 mm and 15 mm $\times$ 525 mm, respectively.
-The material for the scintillator strip is polyvinyltoluene.
-The total number of alternating layers is 105, which corresponds to 20$X_{0}$ to make it possible to absorb whole products from the EM shower ranging from 100 MeV to few GeV energy.
+Simulation models of a sampling calorimeter were constructed as a block consisting of alternating layers of a 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The plastic scintillator is segmented in 15-mm-wide strips, which is alternatively oriented in vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
+The sampling calorimeter model has a cross-section of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length (20$X_{0}$), which is sufficiently long to absorb full photon energy in the range of 100~MeV to 2~GeV.
 
@@
 \includegraphics[width=0.48\textwidth]{figures/SingleEventYZHit.pdf}
-\caption{ An event display of the energy deposit to each scintillator strip in the $x$--$z$ plane (left) and the $y$--$z$ plane (right) for the 1~GeV $\gamma$ perpendicularly entering to the detector ($\theta=$~0).}
+\caption{ Event display of simulated energy deposit patterns for a 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
 \label{fig:Evt_Dis}
@@
 
-The interaction of incident $\gamma$ with the detector was simulated using the GEANT4 (ver.
+The detector response to incident photons was simulated using Geant4 (ver.
 4.10.06) with the standard EM sub-packages~\cite{GEANT4}.
-The surface of the detector is defined as $z=$~0, and the $\gamma$ starts to interact with the detector.
-the incident angle of the $\gamma$ is defined as the polar angle ($\theta$) along the $z$ direction, where $\theta = 0$ case denotes that the $\gamma$ perpendicularly enters into the detector surface.
-Figure~\ref{fig:Evt_Dis} shows the event display illustrating the energy deposit on the each scintillator strip in both of $x$--$z$ and $y$--$z$ planes for the 1~GeV~$\gamma$ with $\theta = 0$.
+The beam direction defines the $z$-axis.
+The photon direction is defined as polar angle ($\theta$) with respect to the $z$-axis.
+Figure~\ref{fig:Evt_Dis} illustrates simulated energy deposit patterns in each strip for a 1-GeV photon at a normal incidence in $xz$- and $yz$-planes.
+Each segmented region in Fig.~\ref{fig:Evt_Dis} represents each channel.
 
-%\begin{figure}[!hbt]
-%\includegraphics[width=0.48\textwidth]{figures/LayerVisibleRatio.jpg}
-%\includegraphics[width=0.48\textwidth]{figures/Moliere_layer.jpg}
-%\caption{  \textcolor{red}{plots should be updated} Sampling fraction (left) and Moliere radius (right) from 1 GeV %$\gamma$ events ($\theta=0$) for each layer}
-%\label{fig:sc_prop}
-%\end{figure}
-
-%Figure~\ref{fig:sc_prop} shows the sampling fraction and the Moliere radius~\cite{PDG} for each layer with 1~GeV $\gamma$.
-In this paper, Moliere radius is defined as the distance including 90\% of (deposited) energy from the center of energy.
-The visible ratio (Moliere radius) decreases (increases) with increasing layer ID.
-It is, therefore, estimated to have better energy resolution and position separation with front layers.
-Note that the very front few layers are largely affected by secondaries going backward.
-
-\section{ANGLE RECONSTRUCTION}
+\section{Reconstruction of Incidence Angles}
 \label{sec:res}
 
-The incident angle of the $\gamma$ is reconstructed with the $\XGB$, which is one of the popular machine learning toolkit providing a scalable tree boosting system~\cite{xgboost:2016}.
-The machine learning is required to be trained.
-The feature, characteristic of a phenomenon, and the target, output to be predicted, are essential inputs for the training.
-The machine learning correlates each feature with the corresponding target for different features.
-Trained machine learning takes measured features and gives the target based on correlations which are made during the training.
-In this paper, the feature corresponds to energy deposits on each scintillator strip and the target corresponds to the incident angle of the $\gamma$.
-
-If the feature for the training is biased, the prediction of the $\XGB$ would be correspondingly biased as the $\XGB$ reliably believes there are no biases in all features given by a user.
-To minimize this, the incident angle is uniformly generated in the range 0 to 50 degrees for incident polar angle ($\theta$) and 0 to 360 degrees for incident azimuthal angle ($\varphi$), which makes the $\XGB$ train all features we are interested in.
-The number of samples for the training is $2\times10^5$ considering computing resources.
-To test the reconstruction of the incident angle, the incident angle is generated with the fixed $\theta$.
+Incidence angles of photons are reconstructed using the XGB model that is a scalable machine learning system for tree boosting~\cite{xgboost:2016}.
+A machine learning model maps a set of data inputs, known as features, to target variables.
+In this study, the XGB model maps a dataset of energy deposits in each scintillator strip to an incidence angle of a photon.
+Training data were carefully prepared using Geant4 simulation such that the input datasets are representative of a detector response of real sampling calorimeters.
+To minimize
+data bias, the incidence angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes azimuthal angle.
+Such a wide angular coverage provides good training datasets for the XGB.
+The number of training samples is $10^{5}$ considering limited computing resources.
+To test the reconstruction of incidence angles, we generated photons at a fixed incidence angle $\theta$.
 Note that the incident energy is known.
@@
 \includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
-\caption{ Reconstructed $\theta$ distribution for $\theta=$~10~deg events.
-The distribution is fitted with the Gaussian function and the Generalized Gaussian function.
-The Generalized Gaussian function provides better description for both tails.}
+\caption{ Reconstructed polar angle distribution for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+The distribution is fitted with the Gaussian and the Generalized Gaussian function.
+The later gives a better result.}
 \label{fig:angle_10degree}
@@
 
-Figure~\ref{fig:angle_10degree} shows reconstructed $\theta$ for 1~GeV $\gamma$ with $\theta=$~10~degrees.
+Figure~\ref{fig:angle_10degree} represents a distribution of reconstructed incidence angles $\theta$ for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
 The distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
-GG function provides better description for both tails of the distribution.
-The GG function can be expressed as
-\begin{equation} 
-f(x; \mu, \alpha, \beta) = \frac{\beta}{2 \alpha \Gamma(1/\beta)}e^{-(|x-\mu|/\alpha)^\beta}
-\end{equation}
-The variation of the GG function can be expressed as, then, $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
-The angular resolution of the incident angle reconstruction is defined as $\sigma$.
+We tested two functions, Gaussian and GG to describe the reconstructed angle distribution.
+The GG function, also known as the generalized error distribution, is expressed as
+\begin{eqnarray} 
+f(x; \mu, \alpha, \beta) = \frac{\beta}{2 \alpha \Gamma(1/\beta)}e^{-(|x-\mu|/\alpha)^\beta},
+\label{eqn:gg}
+\end{eqnarray}
+where $\mu$ denotes a mean value.
+Parameters $\alpha$ and $\beta$ determine the scale and shape of the distribution, respectively.
+Variance of the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
+The angular resolution of the incidence angle reconstruction is defined as $\sigma$.
 
@@
 \includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
-\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
+\caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
 \label{fig:par_scan}
@@
 
-As the reconstruction of the incident angle depends on hyperparameters of the $\XGB$, which controls the details of training processes, dedicated tests to optimize the hyperparameter were executed.
-It is assumed that a set of hyperperameters providing the best angular resolution would be optimized.
+We studied a correlation between byperparameters of the XGB model and the angular resolution.
 The test scans the evaluated angular resolution with different hyperparameters.
-Figure~\ref{fig:par_scan} shows the result of the test for N\_estimators and Max.
+Figure~\ref{fig:par_scan} shows the test results with N\_estimators and Max.
 depth.
-N\_estimators defines allowed maximal number of decision trees, and the Max.
-depth defines complexity of the structure of decision trees.
-The N\_estimators and Max.
-depth are determined to be 300 and 100, respectively.
-Similar tests are applied to different hyperparameters, and definitive values for each hyperparameter are shown in Tab~\ref{tab:XgbPar}.
+N\_estimators defines the maximum allowed number of decision trees to be developed, and the Max.
+depth defines the complexity of the structure of decision trees.
+The best hyperparameter combination was searched for in terms of the angular resolution.
+As a results, N\_estimators and Max.
+depth are set to 300 and 100, respectively.
+Similar tests were also performed for different hyperparameters.
+The best values for other hyperparameters are displayed in Tab~\ref{tab:XgbPar}.
+Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma.
+Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added current model.
+Lastly, Gamma regulates the evaluation of each decision tree.
 
@@
 \includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
-\caption{ The angular resolution as a function of the scintillator strip width for 1~GeV $\gamma$ with $\theta=$~10~deg. The angular resolution is optimized with 15- to 20-mm-wide strips.}
+\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
 \label{fig:angle_reco_width}
@@
 
-The angular resolution was evaluated with the width of scintillator strips varying from 5 mm to 35 mm.
-Figure~\ref{fig:angle_reco_width} shows the angular resolution as a function of the width.
-15-mm-wide strips provide the best angular resolution.
-The width longer than 15 mm suffers from the dilution of the EM shower, resulting in worse resolution.
-On the other hand, the width shorter than 15 mm results in larger size of features, which causes a negative influence on the machine learning.
-Dedicated study is described in fig~\ref{fig:angle_reco_width}.
+Angular resolutions were deduced with varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}.
+The 15-mm-wide strips yield the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+The shorter the strip width is, the larger size of features, which can influence negatively in machine learning.
+For longer strips, the EM shower information can hardly be obtained.
 
 \begin{figure}[!hbt]
+\centering
+\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
 \includegraphics[width=0.48\textwidth]{figures/Fig5_reco_graph.pdf}
+}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
 \includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
-\caption{ The angular resolution as a function of the $\gamma$ energy (left), and $p_{1}$ for 1 GeV as a function of the incident angle (right).
-$p_{1}$ is consistent down to $\theta=$~15~deg and changing at $\theta=$~10~deg, which is coming from the definition of $\theta$ }
+}
+\caption{ Deduced angular resolutions as functions of (a) photon energy for $\theta=$~10$^{\circ}$ and (b) polar angle for $E_{\gamma}=$~1~GeV. }
 \label{fig:angle_reco_dep_gr}
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} shows the angular resolution as a function of the incident $\gamma$ energy for $\theta=$~10~degrees on the left panel.
-The resolution is fitted with $p_{0} + p_{1}/\sqrt{E_{\gamma}(GeV)}$, where the $p_{0}$ denotes the energy-independent contribution and is estimated to be 0.2, and the $p_{1}$ denotes the energy-dependent contribution, mainly related with the development of the EM shower.
-The estimated $p_{1}$ for different $\theta$ can be seen on the right panel of fig.~\ref{fig:angle_reco_dep_gr}.
-They are deviating within $\pm$~0.05~deg range from the 1.1~deg.
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}=$) for $\theta=$~10$^{\circ}$.
+Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be xxx, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
+$p_{1}$ is estimated to be xxx for $\theta>$~15$^{\circ}$ and xxx$^{\circ}$~$\pm$~xxx$^{\circ}$ for $\theta=$~10$^{\circ}$ in Fig.~\ref{fig:angle_reco_dep_gr} (b).
+The discrepancy between them is attributed to the followings: polar angle to be always positive and poor angular resolutions for low $E_{\gamma}$ photons.
+When $\mu$ and $\alpha$ get comparable each other in Eq~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
+This largely affects the case $\mu=$~10$^{\circ}$ and not the case $\mu>$~15$^{\circ}$ considering that the angular resolutions for $E_{\gamma}=$~0.1~GeV is estimated to be 4$^{\circ}$.
 
 \begin{figure}[!hbt]
+\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
 \includegraphics[width=0.48\textwidth]{figures/res_Nlayer.jpg}
+}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
 \includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
-\caption{ Reconstructed $\theta$ for 1 GeV $\gamma$ with $\theta=$~10~deg with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right).
-The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\% with 10~MeV selection.
-The large error bars less than 4.6$X_{0}$ is due to insufficient fitting because the reconstructed angular distributions deviated from the General Gaussian function.}
+}
+\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$.
+Red histogram represents the polar angle distribution by requiring $E_{\rm{tot}}>$~10~MeV.
+(b) Angular resolution as a function of radiation length ($X_{0}$).}
 \label{fig:angle_reco_layer}
@@
 
-The reconstruction of the incident angle is tested with the front layer instead of the full layers considering the cost-effectiveness from the fact that 99\% of the $\gamma$ generates the EM shower in front of 5$X_{0}$.
-The left panel of Figure~\ref{fig:angle_reco_layer} shows reconstructed angle using the front 24 layers of the detector, which corresponds to the 4.6$X_{0}$ for 1~GeV $\gamma$.
-Some $\gamma$s are failed to be reconstructed due to the lack of the channel having the energy deposit.
+Furthermore, incidence angles are reconstructed with the front layers of $X_{0}$ in which 99\% of incident photons generate EM showers.
+Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which corresponds to 4.6$X_{0}$ for 1-GeV photons.
+A fraction of photons failed to be reconstructed due to the lack of active layers.
 The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV.
@@
 \includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
-\caption{ The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
+\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
 \label{fig:multi-parameter}
@@
 All configurations show a decrease in the angular resolution with increasing training samples, which means that enhanced statistics for the training results in better reconstruction.
-The angular resolution with 5-mm-wide scintillator strips is more rapidly decreasing than others.
+The angular resolution with 5-mm-wide scintillator strips decreases more rapidly than others.
 The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features.
-Considering limited computing resources, The setup with 2$\times10^{5}$ events, 24 layers, and the 15-mm-wide strip is chosen for the training of the $\XGB$, where the result is under 0.1 degree difference from the best setup.
+Considering limited computing resources, the setup with $10^{5}$ events, 24 layers, and the 15-mm-wide strip was chosen for training the $\XGB$ model.
+The training result differs by only 0.1$^{\circ}$ from the best setup will full layers.
 
@@
 
-We conduct a feasibility study to measure the incident angle of the $\gamma$ with the finely segmented sampling calorimeter.
-With alternating 1-mm-thick lead plates and 5-mm-thick plastic scintillator strips, the EM shower is largely generated in lead sheets, and is measured by scintillators.
-The incident angle the $\gamma$ is reconstructed with the $\XGB$ using the energy deposited in each scintillator strip.
+We report simulation results on the incidece angle reconstruction of EM sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
+EM shwers are simulated in the new samplinng calorimeter.using Geant4.
+We utilize the $\XGB$ model to reconstruct the photon incident angle by correlating all energy deposits in each strip with the incidence angle all events together.
 
-We optimize the hyperparameter of the $\XGB$, and optimize the detector configuration using the optimized $\XGB$.
-We scan the hyperparameter in the 5-dimensional space and find the set providing the best angular resolution for different detector configurations.
-We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.2+1.1$/ \sqrt{E_\gamma}$ for different incident angles.
-We also find that using 24 front layers gives the angular resolution which is compatible with the angular resolution we get from the full layer.
+We tune the hyperparameter of the $\XGB$ to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
+We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.2~$\oplus~$1.1$/\sqrt{E_\gamma}$ for different incident angles.
+We also conclude that using 24 front layers gives the angular resolution which is comparable with the angular resolution we get from the full layer.
 
-The angular resolution is changing with the variation of the training of the $\XGB$ and the detector configuration.
+We study that the angular resolution is changing with the variation of the training of the $\XGB$ and the detector configuration.
 As the strip width decreases, more channels of scintillator strips are required, and the training of the $\XGB$ gets affected due to the increased feature size.
@@
 On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse.
-We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and 2$\times10^{5}$ training samples.
+We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and $10^{5}$ training samples.
 

### 2022-02-07 paper.tex
updates

@@
 The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
-A 5-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.
+A 3-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{Murayama:2020mcp}.
 
@@
 The photon direction can also be deduced from the information on the EM shower shape.
-The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTOproposal}.
+The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTO:2012}.
 

### 2022-02-19 paper.tex
update

@@
-\documentclass[jkps,preprint,fleqn,showpacs,showkeys]{revtex4}
+\documentclass[preprint,12pt,times,a4paper]{elsarticle}
 
@@
 \usepackage{amsmath}
-\usepackage{bm}
 \usepackage{lineno}
 \usepackage{xspace}
+\usepackage{lipsum}
 \usepackage{cleveref}
 \usepackage{stackengine}
+\usepackage{titlesec}
 \usepackage {xcolor}
+\usepackage[bitstream-charter]{mathdesign}
+\usepackage[T1]{fontenc}
+\usepackage{geometry, float}
+\geometry{a4paper}
+
+\usepackage[normalem]{ulem}
+\usepackage{stackengine}
+
+\journal{Nuclear Instruments and Methods in Physics Research A}
 
@@
 \begin{document}
+
+\begin{frontmatter}
+
 \setcounter{page}{0}
-\title[]{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
+\title{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
 
-\author{YoungJun \surname{Kim}}
-\author{Jung Keun \surname{Ahn}}
-\affiliation{Department of Physics, Korea University, Seoul 02841}
-\author{Junlee \surname{Kim}}
-\email{junlee.kim@cern.ch}
-\author{Eun-Joo \surname{Kim}}
-\email{ejkim@jbnu.ac.kr}
-\affiliation{Department of Physics education, Jeonbuk National University, Jeonju 54896}
-\author{GeiYoub  \surname{Lim}}
-\affiliation{IPNS/KEK Tsukuba, Japan 305-0801}
+\author[jbnu]{Junlee~Kim\corref{cor1}}
+\ead{junlee.kim@cern.ch}
+\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}
+\author[jbnu]{Eun-Joo~Kim\corref{cor2}}
+\ead{ejkim@jbnu.ac.kr}
+
+\author[korea]{Young~Jun~Kim}
+\author[korea]{Jung~Keun~Ahn}
+
+\cortext[cor2]{Corresponding author. Tel.: +82-xxxxxxxxx.}
+\author[kek]{Gei~Youb~Lim}
+
+\address[jbnu]{Division of Science Education, Jeonbuk National University, Jeonju 54896, Korea}
+\address[korea]{Department of Physics, Korea University, Seoul 02841, Korea}
+\address[kek]{Institute of Particle and Nuclear Studies (IPNS), High Energy Accelerator Research Organization (KEK), Tsukuba 305-0801, Japan}
 
@@
 \end{abstract}
+\begin{keyword}
+% keywords here, in the form: keyword \sep keyword
+Electromagnetic Calorimeter \sep Geant4 \sep XGBoost \sep KOTO
+\end{keyword}
 
-%\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
-\keywords{Electromagnetic Calorimeter, Geant4, XGBoost, KOTO}
-\maketitle
+\end{frontmatter}
 
@@
 
-\begin{acknowledgments}
-\end{acknowledgments}
+\section*{Acknowledgement}
+This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and 2020R1A3B2079993).
 

### 2022-02-19 paper.tex
updates

@@
 
-\author[jbnu]{Junlee~Kim\corref{cor1}}
+\author[jbnu]{Junlee~Kim}
 \ead{junlee.kim@cern.ch}
-\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}
-\author[jbnu]{Eun-Joo~Kim\corref{cor2}}
+%\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}
+
+\author[jbnu]{Eun-Joo~Kim\corref{cor1}}
 \ead{ejkim@jbnu.ac.kr}
+\cortext[cor1]{Corresponding author. Tel.: +82-10-4581-5649.}
 
@@
 \author[korea]{Jung~Keun~Ahn}
-
-\cortext[cor2]{Corresponding author. Tel.: +82-xxxxxxxxx.}
 \author[kek]{Gei~Youb~Lim}
@@
 The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter.
+Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter still possessing the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
 The angular resolution is almost constant for small angles less than 30$^{\circ}$, and varies significantly with the incident photon energy.
 The
-energy dependence can be expressed as $\sigma_{\theta}=$~xxx~$\oplus$~yyy~$/\sqrt{E_{\gamma}}$.
+energy dependence can be expressed as $\sigma_{\theta}=$~1.21~$\oplus$~0.45~$/\sqrt{E_{\gamma}}$.
 
@@
 \begin{figure}[!hbt]
+\centering
 \includegraphics[width=0.6\textwidth]{figures/FullLayer_3.jpeg}
@@
 \begin{figure}[!hbt]
+\centering
 \includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
@@
 
-\begin{table}[hbt!]
+\begin{table}[hbt!]{\small
 \centering
@@
 \label{tab:XgbPar}
-\end{table}
+}\end{table}
 
 \begin{figure}[!hbt]
+\centering
 \includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
@@
 \begin{figure}[!hbt]
+\centering
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
@@
 \begin{figure}[!hbt]
+\centering
 \includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}

### 2022-02-21 paper.tex
updates

@@
 \usepackage{titlesec}
-\usepackage {xcolor}
+\usepackage{xcolor}
 \usepackage[bitstream-charter]{mathdesign}
@@
 \usepackage{geometry, float}
+\usepackage{biblatex}
+\addbibresource{paper.bib}
+
 \geometry{a4paper}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/FullLayer_3.jpeg}
+\includegraphics[width=0.6\textwidth]{figures/Fig1_detector_schematic.jpeg}
 \caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb plate and a segmented scintillator plate in 35 strips.
@@
 \begin{figure}[!hbt]
-%\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
-%\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
-\includegraphics[width=0.48\textwidth]{figures/SingleEventXZHit.pdf}
-\includegraphics[width=0.48\textwidth]{figures/SingleEventYZHit.pdf}
+\centering
+\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_XZ.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_YZ.pdf}
 \caption{ Event display of simulated energy deposit patterns for a 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
+\includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
 \caption{ Reconstructed polar angle distribution for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
+\includegraphics[width=0.89\textwidth]{figures/Fig4_Opt.pdf}
 \caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
@@
 Similar tests were also performed for different hyperparameters.
-The best values for other hyperparameters are displayed in Tab~\ref{tab:XgbPar}.
+The best values for other hyperparameters are displayed in Tab.~\ref{tab:XgbPar}.
 Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma.
@@
 \centering
-\includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
+\includegraphics[width=0.58\textwidth]{figures/Fig5_width.pdf}
 \caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_graph.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig6_layer_comp.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig5_reco_inc.pdf}
-}
-\caption{ Deduced angular resolutions as functions of (a) photon energy for $\theta=$~10$^{\circ}$ and (b) polar angle for $E_{\gamma}=$~1~GeV. }
-\label{fig:angle_reco_dep_gr}
-\end{figure}
-
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}=$) for $\theta=$~10$^{\circ}$.
-Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be xxx, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
-$p_{1}$ is estimated to be xxx for $\theta>$~15$^{\circ}$ and xxx$^{\circ}$~$\pm$~xxx$^{\circ}$ for $\theta=$~10$^{\circ}$ in Fig.~\ref{fig:angle_reco_dep_gr} (b).
-The discrepancy between them is attributed to the followings: polar angle to be always positive and poor angular resolutions for low $E_{\gamma}$ photons.
-When $\mu$ and $\alpha$ get comparable each other in Eq~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
-This largely affects the case $\mu=$~10$^{\circ}$ and not the case $\mu>$~15$^{\circ}$ considering that the angular resolutions for $E_{\gamma}=$~0.1~GeV is estimated to be 4$^{\circ}$.
-
-\begin{figure}[!hbt]
-\centering
-\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{figures/res_Nlayer.jpg}
-}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
+\includegraphics[width=0.48\textwidth]{figures/Fig6_nlayer.pdf}
 }
@@
 The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV.
-The angular resolution with the front layer is estimated to be XXX while possessing inefficiency estimated to be 5.8\%.
+The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
+\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
+\includegraphics[width=0.48\textwidth]{figures/Fig7_Fit_eres.pdf}
+}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
+\includegraphics[width=0.48\textwidth]{figures/Fig7_eres.pdf}
+}
+\caption{ Deduced angular resolutions as functions of (a) photon energy for $\theta=$~10$^{\circ}$ and (b) polar angle for $E_{\gamma}=$~1~GeV. }
+\label{fig:angle_reco_dep_gr}
+\end{figure}
+
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}=$) for $\theta=$~10$^{\circ}$.
+Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.45$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
+$p_{1}$ is estimated to be xxx$^{\circ}$ for $\theta>$~yyy$^{\circ}$ and xxx$^{\circ}$ for $\theta=$~yyy$^{\circ}$ in Fig.~\ref{fig:angle_reco_dep_gr} (b).
+The discrepancy between them is attributed to the followings: polar angle to be always positive and poor angular resolutions for low $E_{\gamma}$ photons.
+When $\mu$ and $\alpha$ get comparable each other in Eq~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
+This largely affects the case $\mu=$~10$^{\circ}$ and not the case $\mu>$~15$^{\circ}$ considering that the angular resolutions for $E_{\gamma}=$~0.1~GeV is estimated to be 4$^{\circ}$.
+
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.6\textwidth]{figures/Fig8_nsample.pdf}
 \caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
@@
 We tune the hyperparameter of the $\XGB$ to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
-We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.2~$\oplus~$1.1$/\sqrt{E_\gamma}$ for different incident angles.
+We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.45~$\oplus~$1.21$/\sqrt{E_\gamma}$ for different incident angles.
 We also conclude that using 24 front layers gives the angular resolution which is comparable with the angular resolution we get from the full layer.
@@
 \section*{Acknowledgement}
-This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and 2020R1A3B2079993).
+This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and \\ 2020R1A3B2079993).
 
-\bibliography{paper}
+\printbibliography
 

### 2022-02-23 paper.tex
updates

@@
 The scintillator plates are alternatively segmented in horizontal and vertical strips.
-In this study, we obtained energy deposit in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees.
+In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees.
 Angular resolutions are studied in terms of the strip width.
 The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter still possessing the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
-The angular resolution is almost constant for small angles less than 30$^{\circ}$, and varies significantly with the incident photon energy.
-The
-energy dependence can be expressed as $\sigma_{\theta}=$~1.21~$\oplus$~0.45~$/\sqrt{E_{\gamma}}$.
+Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter with the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
+The angular resolution is mildly dependent on the incidence angle, and varies significantly with the incident photon energy.
+The energy dependence can be expressed as $\sigma_{\theta}=$~0.43~$\oplus p1 /\sqrt{E_{\gamma}}$, where $p1$ gradually decreases with the incidence angle.
 
@@
 \label{sec:mot}
-The electromagnetic (EM) calorimeter plays an important role in experimental studies for the nuclear and particle physics.
+Electromagnetic (EM) calorimeter plays an important role in experimental studies for the nuclear and particle physics.
 Various materials have been developed for better energy and timing resolutions so far~\cite{Calorimeter}.
-EM calorimeters can be divided into two groups: sampling calorimeters and homogeneous calorimeter.
+EM calorimeters can be divided into two groups: sampling calorimeters and homogeneous calorimeters.
 Sampling calorimeters consist of alternating layers of an absorber generating EM showers and an active medium providing signals.
@@
 The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
-A 3-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{Murayama:2020mcp}.
+A 3-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillator plates is an example of the sampling calorimeter~\cite{Murayama:2020mcp}.
 
@@
 
-This paper describes a machine learning approach based on XGBoost (XGB) model~\cite{xgboost:2016} with boosted decision trees in order to reconstruct the directions of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
+This paper describes a machine learning approach based on XGBoost (XGB) model~\cite{xgboost:2016} with boosted decision trees in order to reconstruct the direction of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
 We generated EM showers in a sampling calorimeter using Geant4 simulations.
@@
 Simulation models of a sampling calorimeter were constructed as a block consisting of alternating layers of a 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
-The plastic scintillator is segmented in 15-mm-wide strips, which is alternatively oriented in vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
+The plastic scintillator is segmented in 15-mm-wide strips, which are alternatively oriented in vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
 The sampling calorimeter model has a cross-section of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length (20$X_{0}$), which is sufficiently long to absorb full photon energy in the range of 100~MeV to 2~GeV.
@@
 
-Incidence angles of photons are reconstructed using the XGB model that is a scalable machine learning system for tree boosting~\cite{xgboost:2016}.
+Incidence angles of photons are reconstructed using the XGB model that is a scalable machine learning system for the gradient boosting tree~\cite{xgboost:2016}.
 A machine learning model maps a set of data inputs, known as features, to target variables.
@@
 To test the reconstruction of incidence angles, we generated photons at a fixed incidence angle $\theta$.
-Note that the incident energy is known.
+Note that the incidence energy is known.
 
@@
 Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma.
-Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added current model.
+Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added onto the current model.
 Lastly, Gamma regulates the evaluation of each decision tree.
@@
 \centering
-\caption{Hyperparameters of the $\XGB$}
+\caption{Hyperparameters of the XGB model}
 \begin{tabular}{cccc}
@@
 Furthermore, incidence angles are reconstructed with the front layers of $X_{0}$ in which 99\% of incident photons generate EM showers.
-Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which corresponds to 4.6$X_{0}$ for 1-GeV photons.
+Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons.
 A fraction of photons failed to be reconstructed due to the lack of active layers.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of incidence energy.
 The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}=$) for $\theta=$~10$^{\circ}$.
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~10$^{\circ}$.
 Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.45$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
@@
 The discrepancy between them is attributed to the followings: polar angle to be always positive and poor angular resolutions for low $E_{\gamma}$ photons.
-When $\mu$ and $\alpha$ get comparable each other in Eq~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
+When $\mu$ and $\alpha$ get comparable each other in Eq.~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
 This largely affects the case $\mu=$~10$^{\circ}$ and not the case $\mu>$~15$^{\circ}$ considering that the angular resolutions for $E_{\gamma}=$~0.1~GeV is estimated to be 4$^{\circ}$.
@@
 The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features.
-Considering limited computing resources, the setup with $10^{5}$ events, 24 layers, and the 15-mm-wide strip was chosen for training the $\XGB$ model.
-The training result differs by only 0.1$^{\circ}$ from the best setup will full layers.
+Considering limited computing resources, the setup with $10^{5}$ events, 24 layers, and the 15-mm-wide strip was chosen for training the XGB model.
+The training result differs by only 0.2$^{\circ}$ from the best setup will full layers.
 
@@
 EM shwers are simulated in the new samplinng calorimeter.using Geant4.
-We utilize the $\XGB$ model to reconstruct the photon incident angle by correlating all energy deposits in each strip with the incidence angle all events together.
+We utilize the XGB model to reconstruct the photon incident angle by correlating all energy deposits in each strip with the incidence angle all events together.
 
-We tune the hyperparameter of the $\XGB$ to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
-We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.45~$\oplus~$1.21$/\sqrt{E_\gamma}$ for different incident angles.
+We tune the hyperparameter of the XGB to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
+We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.45~$\oplus~$xxx$/\sqrt{E_\gamma}$ for different incidence angles.
 We also conclude that using 24 front layers gives the angular resolution which is comparable with the angular resolution we get from the full layer.
 
-We study that the angular resolution is changing with the variation of the training of the $\XGB$ and the detector configuration.
-As the strip width decreases, more channels of scintillator strips are required, and the training of the $\XGB$ gets affected due to the increased feature size.
-This is quenched with the larger number of training samples, which qualitatively improves the training of the $\XGB$.
+Furthermore, we study that the angular resolution is changing with the variation of the training of the XGB and the detector configuration.
+As the strip width decreases, more channels of scintillator strips are required, and the training of the XGB gets affected due to the increased feature size.
+This is quenched with the larger number of training samples, which qualitatively improves the training of the XGB.
 On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse.

### 2022-04-04 paper.tex
updates

@@
 The angular resolution is mildly dependent on the incidence angle, and varies significantly with the incident photon energy.
-The energy dependence can be expressed as $\sigma_{\theta}=$~0.43~$\oplus p1 /\sqrt{E_{\gamma}}$, where $p1$ gradually decreases with the incidence angle.
+The energy dependence can be expressed as $\sigma_{\theta}=$~0.43~$\oplus p_{1} /\sqrt{E_{\gamma}}$, where $p_{1}$ gradually decreases with the incidence angle.
 
@@
 To test the reconstruction of incidence angles, we generated photons at a fixed incidence angle $\theta$.
-Note that the incidence energy is known.
+Note that the incident energy is known.
 
@@
 We tested two functions, Gaussian and GG to describe the reconstructed angle distribution.
+Two functions were multiplied by $\sin{x}$ to correct solid angle acceptance.
 The GG function, also known as the generalized error distribution, is expressed as
@@
 A fraction of photons failed to be reconstructed due to the lack of active layers.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of incidence energy.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of incident energy.
 The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.
@@
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig7_eres.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig7_eres_40deg.pdf}
 }
@@
 Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~10$^{\circ}$.
-Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.45$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
-$p_{1}$ is estimated to be xxx$^{\circ}$ for $\theta>$~yyy$^{\circ}$ and xxx$^{\circ}$ for $\theta=$~yyy$^{\circ}$ in Fig.~\ref{fig:angle_reco_dep_gr} (b).
-The discrepancy between them is attributed to the followings: polar angle to be always positive and poor angular resolutions for low $E_{\gamma}$ photons.
-When $\mu$ and $\alpha$ get comparable each other in Eq.~\ref{eqn:gg}, the left tail of the distribution would extend to negative area.
-This largely affects the case $\mu=$~10$^{\circ}$ and not the case $\mu>$~15$^{\circ}$ considering that the angular resolutions for $E_{\gamma}=$~0.1~GeV is estimated to be 4$^{\circ}$.
+Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.43~$\pm$~0.01$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
+$p_{1}$ is estimated to be gradually decreasing from 1.28$^{\circ}$ to 1.04$^{\circ}$ with increasing incidence angles as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
 
@@
 We tune the hyperparameter of the XGB to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
-We find that 15-mm-wide strips provide the best angular resolution, which can be expressed as 0.45~$\oplus~$xxx$/\sqrt{E_\gamma}$ for different incidence angles.
-We also conclude that using 24 front layers gives the angular resolution which is comparable with the angular resolution we get from the full layer.
+We find that 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+We also conclude that using 24 front layers gives the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer.
+We evaluate angular resolutions in terms of the incidence angle and the incident energy.
+The angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$.
+$p_{0}$ is estimated to be 0.43$^{\circ}$ and not dependent on the incidence angle.
+$p_{1}$ is estimated to be 1.28--1.04$^{\circ}$ and gradually decreasing with the incidence angle.
 

### 2022-05-30 paper.tex
updates

@@
 The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter with the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
+Incident photon directions can be well reconstructed in the front part (4.6$X_{0}$) of the EM calorimeter with the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
 The angular resolution is mildly dependent on the incidence angle, and varies significantly with the incident photon energy.
@@
 We generated EM showers in a sampling calorimeter using Geant4 simulations.
-We report on the detector configuration providing the acceptable angular resolution, and report on the angular resolution of the EM sampling calorimeter in terms of the incident angle and energy.
+We report on the detector configuration providing the acceptable angular resolution, and report on the angular resolution of the EM sampling calorimeter in terms of the incidence angle and the incident energy.
 
@@
 Training data were carefully prepared using Geant4 simulation such that the input datasets are representative of a detector response of real sampling calorimeters.
-To minimize
-data bias, the incidence angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes azimuthal angle.
+To minimize data bias, the incidence angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes azimuthal angle.
 Such a wide angular coverage provides good training datasets for the XGB.
@@
 
-Figure~\ref{fig:angle_10degree} represents a distribution of reconstructed incidence angles $\theta$ for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-The distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
+Figure~\ref{fig:angle_10degree} represents a distribution of the relative incidence angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+$\Delta\theta$ denotes how much distant the reconstructed incidence direction is from the true incidence direction radially.
+The central 98\% part of the distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
 We tested two functions, Gaussian and GG to describe the reconstructed angle distribution.
-Two functions were multiplied by $\sin{x}$ to correct solid angle acceptance.
 The GG function, also known as the generalized error distribution, is expressed as
@@
 
-Furthermore, incidence angles are reconstructed with the front layers of $X_{0}$ in which 99\% of incident photons generate EM showers.
+Furthermore, incidence angles are reconstructed with the front layers of $4.6X_{0}$ in which 99\% of incident photons generate EM showers.
 Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons.
 A fraction of photons failed to be reconstructed due to the lack of active layers.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of incident energy.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy.
 The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.

### 2022-05-31 paper.tex
updates

@@
 Lastly, Gamma regulates the evaluation of each decision tree.
-
+It is also worth mentioning that the fraction of the tail is not changing from 2\%.
 \begin{table}[hbt!]{\small
@@
 Angular resolutions were deduced with varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}.
-The 15-mm-wide strips yield the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+The 15-mm-wide strips yield good angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
 The shorter the strip width is, the larger size of features, which can influence negatively in machine learning.
@@
 
-Furthermore, incidence angles are reconstructed with the front layers of $4.6X_{0}$ in which 99\% of incident photons generate EM showers.
+Furthermore, incidence angles are reconstructed with the front layers of $ 6.2X_{0}$ in which 99\% of incident photons generate EM showers.
 Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons.

### 2022-05-31 paper.tex
updates

@@
 
-Furthermore, incidence angles are reconstructed with the front layers of $ 6.2X_{0}$ in which 99\% of incident photons generate EM showers.
-Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons.
+Furthermore, incidence angles are reconstructed with the front layers of 6.2$X_{0}$ in which more than 99\% of incident photons generate EM showers.
+Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 32 layers of the detector, which correspond to 6.2$X_{0}$ for 1-GeV photons.
 A fraction of photons failed to be reconstructed due to the lack of active layers.
 The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy.
-The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.
+The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be xxx\%.
 

### 2022-05-31 paper.tex
updates

@@
 
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~10$^{\circ}$.
-Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.43~$\pm$~0.01$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower.
-$p_{1}$ is estimated to be gradually decreasing from 1.28$^{\circ}$ to 1.04$^{\circ}$ with increasing incidence angles as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~25$^{\circ}$.
+Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy-independent and energy-dependent contribution, respectively.
+$p_{0}$ and $p_{1}$ are constant for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
+For small $\theta$, The values are deviating up to $\pm$0.15$^{\circ}$  as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
 

### 2022-06-07 paper.tex
updates

@@
 \begin{abstract}
-We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
+We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 10~GeV.
 A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
@@
 Angular resolutions are studied in terms of the strip width.
-The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-Incident photon directions can be well reconstructed in the front part (4.6$X_{0}$) of the EM calorimeter with the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$.
+The 15-mm-wide strips provide acceptable angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+Incident photon directions can be well reconstructed in the front part (6.2$X_{0}$) of the EM calorimeter with the acceptable angular resolution of
+1.33~$\pm$~0.01$^{\circ}$.
+
 The angular resolution is mildly dependent on the incidence angle, and varies significantly with the incident photon energy.
@@
 The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy.
-The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be xxx\%.
+The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 1.9\%.
 
@@
 Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~25$^{\circ}$.
-Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy-independent and energy-dependent contribution, respectively.
+Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
 $p_{0}$ and $p_{1}$ are constant for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.

### 2022-06-07 paper.tex
updates

@@
 \begin{abstract}
-We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 10~GeV.
+We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
 A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
@@
 Incident photon directions can be well reconstructed in the front part (6.2$X_{0}$) of the EM calorimeter with the acceptable angular resolution of
-1.33~$\pm$~0.01$^{\circ}$.
-
-The angular resolution is mildly dependent on the incidence angle, and varies significantly with the incident photon energy.
-The energy dependence can be expressed as $\sigma_{\theta}=$~0.43~$\oplus p_{1} /\sqrt{E_{\gamma}}$, where $p_{1}$ gradually decreases with the incidence angle.
+1.30~$\pm$~0.01$^{\circ}$.
+The angular resolution varies significantly with the incident photon energy, and weakly dependent on the incidence angle.
+The energy dependence can be expressed as $\sigma_{\theta}= p_{0} \oplus p_{1} /\sqrt{E_{\gamma}}$.
+For the small angle ($\theta<$~10 deg), the angular resolution is also dependent on the incidence angle, and the dependence disappears as the incident energy increases.
+For the $\theta>$~10 deg, $p_{0}$ and $p_{1}$ are estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
 
@@
 \includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
-\caption{ Reconstructed polar angle distribution for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+\caption{ The relative incidence angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
 The distribution is fitted with the Gaussian and the Generalized Gaussian function.
@@
 Figure~\ref{fig:angle_10degree} represents a distribution of the relative incidence angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-$\Delta\theta$ denotes how much distant the reconstructed incidence direction is from the true incidence direction radially.
+$\Delta\theta$ represents the radial displacement of the reconstructed incidence angle from the true incidence direction.
 The central 98\% part of the distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
@@
 \begin{figure}[!hbt]
-\includegraphics[width=0.89\textwidth]{figures/Fig4_Opt.pdf}
+\centering
+\includegraphics[width=0.69\textwidth]{figures/Fig4_Opt.pdf}
 \caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
@@
 Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
-$p_{0}$ and $p_{1}$ are constant for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
-For small $\theta$, The values are deviating up to $\pm$0.15$^{\circ}$  as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
+$p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
+For small $\theta$, The values are varying up to $\pm$~0.15$^{\circ}$ as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
 

### 2022-06-08 paper.tex
updates

@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
+\includegraphics[width=0.48\textwidth]{figures/Fig7_res_ene.pdf}
+}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
 \includegraphics[width=0.48\textwidth]{figures/Fig7_Fit_eres.pdf}
-}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig7_eres_40deg.pdf}
 }
-\caption{ Deduced angular resolutions as functions of (a) photon energy for $\theta=$~10$^{\circ}$ and (b) polar angle for $E_{\gamma}=$~1~GeV. }
+\caption{ Angular resolutions as functions of the incidence angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$ (b) }
 \label{fig:angle_reco_dep_gr}
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~25$^{\circ}$.
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incidence angle for different incident energies ($E_{\gamma}$).
+The angular resolution does not depend on the incidence angle for high incident energy.
+On the other hand, the angular resolution is especially changing for low incident energy at the small incidence angle.
+Figure~\ref{fig:angle_reco_dep_gr} (b) shows the angular resolution as a function of the incident photon energy at $\theta=$~25$^{\circ}$.
 Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
+
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.58\textwidth]{figures/Fig7_eres_40deg.pdf}
+\caption{ $p_{1}$ as a function of the incidence angle }
+\label{fig:res_edep}
+\end{figure}
+
+Figure~\ref{fig:res_edep} shows estimated $p_{1}$ as a function of the incidence angle.
 $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
-For small $\theta$, The values are varying up to $\pm$~0.15$^{\circ}$ as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
+For small $\theta$, $p_{1}$ is smaller than larger $\theta$ as the angular resolution is significantly dependent on the incidence angle for the low incident energy.
 

### 2022-06-11 paper.tex
updates

@@
 The energy dependence can be expressed as $\sigma_{\theta}= p_{0} \oplus p_{1} /\sqrt{E_{\gamma}}$.
-For the small angle ($\theta<$~10 deg), the angular resolution is also dependent on the incidence angle, and the dependence disappears as the incident energy increases.
+For low energy photons, the angular resolution is dependent on the incidence angle, and the dependence disappears as the incident energy increases.
 For the $\theta>$~10 deg, $p_{0}$ and $p_{1}$ are estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig7_res_ene.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig7_Fit_eres.pdf}
+\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres.pdf}
 }

### 2022-06-11 paper.tex
updates

@@
 $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
-For small $\theta$, $p_{1}$ is smaller than larger $\theta$ as the angular resolution is significantly dependent on the incidence angle for the low incident energy.
+For small $\theta$, $p_{1}$ is smaller than larger $\theta$ from the fact that the angular resolution is largely dependent on the incidence angle for the low incident energy.
 
@@
 The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features.
-Considering limited computing resources, the setup with $10^{5}$ events, 24 layers, and the 15-mm-wide strip was chosen for training the XGB model.
-The training result differs by only 0.2$^{\circ}$ from the best setup will full layers.
+Considering limited computing resources, the setup with $10^{5}$ events, 32 layers, and the 15-mm-wide strip was chosen for training the XGB model.
+The training result differs by only 0.$^{\circ}$ from the best setup will full layers.
 

### 2022-06-11 paper.tex
updates

@@
 \includegraphics[width=0.6\textwidth]{figures/Fig8_nsample.pdf}
-\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
+\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 32 layers or the full layers. }
 \label{fig:multi-parameter}
@@
 Considering limited computing resources, the setup with $10^{5}$ events, 32 layers, and the 15-mm-wide strip was chosen for training the XGB model.
-The training result differs by only 0.$^{\circ}$ from the best setup will full layers.
+The training result differs by only 0.2$^{\circ}$ from the best setup will full layers.
 

### 2022-06-13 paper.tex
updates

@@
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres.pdf}
+\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres_1.pdf}
 }
@@
 We find that 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-We also conclude that using 24 front layers gives the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer.
+We also conclude that using 32 front layers gives the acceptable angular resolution of 1.30~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer.
 We evaluate angular resolutions in terms of the incidence angle and the incident energy.
 The angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$.
-$p_{0}$ is estimated to be 0.43$^{\circ}$ and not dependent on the incidence angle.
-$p_{1}$ is estimated to be 1.28--1.04$^{\circ}$ and gradually decreasing with the incidence angle.
+For large incidence angle ($\theta>$~10~deg), $p_{0}$ and $p_{1}$ are estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
+The angular resolution is largely dependent on the incidence angle for the low incident energy, resulting in smaller values for $p_{1}$.
 
@@
 On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse.
-We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and $10^{5}$ training samples.
+We conclude that 15-mm-wide strips provide the favorable angular resolution with 32 front layers and $10^{5}$ training samples.
 

### 2022-08-03 paper.tex
updates

--- 2022-06-11 paper.tex
@@
 \usepackage{geometry, float}
-\usepackage{biblatex}
-\addbibresource{paper.bib}
+%\usepackage{biblatex}
+%\addbibresource{paper.bib}
 
@@
 \begin{abstract}
-We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
+We report simulation results on the angular resolution of an electromagnetic (EM) sampling calorimeter with photons being in the range of 100~MeV to 2~GeV.
 A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
 The scintillator plates are alternatively segmented in horizontal and vertical strips.
-In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees.
-Angular resolutions are studied in terms of the strip width.
-The 15-mm-wide strips provide acceptable angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-Incident photon directions can be well reconstructed in the front part (6.2$X_{0}$) of the EM calorimeter with the acceptable angular resolution of
-1.30~$\pm$~0.01$^{\circ}$.
-The angular resolution varies significantly with the incident photon energy, and weakly dependent on the incidence angle.
-The energy dependence can be expressed as $\sigma_{\theta}= p_{0} \oplus p_{1} /\sqrt{E_{\gamma}}$.
-For low energy photons, the angular resolution is dependent on the incidence angle, and the dependence disappears as the incident energy increases.
-For the $\theta>$~10 deg, $p_{0}$ and $p_{1}$ are estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
+In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed incident photon angles using the XGBoost with gradient boosted decision trees.
+The performance of the angle reconstruction depends on both of the detector configuration and the goodness of the machine learning.
+The obtained angular resolution can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where the $E_{\gamma}$ is incident photon energy in GeV.
+This energy dependence is consistent for different incident angles in the range of 15 to 40 degrees.
 
@@
 % keywords here, in the form: keyword \sep keyword
-Electromagnetic Calorimeter \sep Geant4 \sep XGBoost \sep KOTO
+Electromagnetic Calorimeter \sep Geant4 \sep XGBoost
 \end{keyword}
@@
 \label{sec:mot}
-Electromagnetic (EM) calorimeter plays an important role in experimental studies for the nuclear and particle physics.
-Various materials have been developed for better energy and timing resolutions so far~\cite{Calorimeter}.
-EM calorimeters can be divided into two groups: sampling calorimeters and homogeneous calorimeters.
-Sampling calorimeters consist of alternating layers of an absorber generating EM showers and an active medium providing signals.
-On the other hand, homogeneous calorimeters are built of only a single type of material that facilitates both EM showers and signal generations.
-Today, the sampling calorimeter becomes very popular in large-scale high energy experiments, owing to its cost-effectiveness.
-In sampling calorimeters the energy deposited in the active medium fluctuates because the active layers are interleaved with absorber layers.
+Electromagnetic (EM) calorimeter plays an important role in experimental studies of nuclear and particle physics~\cite{KOTO:MB, CMS:EMCAL, BELLE:EMCAL}.
+Recently, sampling calorimeters that consist of alternating layers of an absorber generating EM showers and an active medium providing signals have become popular especially in large-scale high energy experiments.
+In sampling calorimeters, energy deposited in the active medium fluctuates because the active layers are interleaved with absorber layers.
 This so-called sampling fluctuation dominates the energy resolution.
+This sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
+A 3-m-long cylindrical calorimeter constructed of alternating layers of Pb and plastic scintillator plates is an example of a sampling calorimeter~\cite{Murayama:2020mcp}.
 
-The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
-A 3-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillator plates is an example of the sampling calorimeter~\cite{Murayama:2020mcp}.
+In addition to the alternating layer structure, the segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction.
+Energy deposits in the active medium segmented in both the longitudinal and lateral directions allow the incident direction of the incoming photon can be deduced.
+A limitation in angular resolution, especially for low energy photons, results from the stochastic behaviors of the EM shower development~\cite{trk:ref}.
+We have performed a simulation study to deduce the incident angle of photon, which will be a starting point to design a detector configuration to provide precise angle measurement for photons.
 
-The segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction.
-The photon direction can also be deduced from the information on the EM shower shape.
-The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTO:2012}.
-
-Stochastic behaviors of the EM shower development limit to the angular resolution of the photon direction measurement.
-Energy deposits in each active layer of a sampling calorimeter fluctuate event by event so that the reconstruction of photon directions necessitates the longitudinal and lateral segmentation of the calorimeter.
-
-This paper describes a machine learning approach based on XGBoost (XGB) model~\cite{xgboost:2016} with boosted decision trees in order to reconstruct the direction of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
-We generated EM showers in a sampling calorimeter using Geant4 simulations.
-We report on the detector configuration providing the acceptable angular resolution, and report on the angular resolution of the EM sampling calorimeter in terms of the incidence angle and the incident energy.
+This paper describes a machine learning approach based on XGBoost (XGB) which is an optimized distributed gradient boosting library~\cite{xgboost:2016}.
+With the machine learning algorithms under the Gradient Boosting framework, we can deduce the direction of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
 
@@
 
-Simulation models of a sampling calorimeter were constructed as a block consisting of alternating layers of a 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
-The plastic scintillator is segmented in 15-mm-wide strips, which are alternatively oriented in vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
-The sampling calorimeter model has a cross-section of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length (20$X_{0}$), which is sufficiently long to absorb full photon energy in the range of 100~MeV to 2~GeV.
+The sampling calorimeter was designed as a block consisting of alternating layers of a 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The plastic scintillator is segmented in 15-mm-wide strips, which are alternatively oriented in the vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
+It has a cross-section of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length, which corresponds to 20 radiation length (20$X_{0}$) that is sufficiently long to absorb full photon energy in the range of 0.1 to 2~GeV.
 
@@
 4.10.06) with the standard EM sub-packages~\cite{GEANT4}.
-The beam direction defines the $z$-axis.
-The photon direction is defined as polar angle ($\theta$) with respect to the $z$-axis.
-Figure~\ref{fig:Evt_Dis} illustrates simulated energy deposit patterns in each strip for a 1-GeV photon at a normal incidence in $xz$- and $yz$-planes.
+The normal direction to the detector surface defines the $z$-axis.
+The photon direction is defines by the polar angle ($\theta$) with respect to the $z$-axis.
+Figure~\ref{fig:Evt_Dis} illustrates simulated energy deposit patterns in each strip for a 1-GeV photon at a normal incident in $xz$- and $yz$-planes.
 Each segmented region in Fig.~\ref{fig:Evt_Dis} represents each channel.
 
-\section{Reconstruction of Incidence Angles}
+\section{Reconstruction of Incident Angles}
 \label{sec:res}
 
-Incidence angles of photons are reconstructed using the XGB model that is a scalable machine learning system for the gradient boosting tree~\cite{xgboost:2016}.
-A machine learning model maps a set of data inputs, known as features, to target variables.
-In this study, the XGB model maps a dataset of energy deposits in each scintillator strip to an incidence angle of a photon.
-Training data were carefully prepared using Geant4 simulation such that the input datasets are representative of a detector response of real sampling calorimeters.
-To minimize data bias, the incidence angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes azimuthal angle.
-Such a wide angular coverage provides good training datasets for the XGB.
+Incident angles of photons are reconstructed using XGB~\cite{xgboost:2016}, which maps a feature, dataset of energy deposits in each scintillator strip, into a target variable, the incident angle of a photon.
+Training data were carefully prepared using the Geant4 simulation such that the input datasets are representative of a detector response of real sampling calorimeters.
+In order to minimize the bias in the training process related to dataset, the incident angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$ where $\varphi$ denotes azimuthal angle.
 The number of training samples is $10^{5}$ considering limited computing resources.
-To test the reconstruction of incidence angles, we generated photons at a fixed incidence angle $\theta$.
-Note that the incident energy is known.
+To test the reconstruction of incident angles, we generated photons at a fixed incident angle $\theta$, with the known incident energy.
 
@@
 \includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
-\caption{ The relative incidence angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+\caption{ The relative incident angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
 The distribution is fitted with the Gaussian and the Generalized Gaussian function.
-The later gives a better result.}
+The Generalized Gaussian function gives a better result.}
 \label{fig:angle_10degree}
@@
 
-Figure~\ref{fig:angle_10degree} represents a distribution of the relative incidence angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-$\Delta\theta$ represents the radial displacement of the reconstructed incidence angle from the true incidence direction.
-The central 98\% part of the distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function.
-We tested two functions, Gaussian and GG to describe the reconstructed angle distribution.
+Figure~\ref{fig:angle_10degree} represents a distribution of the relative incident angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+$\Delta\theta$ represents the radial displacement of the reconstructed incident angle from the true incident direction.
+The central 98\% part of the distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function~\cite{GGfun}.
+We tested two functions, the Gaussian and GG to describe the reconstructed angle distribution.
 The GG function, also known as the generalized error distribution, is expressed as
@@
 \end{eqnarray}
-where $\mu$ denotes a mean value.
+where $\mu$ denotes the mean value.
 Parameters $\alpha$ and $\beta$ determine the scale and shape of the distribution, respectively.
 Variance of the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
-The angular resolution of the incidence angle reconstruction is defined as $\sigma$.
+The angular resolution of the incident angle reconstruction is defined as $\sigma$.
 
@@
 
-We studied a correlation between byperparameters of the XGB model and the angular resolution.
-The test scans the evaluated angular resolution with different hyperparameters.
-Figure~\ref{fig:par_scan} shows the test results with N\_estimators and Max.
+Since the performance of angle reconstruction of the XGB depends on hyperparameters, we scanned evaluated angular resolution by changing the hyperparameters.
+As there are correlations among the hyperparameters, the scanning process was performed in five dimensional space for all possible combinations.
+As an example, figure 4 shows the test results with N\_estimators and Max.
 depth.
@@
 depth defines the complexity of the structure of decision trees.
-The best hyperparameter combination was searched for in terms of the angular resolution.
-As a results, N\_estimators and Max.
+We searched for the hyperparameter combination that generated the best angular resolution.
+As a result, N\_estimators and Max.
 depth are set to 300 and 100, respectively.
-Similar tests were also performed for different hyperparameters.
-The best values for other hyperparameters are displayed in Tab.~\ref{tab:XgbPar}.
-Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma.
-Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added onto the current model.
-Lastly, Gamma regulates the evaluation of each decision tree.
-It is also worth mentioning that the fraction of the tail is not changing from 2\%.
+Similar scans were also performed for different hyperparameters, Subsample, Learning rate, and Gamma.
+Subsample controls the fraction of total event samples for each boosting procedure, Learning rate weights a decision tree to be added onto the current model, and Gamma regulates the evaluation of each decision tree.
+Table~\ref{tab:XgbPar} summarizes optimizes set of hyperparameters which was used for further studies.
+During the optimization process, the fraction of the tail that is not well described by the GG function is around 2\%.
+
 \begin{table}[hbt!]{\small
@@
 
-Angular resolutions were deduced with varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}.
+Angular resolutions were deduced by varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}.
+The narrower the strip width is used, the larger the size of the features becomes.
+As a result, the performance of the angle reconstruction decreases.
+On the other hand, the wider strips hardly provide the detailed information on the EM shower.
 The 15-mm-wide strips yield good angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-The shorter the strip width is, the larger size of features, which can influence negatively in machine learning.
-For longer strips, the EM shower information can hardly be obtained.
 
@@
 
-Furthermore, incidence angles are reconstructed with the front layers of 6.2$X_{0}$ in which more than 99\% of incident photons generate EM showers.
-Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 32 layers of the detector, which correspond to 6.2$X_{0}$ for 1-GeV photons.
-A fraction of photons failed to be reconstructed due to the lack of active layers.
+Focusing only on the angle reconstruction, we design the detector towards the smallest number of layers.
+Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using the front 32 layers of the detector, which correspond to 6.2$X_{0}$, for 1-GeV photons.
+A fraction of photons failed to be reconstructed due to insufficient information caused by deeply penetrating photons without shower generation.
 The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy.
-The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 1.9\%.
+The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while 1.9\% of photons fail to be reconstructed.
 
@@
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_Fit_eres_1.pdf}
 }
-\caption{ Angular resolutions as functions of the incidence angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$ (b) }
+\caption{ Angular resolutions as functions of the incident angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$ (b) }
 \label{fig:angle_reco_dep_gr}
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incidence angle for different incident energies ($E_{\gamma}$).
-The angular resolution does not depend on the incidence angle for high incident energy.
-On the other hand, the angular resolution is especially changing for low incident energy at the small incidence angle.
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident angle for different incident energies ($E_{\gamma}$).
+The angular resolution does not depend on the incident angle for high incident energy.
+On the other hand, the angular resolution changes significantly for low incident energy at small incident angle.
 Figure~\ref{fig:angle_reco_dep_gr} (b) shows the angular resolution as a function of the incident photon energy at $\theta=$~25$^{\circ}$.
-Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
+The angular resolutions fit to a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
 
@@
 \centering
-\includegraphics[width=0.58\textwidth]{figures/Fig7_eres_40deg.pdf}
-\caption{ $p_{1}$ as a function of the incidence angle }
+\includegraphics[width=0.44\textwidth]{figures/Fig7_p0.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_p1.pdf}
+\caption{ $p_{0}$ and $p_{1}$ as a function of the incident angle }
 \label{fig:res_edep}
@@
 
-Figure~\ref{fig:res_edep} shows estimated $p_{1}$ as a function of the incidence angle.
-$p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively.
-For small $\theta$, $p_{1}$ is smaller than larger $\theta$ from the fact that the angular resolution is largely dependent on the incidence angle for the low incident energy.
+Figure~\ref{fig:res_edep} shows estimated $p_{0}$ and $p_{1}$ as a function of the incident angle.
+$p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively in average for $\theta>$~10$^{\circ}$.
+For small $\theta$, $p_{1}$ is smaller than larger $\theta$ from the fact that the angular resolution is largely dependent on the incident angle for the low incident energy while opposite trend can be seen for $p_{0}$.
 
@@
 Figure~\ref{fig:multi-parameter} shows the angular resolution with different numbers of training samples for different detector configurations.
-All configurations show a decrease in the angular resolution with increasing training samples, which means that enhanced statistics for the training results in better reconstruction.
-The angular resolution with 5-mm-wide scintillator strips decreases more rapidly than others.
-The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features.
-Considering limited computing resources, the setup with $10^{5}$ events, 32 layers, and the 15-mm-wide strip was chosen for training the XGB model.
-The training result differs by only 0.2$^{\circ}$ from the best setup will full layers.
+All configurations show improvement in the angular resolution with increasing training samples, which means that the maturity of the machine learning is an important factor on the angle reconstruction.
+The angular resolution with 5-mm-wide scintillator strips is the most rapidly improved with the increasing number of training events.
+That is, the required training events should be large enough to correlate the larger number of features.
+Considering limited computing resources, the configuration of 32 layers and the 15-mm-wide strip with $10^{5}$ training events was chosen for training the XGB model.
+The training result differs by only 0.2$^{\circ}$ from the setup with full layers, 5-mm-wide strips, and $5\times10^{5}$ training events.
 
@@
 
-We report simulation results on the incidece angle reconstruction of EM sampling calorimeters with photons being in the range of 100~MeV to 2~GeV.
-EM shwers are simulated in the new samplinng calorimeter.using Geant4.
-We utilize the XGB model to reconstruct the photon incident angle by correlating all energy deposits in each strip with the incidence angle all events together.
+We report simulation results on the incident angle reconstruction of EM sampling calorimeters with photons in the range of 0.1 to 2~GeV.
+In order to improve the angular resolution, we tune the hyperparameters of the XGBoost taking into account correlating effects among them.
 
-We tune the hyperparameter of the XGB to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration.
-We find that 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
-We also conclude that using 24 front layers gives the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer.
-We evaluate angular resolutions in terms of the incidence angle and the incident energy.
-The angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$.
-$p_{0}$ is estimated to be 0.43$^{\circ}$ and not dependent on the incidence angle.
-$p_{1}$ is estimated to be 1.28--1.04$^{\circ}$ and gradually decreasing with the incidence angle.
+In terms of the detector configuration, strips having narrower width provide better angular resolution using finely measured EM shower with the assumption that the training is fully conducted.
+On the other hand, the configuration with smaller strip width causes larger feature size, which negatively affects the training depending on the quantity of training data.
+We may optimize the angular resolution considering two competing effects from the strip width and the quantity of training data.
+We dedicate front layers of the detector to reconstructing the incident angle.
+We obtain the angular resolution of 1.30~$\pm$~0.01$^{\circ}$ with 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which becomes worse by only 0.1$^{\circ}$ compared to that of the full layers (20$X_{0}$) in case of $10^{5}$ training samples.
 
-Furthermore, we study that the angular resolution is changing with the variation of the training of the XGB and the detector configuration.
-As the strip width decreases, more channels of scintillator strips are required, and the training of the XGB gets affected due to the increased feature size.
-This is quenched with the larger number of training samples, which qualitatively improves the training of the XGB.
-On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse.
-We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and $10^{5}$ training samples.
+The angular resolution depends on photon’s incident energy, where the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
+Except for small incident angles ($\theta<$~15~deg), the two parameters do not significantly change up to 40 degrees and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
 
@@
 
-\section*{Acknowledgement}
-This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and \\ 2020R1A3B2079993).
+\section*{Acknowledgment}
+This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552, \\ 2022R1A5A1030700, and 2020R1A3B2079993)
 
-\printbibliography
+\begin{thebibliography}{99}
+
+\bibitem{KOTO:MB}
+Y. Tajima {\it et al.}, Nucl. Instrum. Meth. A 592, 261 (2008).
+
+\bibitem{CMS:EMCAL}
+Giovanni Mazza {\it et al.} (CMS Collaboration), Nucl. Instrum. Meth. A 958 (2020)
+
+\bibitem{BELLE:EMCAL}
+K. Miyabayashi {\it et al.}, JINST 9 (2014) 09, P09011
+
+\bibitem{Murayama:2020mcp}
+R. Murayama {\it et al.}, Nucl. Instrum. Meth. A 953 (2020)
+
+\bibitem{trk:ref}
+O. Adriani {\it et al.}, Nucl. Instrum. Meth. A 854 (2017)
+
+\bibitem{xgboost:2016}
+C. Tianqi {\it et al.}, 
+{\it Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining},
+(2016) 785.
+
+\bibitem{GGfun}
+D. Gonzalez {\it et al.}, IEEE Trans. Image Processing. 4, 485 (2007)
+
+\bibitem{GEANT4}
+S. Agostinelli {\it et al.},  Nucl. Instr. and Meth. A {\bf 506} (2003) 250.
+
+\end{thebibliography}
+
+%\section*{Acknowledgement}
+%This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and \\ 2020R1A3B2079993).
+
+%\bibliographystyle{elsarticle-num}
+%\bibliography{paper.bib}
+
+%\printbibliography
 

### 2022-08-08 paper.tex
updates

@@
 \setcounter{page}{0}
-\title{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
+\title{Simulation of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
 
@@
 \begin{abstract}
-We report simulation results on the angular resolution of an electromagnetic (EM) sampling calorimeter with photons being in the range of 100~MeV to 2~GeV.
-A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
-The scintillator plates are alternatively segmented in horizontal and vertical strips.
-In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed incident photon angles using the XGBoost with gradient boosted decision trees.
-The performance of the angle reconstruction depends on both of the detector configuration and the goodness of the machine learning.
-The obtained angular resolution can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where the $E_{\gamma}$ is incident photon energy in GeV.
-This energy dependence is consistent for different incident angles in the range of 15 to 40 degrees.
+We report the simulation results for angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
+The simulation model of the EM calorimeter consists of alternating layers of an 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
+The scintillator plates are alternately segmented into horizontal and vertical strips.
+In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed the incident photon angles using XGBoost with gradient-boosted decision trees.
+The performance of the angle reconstruction depends on both the detector configuration and accuracy of machine learning.
+The angular resolution so obtained can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV.
+This energy dependence is consistent for different incident angles
+in the range of 15$^{\circ}$ to 40$^{\circ}$.
 
@@
 \label{sec:mot}
-Electromagnetic (EM) calorimeter plays an important role in experimental studies of nuclear and particle physics~\cite{KOTO:MB, CMS:EMCAL, BELLE:EMCAL}.
-Recently, sampling calorimeters that consist of alternating layers of an absorber generating EM showers and an active medium providing signals have become popular especially in large-scale high energy experiments.
-In sampling calorimeters, energy deposited in the active medium fluctuates because the active layers are interleaved with absorber layers.
+Electromagnetic (EM) calorimeter plays an important role in the experimental studies of nuclear and particle physics~\cite{KOTO:MB, CMS:EMCAL, BELLE:EMCAL}.
+Recently, sampling calorimeters consisting of alternating layers of an absorber that generates EM showers and an active medium that provides signals have become popular, especially in large-scale high-energy experiments.
+In sampling calorimeters, the energy deposited in the active medium fluctuates because the active layers are interleaved with the absorber layers.
 This so-called sampling fluctuation dominates the energy resolution.
@@
 
-In addition to the alternating layer structure, the segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction.
-Energy deposits in the active medium segmented in both the longitudinal and lateral directions allow the incident direction of the incoming photon can be deduced.
-A limitation in angular resolution, especially for low energy photons, results from the stochastic behaviors of the EM shower development~\cite{trk:ref}.
-We have performed a simulation study to deduce the incident angle of photon, which will be a starting point to design a detector configuration to provide precise angle measurement for photons.
+In addition to the alternating layer structure, the segmented structure of the active medium facilitates the measurement of the lateral distributions of the EM shower along the incident photon direction.
+Energy deposits in the active medium segmented in both the longitudinal and lateral directions allow for the deduction of the incident direction of the incoming photon.
+A limitation in the angular resolution, especially for low-energy photons, results from the stochastic behavior of EM shower development~\cite{trk:ref}.
+We performed a simulation study to deduce the incident angle of the photons, which can be a starting point for designing a detector configuration to provide precise angle measurements for photons.
 
-This paper describes a machine learning approach based on XGBoost (XGB) which is an optimized distributed gradient boosting library~\cite{xgboost:2016}.
-With the machine learning algorithms under the Gradient Boosting framework, we can deduce the direction of incident photons entering a sampling calorimeter with alternating layers of a Pb plate and plastic scintillator strips in horizontal and vertical directions.
+This study describes a machine-learning approach based on XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.
+With machine-learning algorithms under the gradient boosting framework, we can deduce the direction of the incident photons entering a sampling calorimeter with alternating layers of Pb plate and plastic scintillator strips in the horizontal and vertical directions.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/Fig1_detector_schematic.jpeg}
-\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb plate and a segmented scintillator plate in 35 strips.
+\includegraphics[width=0.6\textwidth]{Fig1_detector_schematic.jpeg}
+\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb and segmented scintillator plate in 35 strips.
 Each scintillator plate is oriented alternatively in horizontal and vertical directions.
@@
 
-The sampling calorimeter was designed as a block consisting of alternating layers of a 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
-The plastic scintillator is segmented in 15-mm-wide strips, which are alternatively oriented in the vertical and horizontal directions as shown in Fig.~\ref{fig:det_conf}.
-It has a cross-section of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length, which corresponds to 20 radiation length (20$X_{0}$) that is sufficiently long to absorb full photon energy in the range of 0.1 to 2~GeV.
+The sampling calorimeter was designed as a block consisting of alternating layers of an 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The plastic scintillator is segmented into 15-mm-wide strips, which are alternatively oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
+It has a cross-section of size 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length, which corresponds to 20 radiation lengths (20$X_{0}$) that are sufficiently long to absorb full photon energy in the range of 0.1 to 2~GeV.
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_XZ.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_YZ.pdf}
-\caption{ Event display of simulated energy deposit patterns for a 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
+\includegraphics[width=0.48\textwidth]{Fig2_EMShower_XZ.pdf}
+\includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
+\caption{ Event display of simulated energy deposit patterns for an 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
 \label{fig:Evt_Dis}
@@
 
-The detector response to incident photons was simulated using Geant4 (ver.
-4.10.06) with the standard EM sub-packages~\cite{GEANT4}.
-The normal direction to the detector surface defines the $z$-axis.
-The photon direction is defines by the polar angle ($\theta$) with respect to the $z$-axis.
-Figure~\ref{fig:Evt_Dis} illustrates simulated energy deposit patterns in each strip for a 1-GeV photon at a normal incident in $xz$- and $yz$-planes.
-Each segmented region in Fig.~\ref{fig:Evt_Dis} represents each channel.
+The detector response to the incident photons was simulated using Geant4 (ver.
+4.10.06) with standard EM sub-packages~\cite{GEANT4}.
+The direction normal to the detector surface defines the $z$-axis.
+The photon direction was defined by the polar angle ($\theta$) with respect to the $z$-axis.
+Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for an 1-GeV photon at normal incidence in the $xz$- and $yz$-planes.
+Each segmented region shown in Figure~\ref{fig:Evt_Dis} represents a channel.
 
@@
 
-Incident angles of photons are reconstructed using XGB~\cite{xgboost:2016}, which maps a feature, dataset of energy deposits in each scintillator strip, into a target variable, the incident angle of a photon.
-Training data were carefully prepared using the Geant4 simulation such that the input datasets are representative of a detector response of real sampling calorimeters.
-In order to minimize the bias in the training process related to dataset, the incident angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$ where $\varphi$ denotes azimuthal angle.
-The number of training samples is $10^{5}$ considering limited computing resources.
-To test the reconstruction of incident angles, we generated photons at a fixed incident angle $\theta$, with the known incident energy.
+The incident angles of the photons are reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset of the energy deposits in each scintillator strip onto a target variable, the incident angle of a photon.
+Training data were carefully prepared using the Geant4 simulation such that the input datasets were representative of the detector response of the real sampling calorimeters.
+To minimize the bias in the training process related to the dataset, the incident angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes the azimuthal angle.
+The number of training samples was $10^{5}$ considering the limited computing resources.
+To test the reconstruction of the incident angles, we generated photons at a fixed incident angle $\theta$ with a known incident energy.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
+\includegraphics[width=0.7\textwidth]{Fig3_fit_GG.pdf}
 \caption{ The relative incident angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-The distribution is fitted with the Gaussian and the Generalized Gaussian function.
-The Generalized Gaussian function gives a better result.}
+The distribution is fitted with the Gaussian and generalized Gaussian functions.
+The generalized Gaussian function gives a better result.}
 \label{fig:angle_10degree}
@@
 
-Figure~\ref{fig:angle_10degree} represents a distribution of the relative incident angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-$\Delta\theta$ represents the radial displacement of the reconstructed incident angle from the true incident direction.
-The central 98\% part of the distribution is fitted with the Gaussian function and the Generalized Gaussian (GG) function~\cite{GGfun}.
-We tested two functions, the Gaussian and GG to describe the reconstructed angle distribution.
-The GG function, also known as the generalized error distribution, is expressed as
+Figure~\ref{fig:angle_10degree} represents the distribution of the relative incident angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
+$\Delta\theta$ represents the radial displacement of the reconstructed incident angle relative to the true incident direction.
+The central 98\% of the distribution is fitted with the Gaussian and generalized Gaussian (GG) functions~\cite{GGfun}.
+We tested two functions, Gaussian and GG, to describe the reconstructed angular distribution.
+The GG function, also known as the generalized error distribution, is expressed as:
 \begin{eqnarray} 
@@
 \end{eqnarray}
-where $\mu$ denotes the mean value.
-Parameters $\alpha$ and $\beta$ determine the scale and shape of the distribution, respectively.
-Variance of the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
+where $\mu$ is the mean value.
+The parameters $\alpha$ and $\beta$ determine the scale and shape of the distribution, respectively.
+The variance in the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
 The angular resolution of the incident angle reconstruction is defined as $\sigma$.
@@
 \centering
-\includegraphics[width=0.69\textwidth]{figures/Fig4_Opt.pdf}
+\includegraphics[width=0.69\textwidth]{Fig4_Opt.pdf}
 \caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
@@
 
-Since the performance of angle reconstruction of the XGB depends on hyperparameters, we scanned evaluated angular resolution by changing the hyperparameters.
-As there are correlations among the hyperparameters, the scanning process was performed in five dimensional space for all possible combinations.
-As an example, figure 4 shows the test results with N\_estimators and Max.
+Because the performance of the angle reconstruction of the XGB depends on the hyperparameters, we scanned the evaluated angular resolution by changing the hyperparameters.
+As there were correlations among the hyperparameters, the scanning process was performed in a five-dimensional space for all possible combinations.
+As an example, Figure 4 shows the test results for N\_estimators and Max.
 depth.
-N\_estimators defines the maximum allowed number of decision trees to be developed, and the Max.
-depth defines the complexity of the structure of decision trees.
-We searched for the hyperparameter combination that generated the best angular resolution.
-As a result, N\_estimators and Max.
-depth are set to 300 and 100, respectively.
-Similar scans were also performed for different hyperparameters, Subsample, Learning rate, and Gamma.
-Subsample controls the fraction of total event samples for each boosting procedure, Learning rate weights a decision tree to be added onto the current model, and Gamma regulates the evaluation of each decision tree.
-Table~\ref{tab:XgbPar} summarizes optimizes set of hyperparameters which was used for further studies.
-During the optimization process, the fraction of the tail that is not well described by the GG function is around 2\%.
+N\_estimators defines the maximum allowed number of decision trees to be developed, and Max.
+depth defines the complexity of the decision-tree structure.
+We explored a hyperparameter combination that generated the best angular resolution.
+Consequently, the N\_estimators and Max.
+depth were set to 300 and 100, respectively.
+Similar scans were also performed for different hyperparameters, subsample, learning rates, and gamma values.
+Subsample controls the fraction of total event samples for each boosting procedure, the learning rate weights a decision tree to be added onto the current model, and the gamma value regulates the evaluation of each decision tree.
+Table~\ref{tab:XgbPar} lists the optimized set of hyperparameters that are used in further studies.
+During the optimization process, the fraction of the tail that is not well described by the GG function is approximately 2\%.
 
@@
 \centering
-\includegraphics[width=0.58\textwidth]{figures/Fig5_width.pdf}
+\includegraphics[width=0.58\textwidth]{Fig5_width.pdf}
 \caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
@@
 
-Angular resolutions were deduced by varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}.
-The narrower the strip width is used, the larger the size of the features becomes.
-As a result, the performance of the angle reconstruction decreases.
-On the other hand, the wider strips hardly provide the detailed information on the EM shower.
-The 15-mm-wide strips yield good angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+Angular resolutions were deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
+The narrower the strip width, the larger is the size of the features.
+Consequently, the angle-reconstruction performance declines.
+However, the wider strips hardly provide detailed information on the EM shower.
+The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
 
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig6_layer_comp.pdf}
+\includegraphics[width=0.48\textwidth]{Fig6_layer_comp.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{ 
-\includegraphics[width=0.48\textwidth]{figures/Fig6_nlayer.pdf}
+\includegraphics[width=0.48\textwidth]{Fig6_nlayer.pdf}
 }
 \caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$.
-Red histogram represents the polar angle distribution by requiring $E_{\rm{tot}}>$~10~MeV.
-(b) Angular resolution as a function of radiation length ($X_{0}$).}
+The red histogram represents the polar angle distribution for $E_{\rm{tot}}>$~10~MeV.
+(b) Angular resolution as a function of the radiation length ($X_{0}$).}
 \label{fig:angle_reco_layer}
@@
 
-Focusing only on the angle reconstruction, we design the detector towards the smallest number of layers.
-Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using the front 32 layers of the detector, which correspond to 6.2$X_{0}$, for 1-GeV photons.
-A fraction of photons failed to be reconstructed due to insufficient information caused by deeply penetrating photons without shower generation.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy.
-The angular resolution with the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ while 1.9\% of photons fail to be reconstructed.
+Focusing only on the angle reconstruction, we designed the detector with the smallest number of layers.
+Figure~\ref{fig:angle_reco_layer} (a) shows the angles reconstructed using the front 32 layers of the detector, which correspond to 6.2$X_{0}$, for 1-GeV photons.
+A fraction of the photons fail to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation.
+The failed events are represented as a delta function near 0, and such events are removed by fixing the total energy deposit at a value higher than 10~MeV, which is 1\% of the incident energy.
+The angular resolution of the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ when 1.9\% of the photons fail to be reconstructed.
 
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_res_ene.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.44\textwidth]{figures/Fig7_Fit_eres_1.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_Fit_eres_1.pdf}
 }
-\caption{ Angular resolutions as functions of the incident angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$ (b) }
+\caption{ (a) Angular resolution as a function of the incident angle for different incident energies.
+(b) Angular resolution as a function of the incident energy for $\theta=$~25$^{\circ}$; it is fitted to the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$ }
 \label{fig:angle_reco_dep_gr}
@@
 
-Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident angle for different incident energies ($E_{\gamma}$).
-The angular resolution does not depend on the incident angle for high incident energy.
-On the other hand, the angular resolution changes significantly for low incident energy at small incident angle.
+Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of incident angle for different incident energies ($E_{\gamma}$).
+The angular resolution does not depend on the incident angle for high incident energies.
+However, the angular resolution changes significantly for low incident energies at small incident angles.
 Figure~\ref{fig:angle_reco_dep_gr} (b) shows the angular resolution as a function of the incident photon energy at $\theta=$~25$^{\circ}$.
-The angular resolutions fit to a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.
+The angular resolution fits to the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$, where $p_{0}$ and $p_{1}$ represent the energy-independent and energy-dependent contributions, respectively.
 
@@
 \centering
-\includegraphics[width=0.44\textwidth]{figures/Fig7_p0.pdf}
-\includegraphics[width=0.44\textwidth]{figures/Fig7_p1.pdf}
-\caption{ $p_{0}$ and $p_{1}$ as a function of the incident angle }
+\includegraphics[width=0.44\textwidth]{Fig7_p0.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_p1.pdf}
+\caption{ $p_{0}$ and $p_{1}$ values as functions of the incident angle }
 \label{fig:res_edep}
@@
 
-Figure~\ref{fig:res_edep} shows estimated $p_{0}$ and $p_{1}$ as a function of the incident angle.
-$p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively in average for $\theta>$~10$^{\circ}$.
-For small $\theta$, $p_{1}$ is smaller than larger $\theta$ from the fact that the angular resolution is largely dependent on the incident angle for the low incident energy while opposite trend can be seen for $p_{0}$.
+Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ values as functions of the incident angle.
+The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
+For a small $\theta$, $p_{1}$ is smaller than that for a larger $\theta$ because the angular resolution is largely dependent on the incident angle for low incident energies, whereas the opposite trend can be observed for $p_{0}$.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/Fig8_nsample.pdf}
-\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 32 layers or the full layers. }
+\includegraphics[width=0.6\textwidth]{Fig8_nsample.pdf}
+\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers.
+}
 \label{fig:multi-parameter}
@@
 
-Figure~\ref{fig:multi-parameter} shows the angular resolution with different numbers of training samples for different detector configurations.
-All configurations show improvement in the angular resolution with increasing training samples, which means that the maturity of the machine learning is an important factor on the angle reconstruction.
-The angular resolution with 5-mm-wide scintillator strips is the most rapidly improved with the increasing number of training events.
-That is, the required training events should be large enough to correlate the larger number of features.
-Considering limited computing resources, the configuration of 32 layers and the 15-mm-wide strip with $10^{5}$ training events was chosen for training the XGB model.
-The training result differs by only 0.2$^{\circ}$ from the setup with full layers, 5-mm-wide strips, and $5\times10^{5}$ training events.
+Figure~\ref{fig:multi-parameter} shows the angular resolution for different numbers of training samples and different detector configurations.
+All configurations show improvement in the angular resolution with increasing training samples, which indicates that the maturity of machine learning is an important factor in angle reconstruction.
+With an increase in the number of training events, the Angular resolution improves most rapidly for the configuration with 5-mm-wide scintillator strips.
+In other words, the required training events must be sufficiently large to correlate a larger number of features.
+Considering the limited computing resources, the configuration of 32 layers and 15-mm-wide strip with $10^{5}$ training events was chosen to train the XGB model.
+The training result for such a configuration differs by only 0.2$^{\circ}$ from that of the setup with full layers, 5-mm-wide strips, and $5\times10^{5}$ training events.
 
-\section{SUMMARY}
+\section{Summary}
 \label{sec:sum}
 
-We report simulation results on the incident angle reconstruction of EM sampling calorimeters with photons in the range of 0.1 to 2~GeV.
-In order to improve the angular resolution, we tune the hyperparameters of the XGBoost taking into account correlating effects among them.
+We report the simulation results of the incident angle reconstruction of EM sampling calorimeters with photons in the range of 0.1 to 2~GeV.
+~To improve the angular resolution, we tuned the hyperparameters of XGBoost while considering the correlating effects among them.
 
-In terms of the detector configuration, strips having narrower width provide better angular resolution using finely measured EM shower with the assumption that the training is fully conducted.
-On the other hand, the configuration with smaller strip width causes larger feature size, which negatively affects the training depending on the quantity of training data.
-We may optimize the angular resolution considering two competing effects from the strip width and the quantity of training data.
-We dedicate front layers of the detector to reconstructing the incident angle.
-We obtain the angular resolution of 1.30~$\pm$~0.01$^{\circ}$ with 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which becomes worse by only 0.1$^{\circ}$ compared to that of the full layers (20$X_{0}$) in case of $10^{5}$ training samples.
+In terms of detector configuration, strips with narrower widths provide better angular resolution using a finely measured EM shower with the assumption that the training is fully conducted.
+However, the configuration with a smaller strip width causes a larger feature size, which negatively affects the training depending on the quantity of training data.
+The angular resolution may be optimized by considering the two competing effects of the strip width and quantity of training data.
+We dedicated the front layers of the detector to reconstructing the incident angle.
+We obtain an angular resolution of 1.30~$\pm$~0.01$^{\circ}$ for the configuration of 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which is a reduction of 0.1$^{\circ}$ compared to that of the configuration with full layers (20$X_{0}$) in the case of $10^{5}$ training samples.
 
-The angular resolution depends on photon’s incident energy, where the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
-Except for small incident angles ($\theta<$~15~deg), the two parameters do not significantly change up to 40 degrees and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
+The angular resolution depends on the incident energy of the photon, and the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
+Except for small incident angles ($\theta<$~15~deg), the two parameters do not significantly change up to
+$40^{\circ}$, and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
 
@@
 \section*{Acknowledgment}
-This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552, \\ 2022R1A5A1030700, and 2020R1A3B2079993)
+This work was supported by the National Research Foundation of Korea (NRF) 
+(Grants No. 2019R1A2C1084552, 2022R1A5A1030700, and 2020R1A3B2079993) and JSPS KAKENHI Grant No. JP21H01118.
+%%%the Ministry of Education, Culture, Sports, Science, and Technology (MEXT) of Japan and the Japan Society for the Promotion of Science (JSPS) under the MEXT KAKENHI Grant No. JP21H01118.
 

### 2022-08-08 paper.tex
update

@@
 \centering
-\includegraphics[width=0.6\textwidth]{Fig1_detector_schematic.jpeg}
+\includegraphics[width=0.6\textwidth]{figures/Fig1_detector_schematic.jpeg}
 \caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb and segmented scintillator plate in 35 strips.
@@
 \centering
-\includegraphics[width=0.48\textwidth]{Fig2_EMShower_XZ.pdf}
-\includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_XZ.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_YZ.pdf}
 \caption{ Event display of simulated energy deposit patterns for an 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{Fig3_fit_GG.pdf}
+\includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
 \caption{ The relative incident angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
@@
 \centering
-\includegraphics[width=0.69\textwidth]{Fig4_Opt.pdf}
+\includegraphics[width=0.69\textwidth]{figures/Fig4_Opt.pdf}
 \caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
@@
 depth were set to 300 and 100, respectively.
-Similar scans were also performed for different hyperparameters, subsample, learning rates, and gamma values.
-Subsample controls the fraction of total event samples for each boosting procedure, the learning rate weights a decision tree to be added onto the current model, and the gamma value regulates the evaluation of each decision tree.
+Similar scans were also performed for different hyperparameters, subsample, learning rates, and gamma.
+Subsample controls the fraction of total event samples for each boosting procedure, the learning rate weights a decision tree to be added onto the current model, and the gamma regulates the evaluation of each decision tree.
 Table~\ref{tab:XgbPar} lists the optimized set of hyperparameters that are used in further studies.
@@
 \centering
-\includegraphics[width=0.58\textwidth]{Fig5_width.pdf}
+\includegraphics[width=0.58\textwidth]{figures/Fig5_width.pdf}
 \caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{Fig6_layer_comp.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig6_layer_comp.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{ 
-\includegraphics[width=0.48\textwidth]{Fig6_nlayer.pdf}
+\includegraphics[width=0.48\textwidth]{figures/Fig6_nlayer.pdf}
 }
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.44\textwidth]{Fig7_res_ene.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.44\textwidth]{Fig7_Fit_eres_1.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_Fit_eres_1.pdf}
 }
@@
 \centering
-\includegraphics[width=0.44\textwidth]{Fig7_p0.pdf}
-\includegraphics[width=0.44\textwidth]{Fig7_p1.pdf}
-\caption{ $p_{0}$ and $p_{1}$ values as functions of the incident angle }
+\includegraphics[width=0.44\textwidth]{figures/Fig7_p0.pdf}
+\includegraphics[width=0.44\textwidth]{figures/Fig7_p1.pdf}
+\caption{ $p_{0}$ and $p_{1}$ as functions of the incident angle }
 \label{fig:res_edep}
@@
 
-Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ values as functions of the incident angle.
+Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ as functions of the incident angle.
 The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{Fig8_nsample.pdf}
+\includegraphics[width=0.6\textwidth]{figures/Fig8_nsample.pdf}
 \caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers.

### 2022-08-11 paper.tex
u

@@
 \setcounter{page}{0}
-\title{Simulation of Angular Resolution of a New Electromagnetic Sampling Calorimeter}
+\title{Simulation of angular resolution of a new electromagnetic sampling calorimeter}
 
@@
 This study describes a machine-learning approach based on XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.
-With machine-learning algorithms under the gradient boosting framework, we can deduce the direction of the incident photons entering a sampling calorimeter with alternating layers of Pb plate and plastic scintillator strips in the horizontal and vertical directions.
+With machine-learning algorithms under the gradient-boosting framework, we can deduce the direction of the incident photons entering a sampling calorimeter with alternating layers of Pb plate and plastic scintillator strips in the horizontal and vertical directions.
 
-\section{Electromagnetic Shower Simulation}
+\section{Electromagnetic shower simulation}
 \label{sec:ems}
@@
 \caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb and segmented scintillator plate in 35 strips.
-Each scintillator plate is oriented alternatively in horizontal and vertical directions.
+Each scintillator plate is oriented alternately in horizontal and vertical directions.
 See text for details.
@@
 The sampling calorimeter was designed as a block consisting of alternating layers of an 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
-The plastic scintillator is segmented into 15-mm-wide strips, which are alternatively oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
+The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
 It has a cross-section of size 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length, which corresponds to 20 radiation lengths (20$X_{0}$) that are sufficiently long to absorb full photon energy in the range of 0.1 to 2~GeV.
@@
 
-\section{Reconstruction of Incident Angles}
+\section{Reconstruction of incident angles}
 \label{sec:res}
@@
 The narrower the strip width, the larger is the size of the features.
-Consequently, the angle-reconstruction performance declines.
+Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than 5-mm-wide strips.
 However, the wider strips hardly provide detailed information on the EM shower.
@@
 A fraction of the photons fail to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation.
-The failed events are represented as a delta function near 0, and such events are removed by fixing the total energy deposit at a value higher than 10~MeV, which is 1\% of the incident energy.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be higher than 10~MeV, which is 1\% of the incident energy.
 The angular resolution of the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ when 1.9\% of the photons fail to be reconstructed.
@@
 \includegraphics[width=0.44\textwidth]{figures/Fig7_p1.pdf}
-\caption{ $p_{0}$ and $p_{1}$ as functions of the incident angle }
+\caption{ $p_{0}$ and $p_{1}$ as a function of the incident angle }
 \label{fig:res_edep}
@@
 
-Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ as functions of the incident angle.
+Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ as a function of the incident angle.
 The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
@@
 The angular resolution depends on the incident energy of the photon, and the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
-Except for small incident angles ($\theta<$~15~deg), the two parameters do not significantly change up to
+Except for small incident angles ($\theta<$~$^{\circ}$~deg), the two parameters do not significantly change up to
 $40^{\circ}$, and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.

### 2023-01-16 paper.tex
updates

@@
-\documentclass[preprint,12pt,times,a4paper]{elsarticle}
+\documentclass[12pt,times,draftclsnofoot,a4paper]{elsarticle}
 
 \usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{amsmath}
 \usepackage{lineno}
@@
 \usepackage{xcolor}
+\usepackage{comment}
 \usepackage[bitstream-charter]{mathdesign}
@@
 \usepackage{geometry, float}
-%\usepackage{biblatex}
-%\addbibresource{paper.bib}
-
-\geometry{a4paper}
-
 \usepackage[normalem]{ulem}
@@
 \journal{Nuclear Instruments and Methods in Physics Research A}
-
-\newcommand{\XGB}{XGBoost}
 
@@
 \begin{abstract}
-We report the simulation results for angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
-The simulation model of the EM calorimeter consists of alternating layers of an 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate.
+We report on the simulation results for angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
+The simulation model of the EM calorimeter consists of alternating layers of an 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate.
 The scintillator plates are alternately segmented into horizontal and vertical strips.
@@
 The performance of the angle reconstruction depends on both the detector configuration and accuracy of machine learning.
-The angular resolution so obtained can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV.
-This energy dependence is consistent for different incident angles
-in the range of 15$^{\circ}$ to 40$^{\circ}$.
+The angular resolution so obtained can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
+This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.
 
@@
 
+\linenumbers
+
 \section{Motivation}
 \label{sec:mot}
-Electromagnetic (EM) calorimeter plays an important role in the experimental studies of nuclear and particle physics~\cite{KOTO:MB, CMS:EMCAL, BELLE:EMCAL}.
-Recently, sampling calorimeters consisting of alternating layers of an absorber that generates EM showers and an active medium that provides signals have become popular, especially in large-scale high-energy experiments.
-In sampling calorimeters, the energy deposited in the active medium fluctuates because the active layers are interleaved with the absorber layers.
-This so-called sampling fluctuation dominates the energy resolution.
-This sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium.
-A 3-m-long cylindrical calorimeter constructed of alternating layers of Pb and plastic scintillator plates is an example of a sampling calorimeter~\cite{Murayama:2020mcp}.
 
-In addition to the alternating layer structure, the segmented structure of the active medium facilitates the measurement of the lateral distributions of the EM shower along the incident photon direction.
-Energy deposits in the active medium segmented in both the longitudinal and lateral directions allow for the deduction of the incident direction of the incoming photon.
-A limitation in the angular resolution, especially for low-energy photons, results from the stochastic behavior of EM shower development~\cite{trk:ref}.
-We performed a simulation study to deduce the incident angle of the photons, which can be a starting point for designing a detector configuration to provide precise angle measurements for photons.
+Calorimeter plays an important role in the experimental studies of nuclear and particle physics~\cite{unitext}.
+An ideal calorimeter fully absorbs the energy of the entering particle and converts the energy into measurable quantities.
+The sampling calorimeter consists of different materials, one is the absorber generating a shower of secondary particles, and the other is an active medium that generates signals from the energy deposits of the secondaries.
+Because the energy deposit in the active medium fluctuates associated with the dense absorber, the sampling calorimeter has an inevitable drawback in energy resolution, especially in the measurement of gamma.
+This effect can be controlled by adjusting the material budget between the absorber and active medium and their configuration.
+Also, it becomes less critical as gamma energy becomes higher.
 
-This study describes a machine-learning approach based on XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.
-With machine-learning algorithms under the gradient-boosting framework, we can deduce the direction of the incident photons entering a sampling calorimeter with alternating layers of Pb plate and plastic scintillator strips in the horizontal and vertical directions.
+In general, the sampling calorimeter enables cost-effective fabrication of large-scale detectors and design of flexible geometric configuration.
+This detector has been developed in various ways by selecting a material of absorber among many caodidates such as brass~\cite{CMS:mat}, lead~\cite{CDF:mat}, tungsten~\cite{DELPHI:mat}, uranium~\cite{UGAS:mat}, and also of active medium such as scintillators~\cite{CMS:mat,CDF:mat}, gas~\cite{UGAS:mat}, solid-state detector~\cite{DELPHI:mat}, and liquid gas~\cite{LiqAR:mat}.
+Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}.
+
+The sampling calorietmer has been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics.
+The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils.
+Tracking with the silicon detectors on the electron-positron pairs produced at the foils provides an angular resolution of 0.6 degrees for 1-GeV photons and better than 0.16 degrees for energy higher than 10~GeV~\cite{FERMI:LAT}.
+The LAT has two additional components: a scintillating plastic for the charged-particle detection and a homogeneous CsI crystals for energy measurement.
+This triple detector configuration is also used in different missions.
+An energy spectrum measurement of cosmic-ray electrons (CALET)~\cite{CALET} utilizes scintillating fibers and PWO crystals instead of the silicon strips and the CsI crystals, respectively.
+A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for energy measurement.
+The angular resolution of the detector is obtained as 1--2 degrees for 1-GeV photons.
+
+In the accelerator-based experiments, the direction of photons can be precisely obtained by connecting the interaction position obtained from charged particle tracks to their incident position measured at the calorimeter.
+However, it is not possible to reconstruct the interaction (decay) position when we observe $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay, in which no charged particle exists.
+The decay is explained with a CP-violating Flavor Changing Neutral Current process and has significant potential to provide clues to new physics beyond the Standard Model (SM).
+Its branching fraction is calculated to be extremely small as 3~$\times$~10$^{-11}$ in the SM~\cite{KOTOtheory}, which implies that the effect of new physics on the decay could overwhelm that of the SM.
+Any observed deviation from the SM prediction will indicate new physics without hesitation, thanks to the small uncertainty in the theoretical calculation.
+
+The $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay is identified as a final state existing only a single $\pi^{0}$ reconstructed from detected two photons.
+A hermetic detector system enclosing the decay region should be prepared to confirm only two photons in the final state.
+There had been an experimental proposal to detect the $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with the reconstruction of a single $\pi^{0}$ using directional information of two photons~\cite{KOPIO}.
+A Preradiator (PR) is placed in front of the calorimeter to measure the photon's incident angle.
+The PR consists of a close-packed multi-layer sandwich of 8-mm-thick scintillating plastics alternating with the single-plane and this-gap drift chambers with cathode strips.
+For good energy resolution and high detection efficiency against a few hundred MeV photons, the scintillating plastic is used for electron-positron conversion.
+This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250~MeV~\cite{KOPIOcdr}.
+Unfortunately, the proposal was not accepted, and the detector development could not continue.
+
+On the other hand, the KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with a well-collimated small-size neutral beam, which constrains the transverse decay position to be at the beam axis.
+With this assumption, the distance between the decay position and the calorimeter is calculated from the positions and energies of the two photons, and the transverse momentum of $\pi^{0}$ is obtained.
+The two variables, the longitudinal decay position and the transverse momentum, are used to define a signal region of the decay.
+The KOTO experiment started data taking in 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
+The data taking will continue for  several more years, and the sensitivity will reach 10$^{-11}$.
+It is still not enough to determine the branching fraction if it is close to the SM expectations.
+
+A successive experiment of the KOTO is under preparation to observe more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}.
+In this higher-sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$.
+In addition, the neutrons away from the beam axis produce a $\pi^{0}$ or $\eta$ by interacting with detector materials.
+Two photons from those events are also one of main backgrounds.
+We can remove them by comparing the incident angle expected from the reconstructed vertex and the actual measurement using a new sampling calorimeter in this paper.
+
+In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and scintillating plastic layers.
+There is a limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation.
+A deduction of the incident angle of the EM shower using a lead scintillating fiber sandwiched sampling calorimeter is studied~\cite{PbScint}, and the obtained angular resolution is 0.8 degrees for 100-GeV electrons and expected to be larger than 8 degrees for 1-GeV electrons.
+We take a machine-learning approach to get better angular resolution from the analysis.
+Recently, machine-learning analysis has become a critical tool for better measurement of particle identification~\cite{mlp}, timing~\cite{mlt}, and energy~\cite{mle}.
+We use the XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.
+
+A description on the detector configuration and Monte Carlo generation will be given in Section~\ref{sec:ems}.
+In the Section~\ref{sec:res}, results of the machine learning studies on the generated data will be presented, and a summary will follow in the Section~\ref{sec:sum}.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/Fig1_detector_schematic.jpeg}
-\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb and segmented scintillator plate in 35 strips.
-Each scintillator plate is oriented alternately in horizontal and vertical directions.
+\includegraphics[width=0.6\textwidth]{Fig1_detector_schematic.jpeg}
+\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of lead and scintillator plates.
+Each plate is segmented in 35 strips, oriented alternately in horizontal and vertical directions.
 See text for details.
@@
 
-The sampling calorimeter was designed as a block consisting of alternating layers of an 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
-It has a cross-section of size 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length, which corresponds to 20 radiation lengths (20$X_{0}$) that are sufficiently long to absorb full photon energy in the range of 0.1 to 2~GeV.
+It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain photons showers for energies in the range of 0.1 to 2~GeV.
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_XZ.pdf}
-\includegraphics[width=0.48\textwidth]{figures/Fig2_EMShower_YZ.pdf}
+\includegraphics[width=0.48\textwidth]{Fig2_EMShower_XZ.pdf}
+\includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
 \caption{ Event display of simulated energy deposit patterns for an 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
@@
 
-The detector response to the incident photons was simulated using Geant4 (ver.
+The detector response to the incident photons is simulated using Geant4 (ver.
 4.10.06) with standard EM sub-packages~\cite{GEANT4}.
-The direction normal to the detector surface defines the $z$-axis.
-The photon direction was defined by the polar angle ($\theta$) with respect to the $z$-axis.
+The direction normal to the front surface defines the $z$-axis.
+The photon direction is defined by the polar angle ($\theta$) with respect to the $z$-axis.
 Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for an 1-GeV photon at normal incidence in the $xz$- and $yz$-planes.
@@
 
-\section{Reconstruction of incident angles}
+Training data for machine learning are prepared using the Geant4 simulation such that the input dataset is representative of the detector response of the sampling calorimeter.
+In order to minimize the bias in the training process related to the dataset, the incident angles are uniformly generated at the detector surface in the range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes the azimuthal angle.
+The number of training samples is $10^{5}$ considering the limited computing resources.
+To test the reconstruction of the incident angles, photons are generated at a fixed incident angle $\theta$ with known incident energy and incident position.
+Possible noise effects are not simulated in this paper. Instead, application of lower threshold of 0.5~MeV for each strip is tested and found to provide the consistent result without threshold. %%%
+\section{Results}
 \label{sec:res}
+\subsection{Reconstruction of incident angles}
+\label{sec:reco}
 
-The incident angles of the photons are reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset of the energy deposits in each scintillator strip onto a target variable, the incident angle of a photon.
-Training data were carefully prepared using the Geant4 simulation such that the input datasets were representative of the detector response of the real sampling calorimeters.
-To minimize the bias in the training process related to the dataset, the incident angles were uniformly generated at the detector surface in the angular range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes the azimuthal angle.
-The number of training samples was $10^{5}$ considering the limited computing resources.
-To test the reconstruction of the incident angles, we generated photons at a fixed incident angle $\theta$ with a known incident energy.
+The incident angles of the photons are reconstructed using XGBoost~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
+XGBoost constructs  gradient-boosted decision trees using the training dataset, efficiently descending the loss function.
+The size of feature, which is identical with the number of strips, varies with the strip width to have the same coverage.
+In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector.
+Hyperparameters of XGBoost drive how models are trained.
+Main five parameters are studied in this paper.
+\textit{N\_estimators} defines the maximum allowed number of decision trees to be developed, and  \textit{Max.
+depth} defines the complexity of the decision-tree structure.
+\textit{Subsample} controls the fraction of total event samples for each boosting procedure,  \textit{learning rate} weights a decision tree to be added onto the current model, and  \textit{gamma} regulates the evaluation of each decision tree.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figures/Fig3_fit_GG.pdf}
+\includegraphics[width=0.7\textwidth]{Fig3_fit_GG.pdf}
 \caption{ The relative incident angle for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
 The distribution is fitted with the Gaussian and generalized Gaussian functions.
-The generalized Gaussian function gives a better result.}
+The generalized Gaussian function describes the obtained distribution better.}
 \label{fig:angle_10degree}
@@
 Figure~\ref{fig:angle_10degree} represents the distribution of the relative incident angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-$\Delta\theta$ represents the radial displacement of the reconstructed incident angle relative to the true incident direction.
+$\Delta\theta$ is calculated with the radial displacement of the reconstructed incident angle relative to the true incident direction.
 The central 98\% of the distribution is fitted with the Gaussian and generalized Gaussian (GG) functions~\cite{GGfun}.
-We tested two functions, Gaussian and GG, to describe the reconstructed angular distribution.
-The GG function, also known as the generalized error distribution, is expressed as:
+The GG function, also known as the generalized error distribution, describes the obtained distribution, which is expressed as =
 \begin{eqnarray} 
@@
 \centering
-\includegraphics[width=0.69\textwidth]{figures/Fig4_Opt.pdf}
-\caption{Angular resolutions are displayed in terms of combination of N\_estimators and Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
+\includegraphics[width=0.79\textwidth]{Fig4_include_ne250.pdf}
+\caption{Angular resolutions are displayed in terms of combination of \textit{N\_estimators} and \textit{Max.
+depth}.
+The best angular resolution is obtained with \textit{N\_estimators}~=~300 and \textit{Max.
+depth}~=~100.
+}
 \label{fig:par_scan}
@@
 
-Because the performance of the angle reconstruction of the XGB depends on the hyperparameters, we scanned the evaluated angular resolution by changing the hyperparameters.
-As there were correlations among the hyperparameters, the scanning process was performed in a five-dimensional space for all possible combinations.
-As an example, Figure 4 shows the test results for N\_estimators and Max.
-depth.
-N\_estimators defines the maximum allowed number of decision trees to be developed, and Max.
-depth defines the complexity of the decision-tree structure.
-We explored a hyperparameter combination that generated the best angular resolution.
-Consequently, the N\_estimators and Max.
-depth were set to 300 and 100, respectively.
-Similar scans were also performed for different hyperparameters, subsample, learning rates, and gamma.
-Subsample controls the fraction of total event samples for each boosting procedure, the learning rate weights a decision tree to be added onto the current model, and the gamma regulates the evaluation of each decision tree.
+Because the performance of the angle reconstruction of the XGB depends on the hyperparameters, we scan the angular resolution by changing them.
+As there are correlations among the hyperparameters, the scanning process is performed in a five-dimensional space for all possible combinations.
+As an example, Figure 4 shows the test results for \textit{N\_estimators} and \textit{Max.
+depth}.
+We explore a hyperparameter combination that generates the best angular resolution within the uncertainty of 0.01 deg.
+Consequently, the \textit{N\_estimators} and \textit{Max.
+depth} are set to 300 and 100, respectively.
+Similar scans are also performed for different hyperparameters, \textit{subsample}, \textit{learning rates}, and \textit{gamma}.
 Table~\ref{tab:XgbPar} lists the optimized set of hyperparameters that are used in further studies.
-During the optimization process, the fraction of the tail that is not well described by the GG function is approximately 2\%.
+During the optimization process, the fraction of the tail that is not well described by the GG function is approximately 2\% for different sets of hyperparameters.
 
@@
 \caption{Hyperparameters of the XGB model}
-\begin{tabular}{cccc}
+\begin{tabular}{llcc}
 \hline 
 Parameter & Function & Default value & Used value \\ \hline 
-N\_estimators & The number of decision trees & N.A. & 300 \\  
-Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
-Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
-Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
-Gamma & Requirement on minimum loss function & 0 & 0 \\ 
+\textit{N\_estimators} & The number of decision trees & N.A. & 300 \\  
+\textit{Max. depth} & Possible maximum depth of tree structure & 6 & 100 \\ 
+\textit{Subsample} & Fraction of total data used for a single decision & 1 & 0.8 \\ 
+\textit{Learning rate} & Step length for calculation & 0.3 & 0.02 \\ 
+\textit{Gamma} & Requirement on minimum loss function & 0 & 0 \\ 
 \hline
@@
 
+\subsection{Performance of angular reconstruction}
+\label{sec:perf}
+
 \begin{figure}[!hbt]
 \centering
-\includegraphics[width=0.58\textwidth]{figures/Fig5_width.pdf}
+\includegraphics[width=0.58\textwidth]{Fig5_width_including7.5_12.5mm.pdf}
 \caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
@@
 
-Angular resolutions were deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
+To inspect the angular resolution for the spatial resolution of measured EM showers,  %%%
+Angular resolutions are deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
 The narrower the strip width, the larger is the size of the features.
@@
 However, the wider strips hardly provide detailed information on the EM shower.
-The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$.
+The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$,
+and are selected for the further study considering limited budget for the actual construction of the detector.   %%%
 
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.48\textwidth]{figures/Fig6_layer_comp.pdf}
+\includegraphics[width=0.48\textwidth]{Fig6_layer_comp.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{ 
-\includegraphics[width=0.48\textwidth]{figures/Fig6_nlayer.pdf}
+\includegraphics[width=0.48\textwidth]{Fig6_nlayer.pdf}
 }
-\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$.
-The red histogram represents the polar angle distribution for $E_{\rm{tot}}>$~10~MeV.
-(b) Angular resolution as a function of the radiation length ($X_{0}$).}
+\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$  with the front 32 layers only.
+The red histogram represents the angular distribution after requiring $E_{\rm{tot}}>$~10~MeV for the front layers.
+(b) Angular resolution as a function of the radiation length ($X_{0}$) of the front layers.}
 \label{fig:angle_reco_layer}
@@
 
-Focusing only on the angle reconstruction, we designed the detector with the smallest number of layers.
-Figure~\ref{fig:angle_reco_layer} (a) shows the angles reconstructed using the front 32 layers of the detector, which correspond to 6.2$X_{0}$, for 1-GeV photons.
-A fraction of the photons fail to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be higher than 10~MeV, which is 1\% of the incident energy.
-The angular resolution of the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$ when 1.9\% of the photons fail to be reconstructed.
+To further study the feasibility for the detector to be a photon tracker, the reconstruction of the incident angle is conducted with the front layers instead of the full layers. %%
+Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2$X_{0}$.
+A fraction of the photons fail to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%.
+The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit at the front layers should be higher than 10~MeV, which is 1\% of the incident energy.
+The angular resolution of the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
+The evolution of angular resolution degrades with the reduction of the number of layers used as the number of contributors to the reconstruction decreases.
 
@@
 \stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
-\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_res_ene.pdf}
 }\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
-\includegraphics[width=0.44\textwidth]{figures/Fig7_Fit_eres_1.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_Fit_eres_1.pdf}
 }
 \caption{ (a) Angular resolution as a function of the incident angle for different incident energies.
-(b) Angular resolution as a function of the incident energy for $\theta=$~25$^{\circ}$; it is fitted to the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$ }
+(b) Angular resolution as a function of the incident energy for $\theta=$~25$^{\circ}$; it is fitted to the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$.
+All resolutions are estimated with the front 32 layers.
+}
 \label{fig:angle_reco_dep_gr}
@@
 Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of incident angle for different incident energies ($E_{\gamma}$).
+Note that the front 32 layers are used for the reconstruction of the incident angle.
+The inefficiency from the usage of the front layers is estimated to be 2\% at zero degree of incident angle and decreases as 0.5\% at 40 degrees of incident angle.
 The angular resolution does not depend on the incident angle for high incident energies.
@@
 Figure~\ref{fig:angle_reco_dep_gr} (b) shows the angular resolution as a function of the incident photon energy at $\theta=$~25$^{\circ}$.
-The angular resolution fits to the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$, where $p_{0}$ and $p_{1}$ represent the energy-independent and energy-dependent contributions, respectively.
+The angular resolution is well fitted by the function $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(\mathrm{GeV})}$, where $p_{0}$ and $p_{1}$ represent the energy-independent and energy-dependent contributions, respectively, added in quadrature.
 
@@
 \centering
-\includegraphics[width=0.44\textwidth]{figures/Fig7_p0.pdf}
-\includegraphics[width=0.44\textwidth]{figures/Fig7_p1.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_p0.pdf}
+\includegraphics[width=0.44\textwidth]{Fig7_p1.pdf}
 \caption{ $p_{0}$ and $p_{1}$ as a function of the incident angle }
@@
 The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
-For a small $\theta$, $p_{1}$ is smaller than that for a larger $\theta$ because the angular resolution is largely dependent on the incident angle for low incident energies, whereas the opposite trend can be observed for $p_{0}$.
+In case of $\theta$ smaller than 10 degrees, the angular resolution shows different dependency on the incident energy, which results in smaller $p_{1}$ and larger $p_{0}$ compared to the larger angles.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/Fig8_nsample.pdf}
+\includegraphics[width=0.6\textwidth]{Fig8_nsample_400k_500k.pdf}
 \caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers.
+The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.
 }
@@
 Figure~\ref{fig:multi-parameter} shows the angular resolution for different numbers of training samples and different detector configurations.
-All configurations show improvement in the angular resolution with increasing training samples, which indicates that the maturity of machine learning is an important factor in angle reconstruction.
-With an increase in the number of training events, the Angular resolution improves most rapidly for the configuration with 5-mm-wide scintillator strips.
-In other words, the required training events must be sufficiently large to correlate a larger number of features.
-Considering the limited computing resources, the configuration of 32 layers and 15-mm-wide strip with $10^{5}$ training events was chosen to train the XGB model.
-The training result for such a configuration differs by only 0.2$^{\circ}$ from that of the setup with full layers, 5-mm-wide strips, and $5\times10^{5}$ training events.
+The width of curves represents the statistical uncertainty.
+All configurations show improvement in the angular resolution with the increasing number of training samples, which indicates that the maturity of machine learning is an important factor in angle reconstruction.
+With an increase in the number of training events, the angular resolution improves most rapidly for the configuration with 5-mm-wide scintillator strips.
+In other words, the required number of training events should be large enough to provide correct answer from the correlations
+between many features.
+The spectra are fitted with the empirical function of $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ are describing the decreasing trend.
+The numbers of training samples reaching the angular resolution of 1.1 times of $I$ for 25, 15, and 5 mm strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.
 
@@
 
-We report the simulation results of the incident angle reconstruction of EM sampling calorimeters with photons in the range of 0.1 to 2~GeV.
-~To improve the angular resolution, we tuned the hyperparameters of XGBoost while considering the correlating effects among them.
-
-In terms of detector configuration, strips with narrower widths provide better angular resolution using a finely measured EM shower with the assumption that the training is fully conducted.
-However, the configuration with a smaller strip width causes a larger feature size, which negatively affects the training depending on the quantity of training data.
+We report on the optimization of the angle reconstruction of a a toy Lead/Plastic EM sampling calorimeter for photons in the range of 0.1 to 2~GeV, using the machine learning technique for the next KOTO experiment.
+The hyperparameters of the XGBoost have been tuned to obtain the best angular resolution, in which the correlating effects among them need to be considered.
+In terms of the detector configuration, strips with narrower width provide better angular resolution with detailed information on the EM shower when the training on the data is fully conducted.
+However, the configuration with a smaller strip width requires the larger number of channels to have the same coverage, and this negatively affects to train the model.
+training with respect to the quantity of training data.
 The angular resolution may be optimized by considering the two competing effects of the strip width and quantity of training data.
-We dedicated the front layers of the detector to reconstructing the incident angle.
-We obtain an angular resolution of 1.30~$\pm$~0.01$^{\circ}$ for the configuration of 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which is a reduction of 0.1$^{\circ}$ compared to that of the configuration with full layers (20$X_{0}$) in the case of $10^{5}$ training samples.
-
+Focusing on the angle measurement with a compact detector, we can obtain an angular resolution of 1.30~$\pm$~0.01$^{\circ}$ for the configuration of 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which is a reduction of 0.1$^{\circ}$ compared to that of the configuration with full layers (20$X_{0}$) with $10^{5}$ training samples.
 The angular resolution depends on the incident energy of the photon, and the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
-Except for small incident angles ($\theta<$~$^{\circ}$~deg), the two parameters do not significantly change up to
-$40^{\circ}$, and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
+Except for small incident angles ($\theta<$~$^{\circ}$~deg), the two parameters do not significantly change up to $40^{\circ}$, and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
 
@@
 
+\bibitem{unitext}
+M. Livan and R. Wigmans, Calorimetry for collider physics, an Introduction, DOI: https://doi.org/10.1007/978-3-030-23653-3
+
+\bibitem{CMS:mat}
+CMS Collaboration, JINST 2010 JINST 5 T03012
+
+\bibitem{CDF:mat}
+CDF Collaboration, Nucl. Instrum. Meth. A 267 (1988) 272-279
+
+\bibitem{DELPHI:mat}
+DELPHI Collaboration, Nucl. Instrum. Meth. A 305 (1991) 320-330
+
+\bibitem{UGAS:mat}
+Yu. Galaktionov {\it et al.}, Nucl. Instrum. Meth. A 251 (1986) 258-274
+
+\bibitem{LiqAR:mat}
+ATLAS Collaboration, Eur. Phys. J. C (2010) 70: 723–753
+
+\bibitem{shashlik:con}
+A.C. Benvenuti {\it et al.}, Nucl. Instrum. Meth. A 432 (1999) 232-239
+
 \bibitem{KOTO:MB}
-Y. Tajima {\it et al.}, Nucl. Instrum. Meth. A 592, 261 (2008).
+Y. Tajima {\it et al.}, Nucl. Instrum. Meth. A {\bf 592}, 261 (2008).
 
-\bibitem{CMS:EMCAL}
-Giovanni Mazza {\it et al.} (CMS Collaboration), Nucl. Instrum. Meth. A 958 (2020)
+\bibitem{KLOE:con}
+DA$\phi$NE Collaboration, Nucl. Instrum. Meth. A 482 (2002) 364–386
 
-\bibitem{BELLE:EMCAL}
-K. Miyabayashi {\it et al.}, JINST 9 (2014) 09, P09011
+\bibitem{FERMI:LAT}
+W. B. Atwood {\it et al.}, Astrophys J.697 (2009) 1071-1102
 
-\bibitem{Murayama:2020mcp}
-R. Murayama {\it et al.}, Nucl. Instrum. Meth. A 953 (2020)
+\bibitem{CALET}
+N. Cannady {\it et al.}, Astrophys. J. ,Suppl. Ser. 238:5 (2018)
 
-\bibitem{trk:ref}
-O. Adriani {\it et al.}, Nucl. Instrum. Meth. A 854 (2017)
+\bibitem{DMPE}
+J. Chang {\it et al.}, Astropart. Phys. 95 (2017) 6-24
+
+\bibitem{KOTOexp}
+KOTO Collaboration, Phys. Rev. Lett. 126, 121801 (2021)
+
+\bibitem{KOTObeam}
+T. Shimogawa, Nucl. Instrum. Meth. A {\bf 623} (2010) 585-587
+
+\bibitem{KOTOtheory}
+Andrzej J. Buras {\it et al.}, JHEP 11 (2015) 033
+
+\bibitem{KOTO2}
+TF on the extension of the Hadron Experimental Facility, arXiv:2110.04462
+
+\bibitem{KOPIO}
+I.-H. Chiang {\it et al.}, AGS Experimental Proposal 926 (1996).
+
+\bibitem{KOPIOcdr}
+KOPIO Collaboration, Conceptual Design Report (2005)
 
@@
 (2016) 785.
+
+\bibitem{mle}
+DAMPE Collaboration, JINST 17 (2022) 06, P06031
+
+\bibitem{mlp}
+ALICE Collaboration, JINST 17 (2022) 07, C07016
+
+\bibitem{mlt}
+PADME Collaboration, Instruments 6 (2022) 46
 
@@
 
+\bibitem{PbScint}
+Zu-Hao Li {\it et al.}, Chin. Phys. C 38 (2014) 5, 056203
+
 \end{thebibliography}
 
-%\section*{Acknowledgement}
-%This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and \\ 2020R1A3B2079993).
-
-%\bibliographystyle{elsarticle-num}
-%\bibliography{paper.bib}
-
-%\printbibliography
-
 \end{document}

### 2023-01-16 paper.tex
updates

@@
 This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250~MeV~\cite{KOPIOcdr}.
-Unfortunately, the proposal was not accepted, and the detector development could not continue.
 
@@
 There is a limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation.
-A deduction of the incident angle of the EM shower using a lead scintillating fiber sandwiched sampling calorimeter is studied~\cite{PbScint}, and the obtained angular resolution is 0.8 degrees for 100-GeV electrons and expected to be larger than 8 degrees for 1-GeV electrons.
+A deduction of the incident angle of the EM shower using a lead scintillating fiber sandwiched sampling calorimeter is studied~\cite{PbScint}, and the angular resolution is expected to be larger than 8 degrees for 1-GeV electrons.
 We take a machine-learning approach to get better angular resolution from the analysis.
@@
 \end{figure}
-
+\subsubsection{strip width}
 To inspect the angular resolution for the spatial resolution of measured EM showers,  %%%
@@
 
+\subsubsection{the number of layers}
 To further study the feasibility for the detector to be a photon tracker, the reconstruction of the incident angle is conducted with the front layers instead of the full layers. %%
@@
 
+\subsubsection{incident energy}
 Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of incident angle for different incident energies ($E_{\gamma}$).
@@
 
+\subsubsection{training sample}
 Figure~\ref{fig:multi-parameter} shows the angular resolution for different numbers of training samples and different detector configurations.
@@
 
-We report on the optimization of the angle reconstruction of a a toy Lead/Plastic EM sampling calorimeter for photons in the range of 0.1 to 2~GeV, using the machine learning technique for the next KOTO experiment.
+We report on the optimization of the angle reconstruction of a a toy Lead/Plastic EM sampling calorimeter for photons in the range of 0.1 to 2~GeV, using the machine learning technique for the background rejection in the next KOTO experiment.
 The hyperparameters of the XGBoost have been tuned to obtain the best angular resolution, in which the correlating effects among them need to be considered.

### 2023-01-25 paper.tex
updates

@@
 \begin{abstract}
-We report on the simulation results for angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
+We report on the simulation results for the angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
 The simulation model of the EM calorimeter consists of alternating layers of an 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate.
 The scintillator plates are alternately segmented into horizontal and vertical strips.
-In this study, we obtained energy deposits in individual strips using Geant4 simulations and reconstructed the incident photon angles using XGBoost with gradient-boosted decision trees.
+In this study, we obtain energy deposits in individual strips using Geant4 simulations and reconstruct the incident photon angles using XGBoost with gradient-boosted decision trees.
 The performance of the angle reconstruction depends on both the detector configuration and accuracy of machine learning.
-The angular resolution so obtained can be expressed as $0.24 \oplus 1.24/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
+The angular resolution so obtained can be expressed as $0.24 \oplus 1.25/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
 This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.
@@
 
-Calorimeter plays an important role in the experimental studies of nuclear and particle physics~\cite{unitext}.
-An ideal calorimeter fully absorbs the energy of the entering particle and converts the energy into measurable quantities.
-The sampling calorimeter consists of different materials, one is the absorber generating a shower of secondary particles, and the other is an active medium that generates signals from the energy deposits of the secondaries.
-Because the energy deposit in the active medium fluctuates associated with the dense absorber, the sampling calorimeter has an inevitable drawback in energy resolution, especially in the measurement of gamma.
-This effect can be controlled by adjusting the material budget between the absorber and active medium and their configuration.
-Also, it becomes less critical as gamma energy becomes higher.
+Calorimeter plays a crucial role in the experimental studies of nuclear and particle physics~\cite{unitext}.
+An ideal calorimeter fully absorbs the energy of an entering particle and converts the energy into measurable quantities.
+The sampling calorimeter consists of alternating layers of two different materials, one is an absorber generating a shower of secondary particles, and the other is an active medium that generates signals from the energy deposits of the secondaries.
+Because the energy deposit in the active medium fluctuates with respect to the energy loss in the dense absorber, the sampling calorimeter has an inevitable drawback in energy resolution, especially in the gamma measurement.
+However, the energy resolution can be improved by optimizing the alternating layer configuration.
+In addition, it becomes less critical as gamma energy becomes higher.
 
 In general, the sampling calorimeter enables cost-effective fabrication of large-scale detectors and design of flexible geometric configuration.
-This detector has been developed in various ways by selecting a material of absorber among many caodidates such as brass~\cite{CMS:mat}, lead~\cite{CDF:mat}, tungsten~\cite{DELPHI:mat}, uranium~\cite{UGAS:mat}, and also of active medium such as scintillators~\cite{CMS:mat,CDF:mat}, gas~\cite{UGAS:mat}, solid-state detector~\cite{DELPHI:mat}, and liquid gas~\cite{LiqAR:mat}.
+This detector has been developed in various ways by selecting a material of absorber among many candidates such as brass~\cite{CMS:mat}, lead~\cite{CDF:mat}, tungsten~\cite{DELPHI:mat}, uranium~\cite{UGAS:mat}, and also of active medium such as scintillators~\cite{CMS:mat,CDF:mat}, gas~\cite{UGAS:mat}, solid-state detector~\cite{DELPHI:mat}, and liquid gas~\cite{LiqAR:mat}.
 Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}.
@@
 The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils.
-Tracking with the silicon detectors on the electron-positron pairs produced at the foils provides an angular resolution of 0.6 degrees for 1-GeV photons and better than 0.16 degrees for energy higher than 10~GeV~\cite{FERMI:LAT}.
-The LAT has two additional components: a scintillating plastic for the charged-particle detection and a homogeneous CsI crystals for energy measurement.
+Tracking with the silicon detectors on the electron-positron pairs produced at the foils provides an angular resolution of 0.6 degrees for 1-GeV photons and better than 0.16 degrees for photons with energies higher than 10~GeV~\cite{FERMI:LAT}.
+The LAT has two additional components: a plastic scintillator for the charged-particle detection and a homogeneous CsI crystals for the energy measurement.
 This triple detector configuration is also used in different missions.
 An energy spectrum measurement of cosmic-ray electrons (CALET)~\cite{CALET} utilizes scintillating fibers and PWO crystals instead of the silicon strips and the CsI crystals, respectively.
-A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for energy measurement.
-The angular resolution of the detector is obtained as 1--2 degrees for 1-GeV photons.
+A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for the energy measurement.
+The DMPE provides the angular resolution of 1--2 degrees for 1-GeV photons.
 
-In the accelerator-based experiments, the direction of photons can be precisely obtained by connecting the interaction position obtained from charged particle tracks to their incident position measured at the calorimeter.
-However, it is not possible to reconstruct the interaction (decay) position when we observe $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay, in which no charged particle exists.
-The decay is explained with a CP-violating Flavor Changing Neutral Current process and has significant potential to provide clues to new physics beyond the Standard Model (SM).
+In the accelerator-based experiments, the direction of photons can be precisely determined by connecting the interaction position obtained from charged particle tracks to their incident position measured using the calorimeter.
+However, when observing $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay in the absence of charged particles, it is impossible to reconstruct the interaction (decay) position.
+The decay occurs through the CP-violating Flavor Changing Neutral Current and has significant potential to provide clues to new physics beyond the Standard Model (SM).
 Its branching fraction is calculated to be extremely small as 3~$\times$~10$^{-11}$ in the SM~\cite{KOTOtheory}, which implies that the effect of new physics on the decay could overwhelm that of the SM.
@@
 A Preradiator (PR) is placed in front of the calorimeter to measure the photon's incident angle.
-The PR consists of a close-packed multi-layer sandwich of 8-mm-thick scintillating plastics alternating with the single-plane and this-gap drift chambers with cathode strips.
-For good energy resolution and high detection efficiency against a few hundred MeV photons, the scintillating plastic is used for electron-positron conversion.
-This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250~MeV~\cite{KOPIOcdr}.
+The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and this-gap drift chambers with cathode strips.
+For good energy resolution and high detection efficiency against a few hundred MeV photons, the plastic scintillator is used for electron-positron conversion.
+This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250-MeV~photons~\cite{KOPIOcdr}.
 
-On the other hand, the KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with a well-collimated small-size neutral beam, which constrains the transverse decay position to be at the beam axis.
-With this assumption, the distance between the decay position and the calorimeter is calculated from the positions and energies of the two photons, and the transverse momentum of $\pi^{0}$ is obtained.
-The two variables, the longitudinal decay position and the transverse momentum, are used to define a signal region of the decay.
-The KOTO experiment started data taking in 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
-The data taking will continue for  several more years, and the sensitivity will reach 10$^{-11}$.
-It is still not enough to determine the branching fraction if it is close to the SM expectations.
+On the other hand, the KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with a well-collimated small-size neutral beam, which provides a condition that the $\pi^{0}$ decays at the beam axis.
+With this assumption, the decay vertex is calculated using the positions and energies of the two photons measured in the calorimeter.
+The transverse momentum of $\pi^{0}$ is calculated from the vertex.
+The two variables, the decay vertex and the transverse momentum are used to define a signal region of the decay.
+The KOTO experiment started data taking since 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
+The data taking will continue for a few more years, and the sensitivity will reach 10$^{-11}$.
 
 A successive experiment of the KOTO is under preparation to observe more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}.
-In this higher-sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$.
+In this highly sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$.
 In addition, the neutrons away from the beam axis produce a $\pi^{0}$ or $\eta$ by interacting with detector materials.
@@
 
-In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and scintillating plastic layers.
+In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and plastic scintillator layers.
 There is a limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation.
@@
 
-The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick Pb absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
@@
 To test the reconstruction of the incident angles, photons are generated at a fixed incident angle $\theta$ with known incident energy and incident position.
-Possible noise effects are not simulated in this paper. Instead, application of lower threshold of 0.5~MeV for each strip is tested and found to provide the consistent result without threshold. %%%
+We do not take into account any arbitrary noises that would affect the angle reconstruction.
+Instead, the angle reconstruction is tested with a lower threshold of 0.5~MeV for each strip, and the angular resolution does not change.
+
 \section{Results}
@@
 
-The incident angles of the photons are reconstructed using XGBoost~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
+The incident angle of the photons is reconstructed using XGBoost~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
+The feature size identical to the number of strips varies with the strip width to have the same coverage.
+In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector.
 XGBoost constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function.
-The size of feature, which is identical with the number of strips, varies with the strip width to have the same coverage.
-In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector.
-Hyperparameters of XGBoost drive how models are trained.
-Main five parameters are studied in this paper.
-\textit{N\_estimators} defines the maximum allowed number of decision trees to be developed, and  \textit{Max.
+The hyperparameter of XGBoost is the parameter driving how models are trained.
+In this paper, main five parameters are studied.
+\textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max.
 depth} defines the complexity of the decision-tree structure.
@@
 Figure~\ref{fig:angle_10degree} represents the distribution of the relative incident angle ($\Delta\theta$) for 1-GeV photons generated at $\theta=$~10$^{\circ}$.
-$\Delta\theta$ is calculated with the radial displacement of the reconstructed incident angle relative to the true incident direction.
+The $\Delta\theta$ is calculated with the radial displacement of the reconstructed incident angle relative to the true incident direction.
 The central 98\% of the distribution is fitted with the Gaussian and generalized Gaussian (GG) functions~\cite{GGfun}.
-The GG function, also known as the generalized error distribution, describes the obtained distribution, which is expressed as =
+The GG function, also known as the generalized error distribution, shows better agreement with the obtained distribution, which is expressed as
+
 \begin{eqnarray} 
@@
 The parameters $\alpha$ and $\beta$ determine the scale and shape of the distribution, respectively.
-The variance in the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$.
-The angular resolution of the incident angle reconstruction is defined as $\sigma$.
+The variance in the GG function is given by $\sigma^2 \equiv \alpha^2 \Gamma(3/\beta) / \Gamma(1/\beta)$ and the angular resolution is defined as $\sigma$.
+%The angular resolution of the incident angle reconstruction is defined as $\sigma$.
 
@@
 Because the performance of the angle reconstruction of the XGB depends on the hyperparameters, we scan the angular resolution by changing them.
-As there are correlations among the hyperparameters, the scanning process is performed in a five-dimensional space for all possible combinations.
-As an example, Figure 4 shows the test results for \textit{N\_estimators} and \textit{Max.
+Since there are correlations among the hyperparameters, the scanning process is performed in a five-dimensional space for all possible combinations.
+As an example, Figure~\ref{fig:par_scan} shows the test results for \textit{N\_estimators} and \textit{Max.
 depth}.
-We explore a hyperparameter combination that generates the best angular resolution within the uncertainty of 0.01 deg.
+We explore a hyperparameter combination that generates the best angular resolution within the uncertainty of 0.01~deg.
 Consequently, the \textit{N\_estimators} and \textit{Max.
 depth} are set to 300 and 100, respectively.
-Similar scans are also performed for different hyperparameters, \textit{subsample}, \textit{learning rates}, and \textit{gamma}.
+Similar processes are also performed for different hyperparameters, \textit{subsample}, \textit{learning rates}, and \textit{gamma}.
 Table~\ref{tab:XgbPar} lists the optimized set of hyperparameters that are used in further studies.
@@
 \end{figure}
-\subsubsection{strip width}
-To inspect the angular resolution for the spatial resolution of measured EM showers,  %%%
-Angular resolutions are deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
-The narrower the strip width, the larger is the size of the features.
-Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than 5-mm-wide strips.
+\subsubsection{Strip width}
+To inspect how much the angular resolution is affected by the spatial resolution of measured EM showers, Angular resolutions are deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
+The narrower the strip width, the larger the feature size.
+Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than with 5-mm-wide strips.
 However, the wider strips hardly provide detailed information on the EM shower.
-The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$,
-and are selected for the further study considering limited budget for the actual construction of the detector.   %%%
+The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$ and are selected for further study considering the actual construction of a prototype detector.
 
@@
 }
-\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$  with the front 32 layers only.
+\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$  with the front 32 layers of 15-mm-wide strips.
 The red histogram represents the angular distribution after requiring $E_{\rm{tot}}>$~10~MeV for the front layers.
-(b) Angular resolution as a function of the radiation length ($X_{0}$) of the front layers.}
+(b) Angular resolution as a function of the radiation length ($X_{0}$) with the front layers.
+The red line corresponds to the results using entire layers of 105.}
 \label{fig:angle_reco_layer}
@@
 
-\subsubsection{the number of layers}
-To further study the feasibility for the detector to be a photon tracker, the reconstruction of the incident angle is conducted with the front layers instead of the full layers. %%
+\subsubsection{Number of layers}
+To further study the feasibility for the detector to be a photon tracker, the reconstruction of the incident angle is performed with the front layers instead of the full layers.
 Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2$X_{0}$.
-A fraction of the photons fail to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%.
-The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit at the front layers should be higher than 10~MeV, which is 1\% of the incident energy.
-The angular resolution of the front layer is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
+A fraction of the photons fails to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%.
+The failed events are represented as a delta function near 0.
+Such events are removed by requiring the total energy deposit at the front layers to be higher than 10~MeV, which is 1\% of the incident energy.
+The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
 The evolution of angular resolution degrades with the reduction of the number of layers used as the number of contributors to the reconstruction decreases.
@@
 
-\subsubsection{incident energy}
+\subsubsection{Incident energy}
 Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of incident angle for different incident energies ($E_{\gamma}$).
-Note that the front 32 layers are used for the reconstruction of the incident angle.
-The inefficiency from the usage of the front layers is estimated to be 2\% at zero degree of incident angle and decreases as 0.5\% at 40 degrees of incident angle.
+Note that the front 32 layers are used for the angle reconstruction.
+Since the effective radiation length is different according to the incident angles, the inefficiency of the reconstruction is changed from 2\% at zero degrees to 0.5\% at 40 degrees.
 The angular resolution does not depend on the incident angle for high incident energies.
@@
 Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ as a function of the incident angle.
-The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.24$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
-In case of $\theta$ smaller than 10 degrees, the angular resolution shows different dependency on the incident energy, which results in smaller $p_{1}$ and larger $p_{0}$ compared to the larger angles.
+The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.25$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
+In the case of $\theta$ smaller than 10 degrees, the angular resolution shows different dependency on the incident energy, which results in smaller $p_{1}$ and larger $p_{0}$ compared to the larger angles.
 
@@
 
-\subsubsection{training sample}
-Figure~\ref{fig:multi-parameter} shows the angular resolution for different numbers of training samples and different detector configurations.
-The width of curves represents the statistical uncertainty.
-All configurations show improvement in the angular resolution with the increasing number of training samples, which indicates that the maturity of machine learning is an important factor in angle reconstruction.
+\subsubsection{Training sample}
+Figure~\ref{fig:multi-parameter} shows the angular resolution for different numbers of training samples and detector configurations.
+The width of each curve represents the statistical uncertainty.
+All configurations show improvement in the angular resolution with the increasing number of training samples, which indicates that the maturity of machine learning is an important factor in the angle reconstruction.
 With an increase in the number of training events, the angular resolution improves most rapidly for the configuration with 5-mm-wide scintillator strips.
-In other words, the required number of training events should be large enough to provide correct answer from the correlations
-between many features.
-The spectra are fitted with the empirical function of $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ are describing the decreasing trend.
-The numbers of training samples reaching the angular resolution of 1.1 times of $I$ for 25, 15, and 5 mm strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.
+In other words, the required number of training events should be large enough to provide correct answer from the correlations between many features.
+
+The spectra are fitted with the empirical function of $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ describe the decreasing trend.
+The numbers of training samples reaching the angular resolution of 1.1$I$ with 25-, 15-, and 5-mm-wide strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.
 
@@
 
-We report on the optimization of the angle reconstruction of a a toy Lead/Plastic EM sampling calorimeter for photons in the range of 0.1 to 2~GeV, using the machine learning technique for the background rejection in the next KOTO experiment.
-The hyperparameters of the XGBoost have been tuned to obtain the best angular resolution, in which the correlating effects among them need to be considered.
-In terms of the detector configuration, strips with narrower width provide better angular resolution with detailed information on the EM shower when the training on the data is fully conducted.
-However, the configuration with a smaller strip width requires the larger number of channels to have the same coverage, and this negatively affects to train the model.
-training with respect to the quantity of training data.
-The angular resolution may be optimized by considering the two competing effects of the strip width and quantity of training data.
-Focusing on the angle measurement with a compact detector, we can obtain an angular resolution of 1.30~$\pm$~0.01$^{\circ}$ for the configuration of 32 layers (6.2$X_{0}$) of 15-mm-wide strips, which is a reduction of 0.1$^{\circ}$ compared to that of the configuration with full layers (20$X_{0}$) with $10^{5}$ training samples.
-The angular resolution depends on the incident energy of the photon, and the dependence is expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
-Except for small incident angles ($\theta<$~$^{\circ}$~deg), the two parameters do not significantly change up to $40^{\circ}$, and the dependence is estimated to be 0.24 $\oplus$ 1.24$^{\circ}/\sqrt{E_{\gamma}}$.
+A sampling calorimeter for the incident angle measurement of photons will play an essential role in the next stage of the KOTO experiment, which can distinguish $\pi^0$ decays at the off- from in-beam axis.
+The machine-learning approach (XGboost) analyzing the energy-weighted shower shapes enables us to proceed with detailed optimization of the detector to fulfill the experimental goal.
+The angular resolution depends on the values of hyperparameters of the XGboost decided by the user.
+
+The width of strips to record the energy deposit of shower particles is an essential parameter of the angular resolution, which should be compromised between the required angular resolution and construction costs related to the number of read-out channels.
+In addition, the angular resolution is also determined by the training accuracy of the XGBoost, which requires a different number of training data according to the detector configuration.
+When we test a detector configuration with many channels (i.e., narrow strip), we should also prepare a large number of data for the training.
+
+For the toy sampling calorimeter with 15-mm-wide strips and 32 layers, the angular resolution was obtained as 1.30~$\pm$~0.01$^{\circ}$ in machine learning with $10^{5}$ training samples.
+Energy dependence of the angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
+For the angular range of $10^{\circ}<\theta<40^{\circ}$, the  $p_{0}$ and $p_{1}$ values remain unchanged as $p_{0}$ = 0.238$^{\circ}$ $\pm$ 0.012$^{\circ}$ and $p_{1}$ = 1.248$^{\circ}$ $\pm$ 0.002$^{\circ}$, respectively.
 

### 2023-01-26 paper.tex
uodates

@@
 We report on the simulation results for the angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV.
-The simulation model of the EM calorimeter consists of alternating layers of an 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate.
+The simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate.
 The scintillator plates are alternately segmented into horizontal and vertical strips.
 In this study, we obtain energy deposits in individual strips using Geant4 simulations and reconstruct the incident photon angles using XGBoost with gradient-boosted decision trees.
-The performance of the angle reconstruction depends on both the detector configuration and accuracy of machine learning.
-The angular resolution so obtained can be expressed as $0.24 \oplus 1.25/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
+The performance of the angle reconstruction depends on the detector configuration and the accuracy of machine learning.
+The angular resolution is well described by the expression $0.24^{\circ} \oplus 1.25^{\circ}/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
 This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.
@@
 A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for the energy measurement.
-The DMPE provides the angular resolution of 1--2 degrees for 1-GeV photons.
+Theses detectors provide the angular resolution of 1-2 degrees for 1-GeV photons.
 
@@
 A Preradiator (PR) is placed in front of the calorimeter to measure the photon's incident angle.
-The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and this-gap drift chambers with cathode strips.
+The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and thin-gap drift chambers with cathode strips.
 For good energy resolution and high detection efficiency against a few hundred MeV photons, the plastic scintillator is used for electron-positron conversion.
@@
 The KOTO experiment started data taking since 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
-The data taking will continue for a few more years, and the sensitivity will reach 10$^{-11}$.
+The data taking will continue for a few more years, and the sensitivity will be expected to reach $\mathcal{O}$(10$^{-11}$).
 
@@
 Each plate is segmented in 35 strips, oriented alternately in horizontal and vertical directions.
-See text for details.
 }
@@
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
-It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain photons showers for energies in the range of 0.1 to 2~GeV.
+It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM showers for energies in the range of 0.1 to 2~GeV.
 
@@
 The number of training samples is $10^{5}$ considering the limited computing resources.
-To test the reconstruction of the incident angles, photons are generated at a fixed incident angle $\theta$ with known incident energy and incident position.
-We do not take into account any arbitrary noises that would affect the angle reconstruction.
-Instead, the angle reconstruction is tested with a lower threshold of 0.5~MeV for each strip, and the angular resolution does not change.
+The angle reconstruction is studied using photons generated at given incident $\theta$ angle, energy, and position.
+It turns out unchanged with the energy deposit threshold above the noise level of 0.5 MeV.
+Therefore, we do not consider random noises in this study.
 
@@
 
-The incident angle of the photons is reconstructed using XGBoost~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
+The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
 The feature size identical to the number of strips varies with the strip width to have the same coverage.
 In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector.
-XGBoost constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function.
-The hyperparameter of XGBoost is the parameter driving how models are trained.
+XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function.
+The hyperparameter of XGB is the parameter driving how models are trained.
 In this paper, main five parameters are studied.
@@
 \includegraphics[width=0.79\textwidth]{Fig4_include_ne250.pdf}
-\caption{Angular resolutions are displayed in terms of combination of \textit{N\_estimators} and \textit{Max.
-depth}.
-The best angular resolution is obtained with \textit{N\_estimators}~=~300 and \textit{Max.
-depth}~=~100.
-}
+\caption{Angular resolutions are displayed in terms of combination of \textit{N\_estimators} and \textit{Max. depth}. The uncertainty for each value is 0.01~deg. }
 \label{fig:par_scan}
@@
 depth}.
-We explore a hyperparameter combination that generates the best angular resolution within the uncertainty of 0.01~deg.
-Consequently, the \textit{N\_estimators} and \textit{Max.
+The angular resolution improves when both \textit{Max.
+depth} and \textit{N\_estimators} increase.
+Since the uncertainty of the obtained angular resolution is estimated to be 0.01 degrees, many candidates for the hyperparameter set exist.
+Considering the CPU time for the training, the \textit{N\_estimators} and \textit{Max.
 depth} are set to 300 and 100, respectively.
@@
 Table~\ref{tab:XgbPar} lists the optimized set of hyperparameters that are used in further studies.
-During the optimization process, the fraction of the tail that is not well described by the GG function is approximately 2\% for different sets of hyperparameters.
+During the optimization process, the fraction of the tail that is not well described by the GG function is approximately 2\%, and the fraction does not change for different sets of hyperparameters.
 
@@
 \subsubsection{Strip width}
-To inspect how much the angular resolution is affected by the spatial resolution of measured EM showers, Angular resolutions are deduced by varying the strip width from 5 to 35 mm, as shown in Figure~\ref{fig:angle_reco_width}.
+To inspect the dependency of the angular resolution on the strip width, we deduce the angular resolution by varying the strip width from 5 to 35mm, as shown in Figure~\ref{fig:angle_reco_width}.
 The narrower the strip width, the larger the feature size.
@@
 However, the wider strips hardly provide detailed information on the EM shower.
-The 15-mm-wide strips yield a good angular resolution of 1.23~$\pm$~0.01$^{\circ}$ and are selected for further study considering the actual construction of a prototype detector.
+The 15-mm-wide strips yield a good angular resolution of 1.24~$\pm$~0.01$^{\circ}$ and are selected for further study considering the actual construction of a prototype detector, although 10-mm-wide strips provide the best resolution.
 
@@
 \subsubsection{Number of layers}
-To further study the feasibility for the detector to be a photon tracker, the reconstruction of the incident angle is performed with the front layers instead of the full layers.
+We study the dependency of the angle reconstruction on the number of front layers.
 Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2$X_{0}$.
@@
 The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
-The evolution of angular resolution degrades with the reduction of the number of layers used as the number of contributors to the reconstruction decreases.
+The evolution of angular resolution degrades with the reduction of the number of layers used.
 
@@
 Figure~\ref{fig:res_edep} shows the estimated $p_{0}$ and $p_{1}$ as a function of the incident angle.
-The average values of $p_{0}$ and $p_{1}$ are estimated to be 0.24$^{\circ}$ and 1.25$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
+The averages of $p_{0}$ and $p_{1}$ are estimated to be 0.238 $\pm$ 0.012$^{\circ}$ and 1.248 $\pm$ 0.002$^{\circ}$, respectively, for $\theta>$~10$^{\circ}$.
 In the case of $\theta$ smaller than 10 degrees, the angular resolution shows different dependency on the incident energy, which results in smaller $p_{1}$ and larger $p_{0}$ compared to the larger angles.
@@
 The width of each curve represents the statistical uncertainty.
-All configurations show improvement in the angular resolution with the increasing number of training samples, which indicates that the maturity of machine learning is an important factor in the angle reconstruction.
+All configurations show improvement in the angular resolution with the increasing number of training samples.
 With an increase in the number of training events, the angular resolution improves most rapidly for the configuration with 5-mm-wide scintillator strips.
@@
 A sampling calorimeter for the incident angle measurement of photons will play an essential role in the next stage of the KOTO experiment, which can distinguish $\pi^0$ decays at the off- from in-beam axis.
-The machine-learning approach (XGboost) analyzing the energy-weighted shower shapes enables us to proceed with detailed optimization of the detector to fulfill the experimental goal.
-The angular resolution depends on the values of hyperparameters of the XGboost decided by the user.
+The machine-learning approach (XGBoost) analyzing the energy-weighted shower shapes enables us to proceed with detailed optimization of the detector to fulfill the experimental goal.
+The angular resolution depends on the values of hyperparameters of the XGBoost decided by the user.
 
@@
 Energy dependence of the angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.
-For the angular range of $10^{\circ}<\theta<40^{\circ}$, the  $p_{0}$ and $p_{1}$ values remain unchanged as $p_{0}$ = 0.238$^{\circ}$ $\pm$ 0.012$^{\circ}$ and $p_{1}$ = 1.248$^{\circ}$ $\pm$ 0.002$^{\circ}$, respectively.
+For the angular range of $10^{\circ}<\theta<40^{\circ}$, the $p_{0}$ and $p_{1}$ remain unchanged as $p_{0}$ = 0.238 $\pm$ 0.012$^{\circ}$ and $p_{1}$ = 1.248 $\pm$ 0.002$^{\circ}$, respectively.
 

### 2023-01-26 paper.tex
updates

@@
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
-It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM showers for energies in the range of 0.1 to 2~GeV.
+It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.
 
@@
 XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function.
-The hyperparameter of XGB is the parameter driving how models are trained.
+The hyperparameters of XGB drive how models are trained.
 In this paper, main five parameters are studied.

### 2023-03-03 paper.tex
updates

@@
 The performance of the angle reconstruction depends on the detector configuration and the accuracy of machine learning.
-The angular resolution is well described by the expression $0.24^{\circ} \oplus 1.25^{\circ}/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers.
+The angular resolution is well described by the expression $0.24^{\circ} \oplus 1.25^{\circ}/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for 32 layers of 15~mm width strips.
 This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.
@@
 Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}.
-
-The sampling calorietmer has been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics.
+Sampling calorimeters have been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics.
+The PAMELA experiment employs a strip multilayer electromagnetic calorimeter of 22 ($x$,$y$) layers of silicon strip detectors interleaved with 22 tungsten plates, which identifies the particle types and measures the deposited energy, and helps to determine the detection of the particles~\cite{PAMELA}.
 The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils.
@@
 The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and thin-gap drift chambers with cathode strips.
-For good energy resolution and high detection efficiency against a few hundred MeV photons, the plastic scintillator is used for electron-positron conversion.
 This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250-MeV~photons~\cite{KOPIOcdr}.
 
-On the other hand, the KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with a well-collimated small-size neutral beam, which provides a condition that the $\pi^{0}$ decays at the beam axis.
+The KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with the help of a well-collimated and small-size neutral beam, constraining the $\pi^{0}$ decays along the beam axis.
 With this assumption, the decay vertex is calculated using the positions and energies of the two photons measured in the calorimeter.
@@
 The two variables, the decay vertex and the transverse momentum are used to define a signal region of the decay.
-The KOTO experiment started data taking since 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
-The data taking will continue for a few more years, and the sensitivity will be expected to reach $\mathcal{O}$(10$^{-11}$).
+The KOTO experiment started data taking in 2013 and has achieved an experimental sensitivity of 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
+The data taking will continue for a few more years, and the sensitivity is expected to reach $\mathcal{O}$(10$^{-11}$), close to the detection limit for a branching fraction near 3~$\times$~10$^{-11}$
 
-A successive experiment of the KOTO is under preparation to observe more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}.
+A successor experiment to the KOTO is aiming at observing more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}.
 In this highly sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$.
-In addition, the neutrons away from the beam axis produce a $\pi^{0}$ or $\eta$ by interacting with detector materials.
+In addition, the off-axis neutrons could produce a $\pi^{0}$ or $\eta$ by interacting with detector materials.
 Two photons from those events are also one of main backgrounds.
-We can remove them by comparing the incident angle expected from the reconstructed vertex and the actual measurement using a new sampling calorimeter in this paper.
+We can remove them by comparing the incident angle expected from the reconstructed vertex and the actual measurement using a new sampling calorimeter.
 
 In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and plastic scintillator layers.
-There is a limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation.
-A deduction of the incident angle of the EM shower using a lead scintillating fiber sandwiched sampling calorimeter is studied~\cite{PbScint}, and the angular resolution is expected to be larger than 8 degrees for 1-GeV electrons.
-We take a machine-learning approach to get better angular resolution from the analysis.
+There is an intrinsic limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation.
+In a previous study~\cite{PbScint}, a deduction of the incident angle of the EM shower using a similar lead-scintillator sandwiched sampling calorimeter, with a cell size of 9~$\times$~9~mm$^{2}$, is expected to be larger than 8 degrees for 1-GeV electrons.
+In this study, we apply a machine-learning approach to improve angular resolution from the analysis.
 Recently, machine-learning analysis has become a critical tool for better measurement of particle identification~\cite{mlp}, timing~\cite{mlt}, and energy~\cite{mle}.
@@
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
-It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.
+It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.
 
@@
 \includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
-\caption{ Event display of simulated energy deposit patterns for an 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
+\caption{ Event display of simulated energy deposit patterns for a 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
 \label{fig:Evt_Dis}
@@
 The photon direction is defined by the polar angle ($\theta$) with respect to the $z$-axis.
-Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for an 1-GeV photon at normal incidence in the $xz$- and $yz$-planes.
+Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for a 1-GeV photon at normal incidence in the $xz$- and $yz$-planes.
 Each segmented region shown in Figure~\ref{fig:Evt_Dis} represents a channel.
@@
 The number of training samples is $10^{5}$ considering the limited computing resources.
-The angle reconstruction is studied using photons generated at given incident $\theta$ angle, energy, and position.
-It turns out unchanged with the energy deposit threshold above the noise level of 0.5 MeV.
+The angle reconstruction is studied using photons generated at given incident $\theta$ angle and fixed incident energy and incident position.
+It turns out to be unchanged with the energy deposit threshold above the noise level of 0.5 MeV.
 Therefore, we do not consider random noises in this study.
+
+The angular reconstruction can be largely affected by the deviation of the incident position, coming from the spatial resolution of the incident position reconstruction, which can be overcome with the repetitive training for different incident positions.
+In this study, such effects are not considered when evaluating the angular resolution.
+The position resolution is expected to be level of 3~mm and to degrade the angular resolution as much as 40\%.
 
@@
 
-The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon.
-The feature size identical to the number of strips varies with the strip width to have the same coverage.
+The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset onto a target variable.
+Here, the feature dataset and the target varialbe correspond to the energy deposit in each scintillator strip and the incident angle of a photon, respectively.
+The feature dataset size is the number of strips, hence it varies inversely to the strip width to have the same coverage.
 In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector.
@@
 The hyperparameters of XGB drive how models are trained.
-In this paper, main five parameters are studied.
+In this paper, five main parameters are studied.
 \textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max.
 depth} defines the complexity of the decision-tree structure.
-\textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} weights a decision tree to be added onto the current model, and \textit{gamma} regulates the evaluation of each decision tree.
+\textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} determines the step length of gradient boosting, and \textit{gamma} regulates the evaluation of each decision tree.
 
@@
 \subsubsection{Strip width}
-To inspect the dependency of the angular resolution on the strip width, we deduce the angular resolution by varying the strip width from 5 to 35mm, as shown in Figure~\ref{fig:angle_reco_width}.
-The narrower the strip width, the larger the feature size.
+To inspect the dependency of the angular resolution on the strip width, we deduce the angular resolution by varying the strip width from 5 to 35mm, as shown in Figure~\ref{fig:angle_reco_width}, where each point is obtained through the fit procedure.
+The narrower the strip width, the larger the feature dataset size.
 Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than with 5-mm-wide strips.
 However, the wider strips hardly provide detailed information on the EM shower.
-The 15-mm-wide strips yield a good angular resolution of 1.24~$\pm$~0.01$^{\circ}$ and are selected for further study considering the actual construction of a prototype detector, although 10-mm-wide strips provide the best resolution.
+The 15-mm-wide strips yield an angular resolution of 1.24(1)~$\pm$~0.01$^{\circ}$ for photons impacting at the center of the strips and are selected for further study considering the actual construction of a prototype detector, although 10-mm-wide strips provide the best resolution.
 
@@
 (b) Angular resolution as a function of the radiation length ($X_{0}$) with the front layers.
-The red line corresponds to the results using entire layers of 105.}
+The red solid line represented as Full layer in the legend corresponds to the results using entire layers.}
 \label{fig:angle_reco_layer}
@@
 We study the dependency of the angle reconstruction on the number of front layers.
-Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2$X_{0}$.
+Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2~$X_{0}$.
 A fraction of the photons fails to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%.
@@
 The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
-The evolution of angular resolution degrades with the reduction of the number of layers used.
+The evolution of angular resolution degrades with the reduction of the number of layers used, as shown in figure~\ref{fig:angle_reco_layer} (b).
 
@@
 \caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers.
-The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.
-}
+The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.}
 \label{fig:multi-parameter}
@@
 
-The spectra are fitted with the empirical function of $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ describe the decreasing trend.
+The spectra in figure~\ref{fig:multi-parameter} are fitted with the empirical function, $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ describe the decreasing trend.
 The numbers of training samples reaching the angular resolution of 1.1$I$ with 25-, 15-, and 5-mm-wide strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.
@@
 In addition, the angular resolution is also determined by the training accuracy of the XGBoost, which requires a different number of training data according to the detector configuration.
-When we test a detector configuration with many channels (i.e., narrow strip), we should also prepare a large number of data for the training.
+We also emphasize on the interplay between the number of channels and training samples.
 
@@
 
+\bibitem{PAMELA}
+S. V. Borisov {\it et al.}, Instrum Exp Tech 56, 1–8 (2013)
+
 \bibitem{FERMI:LAT}
@@
 
-\bibitem{KOTOexp}
-KOTO Collaboration, Phys. Rev. Lett. 126, 121801 (2021)
-
-\bibitem{KOTObeam}
-T. Shimogawa, Nucl. Instrum. Meth. A {\bf 623} (2010) 585-587
-
 \bibitem{KOTOtheory}
 Andrzej J. Buras {\it et al.}, JHEP 11 (2015) 033
-
-\bibitem{KOTO2}
-TF on the extension of the Hadron Experimental Facility, arXiv:2110.04462
 
@@
 
-\bibitem{xgboost:2016}
-C. Tianqi {\it et al.}, 
-{\it Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining},
-(2016) 785.
+\bibitem{KOTOexp}
+KOTO Collaboration, Phys. Rev. Lett. 126, 121801 (2021)
 
-\bibitem{mle}
-DAMPE Collaboration, JINST 17 (2022) 06, P06031
+\bibitem{KOTO2}
+TF on the extension of the Hadron Experimental Facility, arXiv:2110.04462
+
+%\bibitem{KOTObeam}
+%T. Shimogawa, Nucl. Instrum. Meth. A {\bf 623} (2010) 585-587
+
+\bibitem{PbScint}
+Zu-Hao Li {\it et al.}, Chin. Phys. C 38 (2014) 5, 056203
 
@@
 
+\bibitem{mle}
+DAMPE Collaboration, JINST 17 (2022) 06, P06031
+
+\bibitem{xgboost:2016}
+C. Tianqi {\it et al.}, 
+{\it Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining},
+(2016) 785.
+
 \bibitem{GGfun}
@@
 
-\bibitem{PbScint}
-Zu-Hao Li {\it et al.}, Chin. Phys. C 38 (2014) 5, 056203
-
 \end{thebibliography}

### 2023-03-07 paper.tex
updates

@@
 Sampling calorimeters have been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics.
-The PAMELA experiment employs a strip multilayer electromagnetic calorimeter of 22 ($x$,$y$) layers of silicon strip detectors interleaved with 22 tungsten plates, which identifies the particle types and measures the deposited energy, and helps to determine the detection of the particles~\cite{PAMELA}.
+The PAMELA experiment employs a strip multilayer electromagnetic calorimeter made of 22 ($x$, $y$) silicon strip detectors interleaved with 22 tungsten plates, which identifies the particle types, measures the deposited energy, and helps to determine the direction of the particles~\cite{PAMELA}.
 The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils.
@@
 
-The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
+The toy sampling calorimeter is designed as a block consisting of alternating layers of a 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator.
 The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}.
-It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.
+It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length and 20 radiation lengths (20~$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.
 
@@
 The number of training samples is $10^{5}$ considering the limited computing resources.
-The angle reconstruction is studied using photons generated at given incident $\theta$ angle and fixed incident energy and incident position.
-It turns out to be unchanged with the energy deposit threshold above the noise level of 0.5 MeV.
+The angle reconstruction is studied using photons generated at given incident $\theta$ angle and fixed incident energy and position.
+It turns out to be unchanged with the energy deposit threshold above the noise level of 0.5 MeV, which is sufficiently higher than the expected noise level.
 Therefore, we do not consider random noises in this study.
-
-The angular reconstruction can be largely affected by the deviation of the incident position, coming from the spatial resolution of the incident position reconstruction, which can be overcome with the repetitive training for different incident positions.
-In this study, such effects are not considered when evaluating the angular resolution.
-The position resolution is expected to be level of 3~mm and to degrade the angular resolution as much as 40\%.
 
@@
 The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset onto a target variable.
-Here, the feature dataset and the target varialbe correspond to the energy deposit in each scintillator strip and the incident angle of a photon, respectively.
+Here, the feature dataset and the target variable correspond to the energy deposit in each scintillator strip and the incident angle of a photon, respectively.
 The feature dataset size is the number of strips, hence it varies inversely to the strip width to have the same coverage.
@@
 The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$.
-The evolution of angular resolution degrades with the reduction of the number of layers used, as shown in figure~\ref{fig:angle_reco_layer} (b).
+The evolution of angular resolution degrades with the reduction of the number of layers used, as shown in Figure~\ref{fig:angle_reco_layer} (b).
 
@@
 For the toy sampling calorimeter with 15-mm-wide strips and 32 layers, the angular resolution was obtained as 1.30~$\pm$~0.01$^{\circ}$ in machine learning with $10^{5}$ training samples.
+The present result can be changed when a photon is incident at a different position from the origin of the training process.
+Since the position resolution at the current setup is expected to be 2.1~mm, the angular resolution can be degraded by as much as 25\%.
 Energy dependence of the angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}}$.

### 2023-03-08 paper.tex
updates

@@
 Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}.
-Sampling calorimeters have been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics.
+
+Sampling calorimeters have been used to measure the direction of arriving photons in a space-based detector.
 The PAMELA experiment employs a strip multilayer electromagnetic calorimeter made of 22 ($x$, $y$) silicon strip detectors interleaved with 22 tungsten plates, which identifies the particle types, measures the deposited energy, and helps to determine the direction of the particles~\cite{PAMELA}.
@@
 The KOTO experiment started data taking in 2013 and has achieved an experimental sensitivity of 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}.
-The data taking will continue for a few more years, and the sensitivity is expected to reach $\mathcal{O}$(10$^{-11}$), close to the detection limit for a branching fraction near 3~$\times$~10$^{-11}$
+The data taking will continue for a few more years, and the sensitivity is expected to reach $\mathcal{O}$(10$^{-11}$), close to the detection limit for a branching fraction near 3~$\times$~10$^{-11}$.
 
@@
 \includegraphics[width=0.58\textwidth]{Fig5_width_including7.5_12.5mm.pdf}
-\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
+\caption{ Angular resolutions as a function of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
 \label{fig:angle_reco_width}
@@
 \caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers.
-The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.}
+The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.The vertical dashed-dotted line indicates the 100k events.}
 \label{fig:multi-parameter}
